### 2022-05-22 scripts/Paper 1.Rmd
commit first rmd file

---
title: "Paper 1"
author: "Marion Nyberg"
date: "27/04/2022"
output: html_document
---

```{r setup, include=FALSE}
library(dplyr)
library(data.table)
library(janitor)
library(plotly)
library(plyr)
library(knitr)
library(tidyverse)
#library(devtools)
library(openair)
library(tidyr)
library(naniar)

rm(list = ls())
wd <- ("R:/SET/PlantSci/Shared Work Spaces/Ecology/Flux/SP_data")
setwd(wd)
knitr::opts_knit$set(root.dir = wd)
```

Below are conversion factors and functions used in the markdown file:

```{r functions and conversions}
d.avg <- 1800 * 48 #60 secs * 60 mins * 24 hours (# of secs in day)
co2_conv <- 12.01/(10^6)

tidy.csv <- function(x){
  input <- x[-c(1,2),] %>%
    row_to_names(., 1)
}

gofC.f <- function(x){ # function to convert to mean 30 minute to g of C
  (x*d.avg)*co2_conv
}

gtomg.f <- function(x){ # function to convert from g to mg
  x*1000
}
```

```{r read data and some data class cleaning, include=FALSE}
input <- fread("./PFP/L6/SilverPlains_L6.csv", header = FALSE, na.strings = "-9999") 
input <- tidy.csv(input)

input <- input %>% select(xlDateTime, Fe, Fg_Av, Fh, Fld, Flu, Fn, Fsu, Fsd, Precip, RH, Sws, Ta, Ts, VPD, Wd_SONIC_Av, Ws_SONIC_Av,ER_LT_all, GPP_LT,GPP_SOLO, NEE_LT ) # select met variables (add more as needed)
colnames(input) <- c('Timestamp', 'LE', 'G', 'H', 'LWin', 'LWout', 'NETRAD', 'SWout', 'SWin', 'Precip', 'RH', 'SWC', 'Ta', 'Ts', 'VPD', 'WD', 'WS', 'ER_LT', 'GPP_LT', 'GPP_SOLO', 'NEE_LT')

input$Timestamp <- as.POSIXct(input$Timestamp, format= "%d/%m/%Y %H:%M") # change from character to POSIXct
input[,2:21] <- as.data.frame(sapply(input[,2:21], as.numeric)) # convert data frame from character to numeric

input$jday <-yday(input$Timestamp) # add jday
input$Year <- year(input$Timestamp) # extract year
input$Year <- as.factor(input$Year) # convert year from integer to factor
input$month <- month(as.POSIXct(input$Timestamp)) # extract month
```

```{r weird stuff in data filtered out}
input$SWin <- ifelse(input$SWin < 0, NA, input$SWin)
```

```{r create daily mean dataframe, include=FALSE}
# add variables to this daily df as needed
input.daily <- input %>%
  drop_na(Timestamp) %>% # some NAs in the Timestamp for some reason. Need to look into
  ddply(c("Year", "jday"), summarise,
        Precip = sum(Precip, na.rm = TRUE),
        Ta.mean = mean(Ta, na.rm = TRUE),
        Ta.max = max(Ta, na.rm = TRUE),
        Ta.min = min(Ta, na.rm = TRUE),
        Ts.mean = mean(Ts, na.rm = TRUE),
        Ts.max = max(Ts, na.rm = TRUE),
        Ts.min = min(Ts, na.rm = TRUE),
        SWC = mean(SWC, na.rm = TRUE),
        RH = mean(RH, na.rm = TRUE),
        VPD = mean(VPD, na.rm = TRUE),
        NEE_LT = mean(NEE_LT, na.rm = TRUE), #daily average umol m-2 s-1
        ER_LT = mean(ER_LT, na.rm = TRUE),
        GPP_LT = mean(GPP_LT, na.rm = TRUE)) %>%
  mutate(NEE_LT.gC = gofC.f(NEE_LT),  #converts to daily total NEE in g C CO2
         ER_LT.gC = gofC.f(ER_LT),
         GPP_LT.gC = gofC.f(GPP_LT))
```

## Results {.tabset}

### Precipitation

```{r Precipitation, echo=FALSE, message = FALSE, fig.width = 10, fig.height = 4}
# this is the rainfall data for Interlaken estate, but there is a lot missing so results are probably underestimated
# need to uodate this each month or so from BOM website
input.bom.rain <- read.csv("R:/SET/PlantSci/Shared Work Spaces/Ecology/Peoples files/Marion Nyberg/PhD/SP warming experiment/Interlaken_BOM_rainfall.csv") %>% #filter(Year >= 2010 & Year <= 2019) %>% # used all years available due to missing data 1995 - 2021
  select(Year, Month, Day, Rainfall.amount..millimetres.) %>%
  mutate(Precip = replace_na(Rainfall.amount..millimetres., 0)) %>%
  ddply(c("Year", "Month"), summarise,
  monthly.total = sum(Precip)) %>%
  ddply(c("Month"), summarise,
        monthly.total = mean(monthly.total)) 
names(input.bom.rain)[1] <- "month"
input.bom.rain$Year <- "BOMavg"

input.daily %>% mutate(Precip = replace_na(Precip, 0)) %>%
  ddply(c("Year", "month"), summarise,
  monthly.total = sum(Precip)) %>%
  ggplot(., aes(x = month, y = monthly.total, group = Year, fill = Year)) +
       scale_x_discrete(limits = month.abb) +
  geom_col(position = "dodge") + 
  ylab("Monthly rainfall (mm)")+
  xlab("Month")+
  theme_classic()
```

Total monthly precipitation at Silver Plains. The BOM average is data from the Interlaken Estate (1995-2021), however, there are multiple missing values, so results may be underestimated.

### Air and soil temperature

Mean daily air temperature (top) and monthly (bottom)
Mean daily air temperature

```{r Air temperature, echo=FALSE, message = FALSE, fig.width = 10, fig.height = 4}
ggplotly(ggplot(input.daily, aes(x = jday, y = Ts, group = Year)) +
  geom_line(aes(color = Year))+
  theme_classic())

ggplotly(ggplot(input.daily, aes(x = jday, y = Ta.mean, group = Year)) +
  geom_line(aes(color = Year))+
     geom_ribbon(aes(ymin=Ta.min, ymax=Ta.max), alpha=.3, linetype=0) +
  theme_classic())

ggplotly(ggplot(input.daily, aes(x = jday, y = Ta.max, group = Year)) +
  geom_line(aes(color = Year))+
  theme_classic())

ggplotly(ggplot(input.daily, aes(x = jday, y = Ta.min, group = Year)) +
  geom_line(aes(color = Year))+
  theme_classic())
```

### VPD

```{r VPD, echo=FALSE, message = FALSE, fig.width = 10, fig.height = 4}
ggplotly(ggplot(input.daily, aes(x = as.Date(jday, origin = ("2020-01-01")), y = VPD, group = Year)) +
  geom_line(aes(color = Year))+
  scale_x_date(date_labels = "%b", date_breaks = "1 month") +
  xlab("Month")+
  theme_classic())
```

### SWC

```{r, echo=FALSE, message = FALSE, fig.width = 10, fig.height = 4}
ggplotly(ggplot(input.daily, aes(jday, SWC, group = Year)) +
  geom_line(aes(color = Year))+
  xlab('Julian day of year') +
  ylab('SWC %') +
  theme_classic())
```

### 2022-05-23 scripts/Paper 1.Rmd
update

@@
 # need to uodate this each month or so from BOM website
-input.bom.rain <- read.csv("R:/SET/PlantSci/Shared Work Spaces/Ecology/Peoples files/Marion Nyberg/PhD/SP warming experiment/Interlaken_BOM_rainfall.csv") %>% #filter(Year >= 2010 & Year <= 2019) %>% # used all years available due to missing data 1995 - 2021
+input.bom.rain <- read.csv("R:/SET/PlantSci/Shared Work Spaces/Ecology/Peoples files/Marion Nyberg/PhD/SP warming experiment/Interlaken_BOM_rainfall.csv") %>% filter(Year >= 2019)
+  #filter(Year >= 2010 & Year <= 2019) %>% # used all years available due to missing data 1995 - 2021
   select(Year, Month, Day, Rainfall.amount..millimetres.) %>%
@@
 ```
+
+```{r timeseries analysis}
+library(forecast)
+
+```

### 2022-05-24 scripts/Paper 1.Rmd
add rainfall data

@@
 ```{r Precipitation, echo=FALSE, message = FALSE, fig.width = 10, fig.height = 4}
-# this is the rainfall data for Interlaken estate, but there is a lot missing so results are probably underestimated
-# need to uodate this each month or so from BOM website
-input.bom.rain <- read.csv("R:/SET/PlantSci/Shared Work Spaces/Ecology/Peoples files/Marion Nyberg/PhD/SP warming experiment/Interlaken_BOM_rainfall.csv") %>% filter(Year >= 2019)
-  #filter(Year >= 2010 & Year <= 2019) %>% # used all years available due to missing data 1995 - 2021
-  select(Year, Month, Day, Rainfall.amount..millimetres.) %>%
-  mutate(Precip = replace_na(Rainfall.amount..millimetres., 0)) %>%
-  ddply(c("Year", "Month"), summarise,
-  monthly.total = sum(Precip)) %>%
-  ddply(c("Month"), summarise,
-        monthly.total = mean(monthly.total)) 
-names(input.bom.rain)[1] <- "month"
-input.bom.rain$Year <- "BOMavg"
-
 input.daily %>% mutate(Precip = replace_na(Precip, 0)) %>%
@@
   theme_classic()
+
+#below is precip data from liaweenee - it only goes up to Jan 2022 right now
+rainfall_L <- read.csv("R:/SET/PlantSci/Shared Work Spaces/Ecology/Peoples files/Marion Nyberg/PhD/Rainfall/rainfall.csv")
+rainfall_L <- rainfall_L[-1]
+colnames(rainfall_L)[4] <- "Precip"
+rainfall_L$Year <- as.factor(rainfall_L$Year)
+
+rainfall_L %>% mutate(Precip = replace_na(Precip, 0)) %>%
+  ddply(c("Year", "Month"), summarise,
+  monthly.total = sum(Precip)) %>%
+  ggplot(., aes(x = Month, y = monthly.total, group = Year, fill = Year)) +
+       scale_x_discrete(limits = month.abb) +
+  geom_col(position = "dodge") + 
+  ylab("Monthly rainfall (mm)")+
+  xlab("Month")+
+  theme_classic()
+
 ```

### 2022-05-24 scripts/Paper 1.Rmd
update

@@
   drop_na(Timestamp) %>% # some NAs in the Timestamp for some reason. Need to look into
-  ddply(c("Year", "jday"), summarise,
+  ddply(c("Year", "jday", "month"), summarise,
         Precip = sum(Precip, na.rm = TRUE),

### 2022-05-26 scripts/Paper 1.Rmd
update

@@
 rainfall_L$Year <- as.factor(rainfall_L$Year)
+rainfall_L <- rainfall_L %>% filter(Year == 2019)
+colnames(rainfall_L)[3] <- "jday"
+colnames(rainfall_L)[2] <- "month"
+rainfall_L$Site <- "L"
 
@@
 
+rainfall.SP <- input.daily %>% select(Precip, jday, month, Year)
+rainfall.SP$Site <- "SP"
+
+rainfall <- rbind(rainfall_L, rainfall.SP)
+
 ```
-
-Total monthly precipitation at Silver Plains. The BOM average is data from the Interlaken Estate (1995-2021), however, there are multiple missing values, so results may be underestimated.
 
@@
 ```{r Air temperature, echo=FALSE, message = FALSE, fig.width = 10, fig.height = 4}
-ggplotly(ggplot(input.daily, aes(x = jday, y = Ts, group = Year)) +
-  geom_line(aes(color = Year))+
-  theme_classic())
 

### 2022-05-27 scripts/Paper 1.Rmd
add seasonal rainfall

@@
 library(naniar)
+library(forecast)
 
@@
 rainfall_L %>% mutate(Precip = replace_na(Precip, 0)) %>%
-  ddply(c("Year", "Month"), summarise,
+  ddply(c("Year", "month"), summarise,
   monthly.total = sum(Precip)) %>%
-  ggplot(., aes(x = Month, y = monthly.total, group = Year, fill = Year)) +
+  ggplot(., aes(x = month, y = monthly.total, group = Year, fill = Year)) +
        scale_x_discrete(limits = month.abb) +
@@
   ylab("Monthly rainfall (mm)")+
-  xlab("Month")+
+  xlab("month")+
   theme_classic()
@@
 ```{r Air temperature, echo=FALSE, message = FALSE, fig.width = 10, fig.height = 4}
-
 ggplotly(ggplot(input.daily, aes(x = jday, y = Ta.mean, group = Year)) +
@@
 
+```{r add seasons, include=FALSE}
+rainfall$season <- "" # add season variable
+
+# define seasons
+winter <- (rainfall$month == "6" | rainfall$month == "7" | rainfall$month == "8")
+spring <- (rainfall$month == "9" | rainfall$month == "10" | rainfall$month == "11")
+summer <- (rainfall$month == "12" | rainfall$month == "1" | rainfall$month == "2")
+autumn <- (rainfall$month == "3" | rainfall$month == "4" | rainfall$month == "5")
+
+rainfall$season[winter] <- "Winter"
+rainfall$season[spring] <- "Spring"
+rainfall$season[summer] <- "Summer"
+rainfall$season[autumn] <- "Autumn"
+
+season_levelorder <-  c('Summer', 'Autumn', 'Winter', 'Spring')
+
+rainfall$season <- factor(rainfall$season , levels=c('Summer', 'Autumn', 'Winter', 'Spring'))
+```
+
+```{r create rainfall summary}
+rainfall.summary <- rainfall %>% ddply(c("Year", "Site", "season"), summarise,
+                                       seasonal.sum = sum(Precip, na.rm = TRUE))
+rainfall.summary %>% 
+  ggplot(., aes(x = season, y = seasonal.sum, group = Year, fill = Site)) +
+  geom_col(position = "dodge", aes(fill = Year)) + 
+  ylab("Monthly rainfall (mm)")+
+  xlab("month")+
+  theme_classic()
+
+```
+
 ```{r timeseries analysis}
 library(forecast)
-
 ```

### 2022-05-27 scripts/Paper 1.Rmd
u

@@
 library(forecast)
+library(kableExtra)
 
@@
                                        seasonal.sum = sum(Precip, na.rm = TRUE))
+
+rainfall.summary %>% kbl() %>% kable_styling()
+
 rainfall.summary %>% 

### 2022-05-27 scripts/Paper 1.Rmd
u

@@
 ```{r setup, include=FALSE}
-library(dplyr)
 library(data.table)
@@
 library(plyr)
+library(dplyr)
 library(knitr)
@@
 library(kableExtra)
+library(htmltools)
 
@@
 spring <- (rainfall$month == "9" | rainfall$month == "10" | rainfall$month == "11")
-summer <- (rainfall$month == "12" | rainfall$month == "1" | rainfall$month == "2")
+earlysummer <- (rainfall$month == "12")
+latesummer <- (rainfall$month == "1" | rainfall$month == "2")
 autumn <- (rainfall$month == "3" | rainfall$month == "4" | rainfall$month == "5")
@@
 rainfall$season[spring] <- "Spring"
-rainfall$season[summer] <- "Summer"
+rainfall$season[earlysummer] <- "EarlySummer"
+rainfall$season[latesummer] <- "LateSummer"
 rainfall$season[autumn] <- "Autumn"
 
-season_levelorder <-  c('Summer', 'Autumn', 'Winter', 'Spring')
+rainfall$season <- factor(rainfall$season , levels=c('EarlySummer','LateSummer', 'Autumn', 'Winter', 'Spring'))
 
-rainfall$season <- factor(rainfall$season , levels=c('Summer', 'Autumn', 'Winter', 'Spring'))
+input.daily$season <- "" # add season variable
+
+# define seasons
+winter <- (input.daily$month == "6" | input.daily$month == "7" | input.daily$month == "8")
+spring <- (input.daily$month == "9" | input.daily$month == "10" | input.daily$month == "11")
+earlysummer <- (input.daily$month == "12")
+latesummer <- (input.daily$month == "1" | input.daily$month == "2")
+autumn <- (input.daily$month == "3" | input.daily$month == "4" | input.daily$month == "5")
+
+input.daily$season[winter] <- "Winter"
+input.daily$season[spring] <- "Spring"
+input.daily$season[earlysummer] <- "EarlySummer"
+input.daily$season[latesummer] <- "LateSummer"
+input.daily$season[autumn] <- "Autumn"
+
+input.daily$season <- factor(input.daily$season , levels=c('EarlySummer','LateSummer', 'Autumn', 'Winter', 'Spring'))
 ```
@@
                                        seasonal.sum = sum(Precip, na.rm = TRUE))
-
-rainfall.summary %>% kbl() %>% kable_styling()
 
@@
 ```
+```{r seasonal NEE}
+NEE.summary <- input.daily %>% ddply(c("Year", "season", "jday"), summarise,
+                                       seasonal.sum = cumsum(NEE_LT.gC))
+
+# check when switches from sink to source
+
+input.daily %>% select(jday, NEE_LT.gC, Year) %>%
+  ggplot(., aes(jday, NEE_LT.gC)) +
+  geom_line(aes(colour = Year))
+
+NEE.summary %>%
+  ggplot(., aes(jday, seasonal.sum)) +
+  geom_line(aes(colour = Year))
+
+```
 

### 2022-05-28 scripts/Paper 1.Rmd
add monthly avg

@@
 library(htmltools)
+library(ggpubr)
+library(rstatix)
+library(broom)
 
@@
 input$month <- month(as.POSIXct(input$Timestamp)) # extract month
+input$month <- as.factor(input$month)
 ```
@@
 rainfall <- rbind(rainfall_L, rainfall.SP)
+rainfall$month <- as.factor(rainfall$month)
 
@@
 ```{r create rainfall summary}
-rainfall.summary <- rainfall %>% ddply(c("Year", "Site", "season"), summarise,
-                                       seasonal.sum = sum(Precip, na.rm = TRUE))
+rainfall.summary <- rainfall %>% ddply(c("Year", "Site", "month"), summarise,
+                                       monthly.sum = sum(Precip, na.rm = TRUE))
 
 rainfall.summary %>% 
-  ggplot(., aes(x = season, y = seasonal.sum, group = Year, fill = Site)) +
+  ggplot(., aes(x = month, y = monthly.sum, group = Year, fill = Site)) +
   geom_col(position = "dodge", aes(fill = Year)) + 
@@
 
+rainfall.summary %>% 
+  ggplot(., aes(x = month, y = monthly.sum, group = Year, fill = Site)) +
+  geom_point(aes(color = Year, size = 2)) + 
+  ylab("Monthly rainfall (mm)")+
+  xlab("month")+
+  theme_classic()
+
 ```
+
 ```{r seasonal NEE}
-NEE.summary <- input.daily %>% ddply(c("Year", "season", "jday"), summarise,
-                                       seasonal.sum = cumsum(NEE_LT.gC))
+NEE.summary <- input.daily %>% ddply(c("month", "Year"), summarise,
+                                       monthly.sum = sum(NEE_LT.gC))
 
 # check when switches from sink to source
+
+NEE.summary %>% 
+  ggplot(., aes(x = month, y = monthly.sum, group = Year, fill = Site)) +
+  geom_col(position = "dodge", aes(fill = Year)) + 
+  ylab("Monthly rainfall (mm)")+
+  xlab("month")+
+  theme_classic()
 
@@
 ```{r timeseries analysis}
-library(forecast)
+tsData <- EuStockMarkets[, 1] # ts data
+decomposedRes <- decompose(tsData, type="mult") # use type = "additive" for additive components
+plot (decomposedRes) # see plot below
+stlRes <- stl(tsData, s.window = "periodic")
+
+input.daily %>% anova_test(NEE_LT.gC~Precip+season)
+
+rainfall$TS <- as.Date(with(rainfall, paste(Year, month, jday,sep="-")), "%Y-%m-%d")
+
+TSData <- rainfall[, 1] # ts data
+decomposedRes <- decompose(tsData, type="mult") # use type = "additive" for additive components
+plot (decomposedRes) # see plot below
+stlRes <- stl(tsData, s.window = "periodic")
 ```

### 2022-05-29 scripts/Paper 1.Rmd
add jday to rainfall

@@
 rainfall_L <- rainfall_L %>% filter(Year == 2019)
-colnames(rainfall_L)[3] <- "jday"
+colnames(rainfall_L)[3] <- "day"
 colnames(rainfall_L)[2] <- "month"
 rainfall_L$Site <- "L"
+rainfall_L$date <- as.Date(with(rainfall_L, paste(Year, month, day,sep="-")), "%Y-%m-%d")
+rainfall_L$jday <- yday(rainfall_L$date)
 
@@
 
+```{r create new dataframe for timeseries analysis}
+rainfall.2merge <- rainfall %>% filter(Year == 2019  & jday < 354)
+input.daily$Site <- "SP"
+
+tsData <- rbind.fill(rainfall.2merge, input.daily) %>% 
+  select(Year, month, jday, Precip, NEE_LT.gC, ER_LT.gC, GPP_LT.gC) %>%
+  mutate(
+    NEE2weeks = lag(NEE_LT.gC, n = 14, default = NA)
+  )
+
+tsData$date <- as.Date(with(tsData, paste(Year, month, jday,sep="-")), "%Y-%m-%d")
+lm1 <- lm(NEE2weeks~Precip, tsData)
+summary(lm1)
+
+lm2 <- lm(NEE_LT.gC~Precip, tsData)
+summary(lm2)
+```
+
 ```{r timeseries analysis}
@@
 
-TSData <- rainfall[, 1] # ts data
-decomposedRes <- decompose(tsData, type="mult") # use type = "additive" for additive components
-plot (decomposedRes) # see plot below
-stlRes <- stl(tsData, s.window = "periodic")
 ```

### 2022-05-29 scripts/Paper 1.Rmd
u

@@
 rainfall.SP$Site <- "SP"
+rainfall.SP$date <- as.Date(with(rainfall.SP, paste(Year, month, jday,sep="-")), "%Y-%m-%j")
+rainfall.2merge <- rainfall_L %>% filter(Year == 2019  & jday >= 244 & jday < 354)
 
-rainfall <- rbind(rainfall_L, rainfall.SP)
+rainfall <- rbind.fill(rainfall.2merge, rainfall.SP)
 rainfall$month <- as.factor(rainfall$month)
@@
   theme_classic()
-
-rainfall.summary %>% 
-  ggplot(., aes(x = month, y = monthly.sum, group = Year, fill = Site)) +
-  geom_point(aes(color = Year, size = 2)) + 
-  ylab("Monthly rainfall (mm)")+
-  xlab("month")+
-  theme_classic()
-
 ```

### 2022-05-29 scripts/Paper 1.Rmd
update

@@
 
+rainfall%>% ddply(c("Year", "season"), summarise,
+                    seasonal.sum = sum(Precip, na.rm = TRUE))
+
 rainfall.summary %>% 
@@
 ```{r seasonal NEE}
-NEE.summary <- input.daily %>% ddply(c("month", "Year"), summarise,
+NEE.summary <- input.daily %>% ddply(c("Year", "month"), summarise,
                                        monthly.sum = sum(NEE_LT.gC))
+
+GPP.summary <- input.daily %>% ddply(c("Year", "month"), summarise,
+                                       monthly.sum = sum(GPP_LT.gC))
+
+ER.summary <- input.daily %>% ddply(c("Year", "month"), summarise,
+                                       monthly.sum = sum(ER_LT.gC))
 
@@
   geom_col(position = "dodge", aes(fill = Year)) + 
-  ylab("Monthly rainfall (mm)")+
+  ylab("Monthly NEE")+
   xlab("month")+
@@
 
-input.daily %>% select(jday, NEE_LT.gC, Year) %>%
-  ggplot(., aes(jday, NEE_LT.gC)) +
-  geom_line(aes(colour = Year))
+GPP.summary %>%
+  ggplot(., aes(x = month, y = monthly.sum, group = Year, fill = Site)) +
+  geom_col(position = "dodge", aes(fill = Year)) + 
+  ylab("Monthly GPP")+
+  xlab("month")+
+  theme_classic()
 
-NEE.summary %>%
-  ggplot(., aes(jday, seasonal.sum)) +
-  geom_line(aes(colour = Year))
-
+ER.summary %>%
+  ggplot(., aes(x = month, y = monthly.sum, group = Year, fill = Site)) +
+  geom_col(position = "dodge", aes(fill = Year)) + 
+  ylab("Monthly ER")+
+  xlab("month")+
+  theme_classic()
 ```

### 2022-06-08 scripts/Paper 1.Rmd
u

@@
 
+Ts.summary <- input.daily %>% ddply(c("Year", "month"), summarise,
+                                       monthly.mean = mean(Ts.mean))
+
 # check when switches from sink to source
@@
   ggplot(., aes(x = month, y = monthly.sum, group = Year, fill = Site)) +
+  geom_col(position = "dodge", aes(fill = Year)) + 
+  ylab("Monthly ER")+
+  xlab("month")+
+  theme_classic()
+
+Ts.summary %>%
+  ggplot(., aes(x = month, y = monthly.mean, group = Year, fill = Site)) +
   geom_col(position = "dodge", aes(fill = Year)) + 

### 2022-06-13 scripts/Paper 1.Rmd
add months to rainfall

--- 2022-05-29 scripts/Paper 1.Rmd
@@
   ggplot(., aes(x = month, y = monthly.total, group = Year, fill = Year)) +
-       scale_x_discrete(limits = month.abb) +
+       #scale_x_discrete(limits = month.abb) +
   geom_col(position = "dodge") + 
@@
 rainfall_L <- rainfall_L %>% filter(Year == 2019)
-colnames(rainfall_L)[3] <- "day"
+colnames(rainfall_L)[3] <- "jday"
 colnames(rainfall_L)[2] <- "month"
 rainfall_L$Site <- "L"
-rainfall_L$date <- as.Date(with(rainfall_L, paste(Year, month, day,sep="-")), "%Y-%m-%d")
-rainfall_L$jday <- yday(rainfall_L$date)
 
@@
 rainfall.SP$Site <- "SP"
-rainfall.SP$date <- as.Date(with(rainfall.SP, paste(Year, month, jday,sep="-")), "%Y-%m-%j")
-rainfall.2merge <- rainfall_L %>% filter(Year == 2019  & jday >= 244 & jday < 354)
 
-rainfall <- rbind.fill(rainfall.2merge, rainfall.SP)
+rainfall <- rbind(rainfall_L, rainfall.SP)
 rainfall$month <- as.factor(rainfall$month) 
+rainfall$month <- month.abb[rainfall$month]
+
+rainfall %>%  mutate(Precip = replace_na(Precip, 0)) %>%
+  ddply(c("Year", "month"), summarise,
+  monthly.total = sum(Precip)) %>%
+  ggplot(., aes(x = month, y = monthly.total, group = Year, fill = Year)) +
+       scale_x_discrete(limits = month.abb) +
+  geom_col(position = "dodge") + 
+  ylab("Monthly rainfall (mm)")+
+  xlab("Month")+
+  theme_classic()
 
@@
   theme_classic()
+
+rainfall.summary %>% 
+  ggplot(., aes(x = month, y = monthly.sum, group = Year, fill = Site)) +
+  geom_point(aes(color = Year, size = 2)) + 
+  ylab("Monthly rainfall (mm)")+
+  xlab("month")+
+  theme_classic()
+
 ```
@@
 
-NEE.summary %>%
-  ggplot(., aes(jday, seasonal.sum)) +
-  geom_line(aes(colour = Year))
-
 ```
 
-```{r create new dataframe for timeseries analysis}
-rainfall.2merge <- rainfall %>% filter(Year == 2019  & jday < 354)
-input.daily$Site <- "SP"
+```{r cumulative fluxes}
 
-tsData <- rbind.fill(rainfall.2merge, input.daily) %>% 
-  select(Year, month, jday, Precip, NEE_LT.gC, ER_LT.gC, GPP_LT.gC) %>%
-  mutate(
-    NEE2weeks = lag(NEE_LT.gC, n = 14, default = NA)
-  )
+cumulative.co2fluxes <- input %>%
+  drop_na(Timestamp) %>% # some NAs in the Timestamp for some reason. Need to look into
+  ddply(c("Year", "jday", "month", "season"), summarise,
+        Fco2 = gofC.f(mean(Fco2, na.rm = TRUE)),
+        ER = gofC.f(mean(ER_SOLO, na.rm = TRUE)),
+        GPP = gofC.f(mean(GPP_SOLO, na.rm = TRUE)))
 
-tsData$date <- as.Date(with(tsData, paste(Year, month, jday,sep="-")), "%Y-%m-%d")
-lm1 <- lm(NEE2weeks~Precip, tsData)
-summary(lm1)
+input.co2fluxes$GPP <- ifelse(input.co2fluxes$GPP < 0 , NA, input.co2fluxes$GPP) # for some reason there were values < 0 for GPP
 
-lm2 <- lm(NEE_LT.gC~Precip, tsData)
-summary(lm2)
+input.co2fluxes$ERcum_year <- as.numeric(unlist(tapply(input.co2fluxes$ER, input.co2fluxes$Year, cumsum)))
+input.co2fluxes$NEEcum_year <- as.numeric(unlist(tapply(input.co2fluxes$Fco2, input.co2fluxes$Year, cumsum)))
+input.co2fluxes$GPPcum_year <- as.numeric(unlist(tapply(input.co2fluxes$GPP, input.co2fluxes$Year, cumsum)))
+
+input.co2fluxes$GPP<- ifelse(is.na(input.co2fluxes$GPP), "0", input.co2fluxes$GPP) # replace NA with 0 for cumsum
+
+(NEE <- plot_ly(input.co2fluxes, x = ~jday, y = ~NEEcum_year, split = ~Year, name = ~Year, type = 'scatter', mode = 'lines'))
+
+(ER <- plot_ly(input.co2fluxes, x = ~jday, y = ~ERcum_year, split = ~Year, name = ~Year, type = 'scatter', mode = 'lines'))
+
+(GPP <- plot_ly(input.co2fluxes, x = ~jday, y = ~GPPcum_year, split = ~Year, name = ~Year, type = 'scatter', mode = 'lines'))
+
 ```
@@
 
+TSData <- rainfall[, 1] # ts data
+decomposedRes <- decompose(tsData, type="mult") # use type = "additive" for additive components
+plot (decomposedRes) # see plot below
+stlRes <- stl(tsData, s.window = "periodic")
 ```

### 2022-06-14 scripts/Paper 1.Rmd
update

@@
 library(broom)
+library(gtable)
+library(gridExtra)
+library(cowplot)
 
@@
          GPP_LT.gC = gofC.f(GPP_LT))
+
+input.daily$month <- as.numeric(input.daily$month) 
+input.daily$month <- month.abb[input.daily$month]
+
 ```
@@
 
-```{r Precipitation, echo=FALSE, message = FALSE, fig.width = 10, fig.height = 4}
-input.daily %>% mutate(Precip = replace_na(Precip, 0)) %>%
+```{r Precipitation, echo=FALSE, message = FALSE, fig.width = 8, fig.height = 4}
+
+(SP.rain <- input.daily %>% mutate(Precip = replace_na(Precip, 0)) %>%
   ddply(c("Year", "month"), summarise,
@@
   xlab("Month")+
-  theme_classic()
+   scale_x_discrete(limits = month.abb) +
+  theme_classic()+
+  theme(axis.title = element_text(size = 14),
+          axis.text = element_text(size = 13),
+          legend.text = element_text(size = 13),
+          legend.title = element_text(size = 14)))
 
@@
 rainfall_L <- read.csv("R:/SET/PlantSci/Shared Work Spaces/Ecology/Peoples files/Marion Nyberg/PhD/Rainfall/rainfall.csv")
-rainfall_L <- rainfall_L[-1]
-colnames(rainfall_L)[4] <- "Precip"
+rainfall_L <- rainfall_L[-4]
+colnames(rainfall_L)[5] <- "Precip"
 rainfall_L$Year <- as.factor(rainfall_L$Year)
 rainfall_L <- rainfall_L %>% filter(Year == 2019)
-colnames(rainfall_L)[3] <- "jday"
-colnames(rainfall_L)[2] <- "month"
+colnames(rainfall_L)[1] <- "jday"
+colnames(rainfall_L)[3] <- "month"
 rainfall_L$Site <- "L"
+rainfall_L <- rainfall_L %>% filter(month >= 9)
 
@@
 rainfall <- rbind(rainfall_L, rainfall.SP)
-rainfall$month <- as.factor(rainfall$month) 
-rainfall$month <- month.abb[rainfall$month]
+rainfall$month <- as.numeric(rainfall$month) 
+rainfall$month.abb <- month.abb[rainfall$month]
 
@@
   xlab("Month")+
-  theme_classic()
+  theme_classic()+
+    theme(axis.title = element_text(size = 14),
+          axis.text = element_text(size = 13),
+          legend.text = element_text(size = 13),
+          legend.title = element_text(size = 14))
 
@@
 
-```{r Air temperature, echo=FALSE, message = FALSE, fig.width = 10, fig.height = 4}
-ggplotly(ggplot(input.daily, aes(x = jday, y = Ta.mean, group = Year)) +
-  geom_line(aes(color = Year))+
-     geom_ribbon(aes(ymin=Ta.min, ymax=Ta.max), alpha=.3, linetype=0) +
-  theme_classic())
+```{r Air temperature, echo=FALSE, message = FALSE, fig.width = 8, fig.height = 4}
+TA <- ggplot(input.daily, aes(x = jday, y = Ta.mean, group = Year)) +
+  geom_line(aes(color = Year), size =1)+
+    xlab("Julian day of year")+
+    ylab("Air temperature (°C)")+
+     #geom_ribbon(aes(ymin=Ta.min, ymax=Ta.max), alpha=.3, linetype=0) +
+  theme_classic()+
+    theme(axis.title = element_text(size = 14),
+          axis.text = element_text(size = 13),
+          legend.text = element_text(size = 13),
+          legend.title = element_text(size = 14))
+
+(TS <- ggplot(input.daily, aes(x = jday, y = Ts.mean, group = Year)) +
+  geom_line(aes(color = Year), size =1)+
+    xlab("Julian day of year")+
+    ylab("Soil temperature (°C)")+
+     #geom_ribbon(aes(ymin=Ta.min, ymax=Ta.max), alpha=.3, linetype=0) +
+  theme_classic()+
+    theme(axis.title = element_text(size = 14),
+          axis.text = element_text(size = 13),
+          legend.text = element_text(size = 13),
+          legend.title = element_text(size = 14)))
 
@@
 
-```{r, echo=FALSE, message = FALSE, fig.width = 10, fig.height = 4}
-ggplotly(ggplot(input.daily, aes(jday, SWC, group = Year)) +
-  geom_line(aes(color = Year))+
+```{r, echo=FALSE, message = FALSE, fig.width = 8, fig.height = 4}
+SWC <- ggplot(input.daily, aes(jday, SWC, group = Year)) +
+  geom_line(aes(color = Year), size = 1.5)+
   xlab('Julian day of year') +
   ylab('SWC %') +
-  theme_classic())
+  theme_classic() + 
+    theme(axis.title = element_text(size = 14),
+          axis.text = element_text(size = 13),
+          legend.text = element_text(size = 13),
+          legend.title = element_text(size = 14))
+```
+
+```{r, fig.width = 10, fig.height = 6}
+Legend.met<- get_legend(SP.rain+ theme(legend.position = 'right'))
+
+Fig1 <- plot_grid(SP.rain + theme(legend.position="none"), TA+ theme(legend.position="none"),
+             SWC+ theme(legend.position="none"), TS+ theme(legend.position="none"), ncol = 2, rel_heights = c(0.5, 0.5, 0.5, 0.5))
+
+Fig1
+tiff("Fig1.tiff", units="in", width=10, height=6,  res=300)
+print(Fig1)
+dev.off()
+
+Legend.met
 ```
@@
 ```
-
-```{r timeseries analysis}
-tsData <- EuStockMarkets[, 1] # ts data
-decomposedRes <- decompose(tsData, type="mult") # use type = "additive" for additive components
-plot (decomposedRes) # see plot below
-stlRes <- stl(tsData, s.window = "periodic")
-
-input.daily %>% anova_test(NEE_LT.gC~Precip+season)
-
-rainfall$TS <- as.Date(with(rainfall, paste(Year, month, jday,sep="-")), "%Y-%m-%d")
-
-TSData <- rainfall[, 1] # ts data
-decomposedRes <- decompose(tsData, type="mult") # use type = "additive" for additive components
-plot (decomposedRes) # see plot below
-stlRes <- stl(tsData, s.window = "periodic")
-```

### 2022-06-14 scripts/Paper 1.Rmd
update

@@
 
-cumulative.co2fluxes <- input %>%
-  drop_na(Timestamp) %>% # some NAs in the Timestamp for some reason. Need to look into
-  ddply(c("Year", "jday", "month", "season"), summarise,
-        Fco2 = gofC.f(mean(Fco2, na.rm = TRUE)),
-        ER = gofC.f(mean(ER_SOLO, na.rm = TRUE)),
-        GPP = gofC.f(mean(GPP_SOLO, na.rm = TRUE)))
+cum.co2fluxes <- input.daily %>%
+  ddply(c("Year", "jday", "month"), summarise,
+        Fco2 = gofC.f(mean(NEE_LT.gC, na.rm = TRUE)),
+        ER = gofC.f(mean(ER_LT.gC, na.rm = TRUE)),
+        GPP = gofC.f(mean(GPP_LT.gC, na.rm = TRUE)))
 

### 2022-06-14 scripts/Paper 1.Rmd
update

@@
 rm(list = ls())
-wd <- ("R:/SET/PlantSci/Shared Work Spaces/Ecology/Flux/SP_data")
-setwd(wd)
-knitr::opts_knit$set(root.dir = wd)
+#wd <- ("R:/SET/PlantSci/Shared Work Spaces/Ecology/Flux/SP_data")
+#setwd(wd)
+#knitr::opts_knit$set(root.dir = wd)
 ```
@@
 ```{r read data and some data class cleaning, include=FALSE}
-input <- fread("./PFP/L6/SilverPlains_L6.csv", header = FALSE, na.strings = "-9999") 
+input <- fread("R:/SET/PlantSci/Shared Work Spaces/Ecology/Flux/SP_data/PFP/L6/SilverPlains_L6.csv", header = FALSE, na.strings = "-9999") 
 input <- tidy.csv(input)
@@
         Precip = sum(Precip, na.rm = TRUE),
+        SWin = sum(SWin),
         Ta.mean = mean(Ta, na.rm = TRUE),
@@
 ```{r Precipitation, echo=FALSE, message = FALSE, fig.width = 8, fig.height = 4}
-
 (SP.rain <- input.daily %>% mutate(Precip = replace_na(Precip, 0)) %>%
@@
 rainfall_L <- rainfall_L[-4]
-colnames(rainfall_L)[5] <- "Precip"
+colnames(rainfall_L)[4] <- "Precip"
 rainfall_L$Year <- as.factor(rainfall_L$Year)
@@
 rainfall_L <- rainfall_L %>% filter(month >= 9)
+rainfall_L$month <- as.numeric(rainfall_L$month) 
+rainfall_L$month<- month.abb[rainfall_L$month]
 
@@
 rainfall <- rbind(rainfall_L, rainfall.SP)
-rainfall$month <- as.numeric(rainfall$month) 
-rainfall$month.abb <- month.abb[rainfall$month]
 
@@
 
-input.co2fluxes$GPP <- ifelse(input.co2fluxes$GPP < 0 , NA, input.co2fluxes$GPP) # for some reason there were values < 0 for GPP
-
-input.co2fluxes$ERcum_year <- as.numeric(unlist(tapply(input.co2fluxes$ER, input.co2fluxes$Year, cumsum)))
-input.co2fluxes$NEEcum_year <- as.numeric(unlist(tapply(input.co2fluxes$Fco2, input.co2fluxes$Year, cumsum)))
-input.co2fluxes$GPPcum_year <- as.numeric(unlist(tapply(input.co2fluxes$GPP, input.co2fluxes$Year, cumsum)))
-
-input.co2fluxes$GPP<- ifelse(is.na(input.co2fluxes$GPP), "0", input.co2fluxes$GPP) # replace NA with 0 for cumsum
-
-(NEE <- plot_ly(input.co2fluxes, x = ~jday, y = ~NEEcum_year, split = ~Year, name = ~Year, type = 'scatter', mode = 'lines'))
-
-(ER <- plot_ly(input.co2fluxes, x = ~jday, y = ~ERcum_year, split = ~Year, name = ~Year, type = 'scatter', mode = 'lines'))
-
-(GPP <- plot_ly(input.co2fluxes, x = ~jday, y = ~GPPcum_year, split = ~Year, name = ~Year, type = 'scatter', mode = 'lines'))
-
 ```

### 2022-06-14 scripts/Paper 1.Rmd

@@
 rainfall.SP$Site <- "SP"
-
 rainfall <- rbind(rainfall_L, rainfall.SP)
@@
           legend.title = element_text(size = 14))
+
+rainfall <- rbind.fill(rainfall.2merge, rainfall.SP)
+rainfall$month <- as.factor(rainfall$month)
 
@@
 ```{r seasonal NEE}
-NEE.summary <- input.daily %>% ddply(c("month", "Year"), summarise,
+NEE.summary <- input.daily %>% ddply(c("Year", "month"), summarise,
                                        monthly.sum = sum(NEE_LT.gC))
+
+GPP.summary <- input.daily %>% ddply(c("Year", "month"), summarise,
+                                       monthly.sum = sum(GPP_LT.gC))
+
+ER.summary <- input.daily %>% ddply(c("Year", "month"), summarise,
+                                       monthly.sum = sum(ER_LT.gC))
+
+Ts.summary <- input.daily %>% ddply(c("Year", "month"), summarise,
+                                       monthly.mean = mean(Ts.mean))
 
@@
 
-input.daily %>% select(jday, NEE_LT.gC, Year) %>%
-  ggplot(., aes(jday, NEE_LT.gC)) +
-  geom_line(aes(colour = Year))
+GPP.summary %>%
+  ggplot(., aes(x = month, y = monthly.sum, group = Year, fill = Site)) +
+  geom_col(position = "dodge", aes(fill = Year)) + 
+  ylab("Monthly GPP")+
+  xlab("month")+
+  theme_classic()
 
+ER.summary %>%
+  ggplot(., aes(x = month, y = monthly.sum, group = Year, fill = Site)) +
+  geom_col(position = "dodge", aes(fill = Year)) + 
+  ylab("Monthly ER")+
+  xlab("month")+
+  theme_classic()
+
+Ts.summary %>%
+  ggplot(., aes(x = month, y = monthly.mean, group = Year, fill = Site)) +
+  geom_col(position = "dodge", aes(fill = Year)) + 
+  ylab("Monthly ER")+
+  xlab("month")+
+  theme_classic()
 ```
@@
 ```{r cumulative fluxes}
-
 cum.co2fluxes <- input.daily %>%
-  ddply(c("Year", "jday", "month"), summarise,
-        Fco2 = gofC.f(mean(NEE_LT.gC, na.rm = TRUE)),
-        ER = gofC.f(mean(ER_LT.gC, na.rm = TRUE)),
-        GPP = gofC.f(mean(GPP_LT.gC, na.rm = TRUE)))
-
+  select(NEE_LT.gC, GPP_LT.gC, ER_LT.gC, jday, Year, month)
 ```

### 2022-06-14 scripts/Paper 1.Rmd
u

@@
 
-rainfall <- rbind.fill(rainfall.2merge, rainfall.SP)
-rainfall$month <- as.factor(rainfall$month)
-
 ```
@@
 ```{r, echo=FALSE, message = FALSE, fig.width = 8, fig.height = 4}
-SWC <- ggplot(input.daily, aes(jday, SWC, group = Year)) +
+(SWC <- ggplot(input.daily, aes(jday, SWC, group = Year)) +
   geom_line(aes(color = Year), size = 1.5)+
@@
           legend.text = element_text(size = 13),
-          legend.title = element_text(size = 14))
+          legend.title = element_text(size = 14)))
 ```
@@
   geom_col(position = "dodge", aes(fill = Year)) + 
+         scale_x_discrete(limits = month.abb) +
+
   ylab("Monthly NEE")+
@@
 
-```{r cumulative fluxes}
+```{r cumulative fluxes, fig.width = 10, fig.height = 6}
 cum.co2fluxes <- input.daily %>%
-  select(NEE_LT.gC, GPP_LT.gC, ER_LT.gC, jday, Year, month)
+  select(NEE_LT.gC, GPP_LT.gC, ER_LT.gC, jday, Year, month) %>% 
+  group_by(Year) %>% 
+  mutate(NEEcum = cumsum(NEE_LT.gC),
+         GPPcum = cumsum(GPP_LT.gC),
+         ERcum = cumsum(ER_LT.gC))
+
+(NEEcum.p <-cum.co2fluxes %>% 
+  ggplot(., aes(jday, NEEcum, color = Year)) +
+  geom_line(size = 1)+
+  ylab(bquote('Cumulative NEE (g C' ~m^-2~')'))+
+  xlab("Julian day of year")+
+  theme_classic()+ 
+    theme(axis.title = element_text(size = 14),
+          axis.text = element_text(size = 13),
+          legend.position = "none"))
+
+(NEE.time <- input.daily %>% 
+  ggplot(., aes(jday, NEE_LT.gC, color = Year)) +
+  geom_line(size = 1)+
+  ylab(bquote('Cumulative NEE (g C' ~m^-2~ day^-1*')'))+
+  xlab("Julian day of year")+
+  theme_classic()+ 
+    theme(axis.title = element_text(size = 14),
+          axis.text = element_text(size = 13),
+          legend.position = "none"))
+
+(NEE.bar <- NEE.summary %>% 
+  ggplot(., aes(x = month, y = monthly.sum, group = Year, fill = Site)) +
+  geom_col(position = "dodge", aes(fill = Year)) + 
+         scale_x_discrete(limits = month.abb) +
+  ylab(bquote('Total monthly NEE (g C' ~m^-2~')'))+
+  xlab("Month")+
+  theme_classic() + 
+    theme(axis.title = element_text(size = 14),
+          axis.text = element_text(size = 13),
+          legend.position = "none"))
+
+(GPPcum.p <-cum.co2fluxes %>% 
+  ggplot(., aes(jday, GPPcum, color = Year)) +
+  geom_line(size = 1)+
+  ylab(bquote('Cumulative GPP (g C' ~m^-2~')'))+
+  xlab("Julian day of year")+
+  theme_classic()+ 
+    theme(axis.title = element_text(size = 14),
+          axis.text = element_text(size = 13),
+          legend.position = "none"))
+
+(ERcum.p <-cum.co2fluxes %>% 
+  ggplot(., aes(jday, ERcum, color = Year)) +
+  geom_line(size =1)+
+  ylab(bquote('Cumulative ER (g C' ~m^-2~')'))+
+  xlab("Julian day of year")+
+  theme_classic()+ 
+    theme(axis.title = element_text(size = 14),
+          axis.text = element_text(size = 13),
+          legend.position = "none"))
+
+Fig2 <- plot_grid(NEE.bar, NEEcum.p,
+             GPPcum.p, ERcum.p, ncol = 2, rel_heights = c(0.5, 0.5, 0.5, 0.5))
+
+Fig2
+tiff("Fig2.tiff", units="in", width=10, height=6,  res=300)
+print(Fig2)
+dev.off()
+
 ```

### 2022-06-15 scripts/Paper 1.Rmd
add days since jul1

@@
 
+input.daily$dayssinceJul1 <- ""
+
+Grow19.20 <- input.daily[1:194,]
+Grow19.20$dayssinceJul1 <- 1:194
+
+Grow20.21 <- input.daily[195:559,]
+Grow20.21$dayssinceJul1 <- 1:365
+
+Grow21.22 <- input.daily[560:907,]
+Grow21.22$dayssinceJul1 <-1:348
+
+input.rearranged <- rbind(Grow19.20,Grow20.21, Grow21.22)
 ```
@@
 rainfall_L$Site <- "L"
-rainfall_L <- rainfall_L %>% filter(month >= 9)
+rainfall_L <- rainfall_L %>% filter(month >= 5)
 rainfall_L$month <- as.numeric(rainfall_L$month) 
@@
 # define seasons
-winter <- (rainfall$month == "6" | rainfall$month == "7" | rainfall$month == "8")
-spring <- (rainfall$month == "9" | rainfall$month == "10" | rainfall$month == "11")
-earlysummer <- (rainfall$month == "12")
-latesummer <- (rainfall$month == "1" | rainfall$month == "2")
-autumn <- (rainfall$month == "3" | rainfall$month == "4" | rainfall$month == "5")
+winter <- (rainfall$month == "Jun" | rainfall$month == "Jul" | rainfall$month == "Aug")
+spring <- (rainfall$month == "Sep" | rainfall$month == "Oct" | rainfall$month == "Nov")
+earlysummer <- (rainfall$month == "Dec")
+latesummer <- (rainfall$month == "Jan" | rainfall$month == "Feb")
+autumn <- (rainfall$month == "Mar" | rainfall$month == "Apr" | rainfall$month == "May")
 
@@
 
-rainfall%>% ddply(c("Year", "season"), summarise,
+Seasonal.rain <- rainfall%>% filter(Year == 2020 | Year == 2021 | Year == 2022) %>% ddply(c("Year", "season"), summarise,
                     seasonal.sum = sum(Precip, na.rm = TRUE))
 
-rainfall.summary %>% 
-  ggplot(., aes(x = month, y = monthly.sum, group = Year, fill = Site)) +
-  geom_col(position = "dodge", aes(fill = Year)) + 
-  ylab("Monthly rainfall (mm)")+
-  xlab("month")+
-  theme_classic()
+rain.aov <- aov(seasonal.sum~Year*season, data =Seasonal.rain)
+summary(rain.aov)
+
+TukeyHSD(rain.aov)
 ```

### 2022-06-15 scripts/Paper 1.Rmd
seasonal rainfall

@@
 Grow19.20 <- input.daily[1:194,]
-Grow19.20$dayssinceJul1 <- 1:194
+Grow19.20$dayssinceJul1 <- 173:366
+Grow19.20$GSYear <- "19/20"
 
@@
 Grow20.21$dayssinceJul1 <- 1:365
+Grow20.21$GSYear <- "20/21"
 
@@
 Grow21.22$dayssinceJul1 <-1:348
+Grow21.22$GSYear <- "21/22"
 
@@
 rainfall_L$Site <- "L"
-rainfall_L <- rainfall_L %>% filter(month >= 5)
+rainfall_L <- rainfall_L %>% filter(month >= 6)
 rainfall_L$month <- as.numeric(rainfall_L$month) 
 rainfall_L$month<- month.abb[rainfall_L$month]
+rainfall_L$GSYear <- "19/20"
+
+input.rearranged$season <- "" # add season variable
+
+# define seasons
+winter <- (rainfall_L$month == "Jun" | rainfall_L$month == "Jul" | rainfall_L$month == "Aug")
+spring <- (rainfall_L$month == "Sep" | rainfall_L$month == "Oct" | rainfall_L$month == "Nov")
+earlysummer <- (rainfall_L$month == "Dec")
+latesummer <- (rainfall_L$month == "Jan" | rainfall_L$month == "Feb")
+autumn <- (rainfall_L$month == "Mar" | rainfall_L$month == "Apr" | rainfall_L$month == "May")
+
+rainfall_L$season[winter] <- "Winter"
+rainfall_L$season[spring] <- "Spring"
+rainfall_L$season[earlysummer] <- "EarlySummer"
+rainfall_L$season[latesummer] <- "LateSummer"
+rainfall_L$season[autumn] <- "Autumn"
+
+rainfall_L$season <- factor(rainfall_L$season , levels=c('EarlySummer','LateSummer', 'Autumn', 'Winter', 'Spring'))
 
@@
 rainfall$season <- factor(rainfall$season , levels=c('EarlySummer','LateSummer', 'Autumn', 'Winter', 'Spring'))
-
-input.daily$season <- "" # add season variable
-
-# define seasons
-winter <- (input.daily$month == "6" | input.daily$month == "7" | input.daily$month == "8")
-spring <- (input.daily$month == "9" | input.daily$month == "10" | input.daily$month == "11")
-earlysummer <- (input.daily$month == "12")
-latesummer <- (input.daily$month == "1" | input.daily$month == "2")
-autumn <- (input.daily$month == "3" | input.daily$month == "4" | input.daily$month == "5")
-
-input.daily$season[winter] <- "Winter"
-input.daily$season[spring] <- "Spring"
-input.daily$season[earlysummer] <- "EarlySummer"
-input.daily$season[latesummer] <- "LateSummer"
-input.daily$season[autumn] <- "Autumn"
-
-input.daily$season <- factor(input.daily$season , levels=c('EarlySummer','LateSummer', 'Autumn', 'Winter', 'Spring'))
-```
-
-```{r create rainfall summary}
-rainfall.summary <- rainfall %>% ddply(c("Year", "Site", "month"), summarise,
-                                       monthly.sum = sum(Precip, na.rm = TRUE))
-
-Seasonal.rain <- rainfall%>% filter(Year == 2020 | Year == 2021 | Year == 2022) %>% ddply(c("Year", "season"), summarise,
-                    seasonal.sum = sum(Precip, na.rm = TRUE))
-
-rain.aov <- aov(seasonal.sum~Year*season, data =Seasonal.rain)
-summary(rain.aov)
-
-TukeyHSD(rain.aov)
 ```
@@
 ```{r cumulative fluxes, fig.width = 10, fig.height = 6}
-cum.co2fluxes <- input.daily %>%
-  select(NEE_LT.gC, GPP_LT.gC, ER_LT.gC, jday, Year, month) %>% 
-  group_by(Year) %>% 
+cum.co2fluxes <- input.rearranged %>% #input.daily %>%
+  select(NEE_LT.gC, GPP_LT.gC, ER_LT.gC, dayssinceJul1, GSYear) %>% 
+  group_by(GSYear) %>% 
   mutate(NEEcum = cumsum(NEE_LT.gC),
@@
 (NEEcum.p <-cum.co2fluxes %>% 
-  ggplot(., aes(jday, NEEcum, color = Year)) +
+  ggplot(., aes(dayssinceJul1, NEEcum, color = GSYear)) +
   geom_line(size = 1)+
   ylab(bquote('Cumulative NEE (g C' ~m^-2~')'))+
-  xlab("Julian day of year")+
+  xlab("Days since July 1st")+
   theme_classic()+ 
     theme(axis.title = element_text(size = 14),
-          axis.text = element_text(size = 13),
-          legend.position = "none"))
+          axis.text = element_text(size = 13)))
 
@@
   ylab(bquote('Cumulative NEE (g C' ~m^-2~ day^-1*')'))+
-  xlab("Julian day of year")+
+  xlab("Days since July 1st")+
   theme_classic()+ 
@@
 (GPPcum.p <-cum.co2fluxes %>% 
-  ggplot(., aes(jday, GPPcum, color = Year)) +
+  ggplot(., aes(dayssinceJul1, GPPcum, color = GSYear)) +
   geom_line(size = 1)+
   ylab(bquote('Cumulative GPP (g C' ~m^-2~')'))+
-  xlab("Julian day of year")+
+  xlab("Days since July 1st")+
   theme_classic()+ 
     theme(axis.title = element_text(size = 14),
-          axis.text = element_text(size = 13),
-          legend.position = "none"))
+          axis.text = element_text(size = 13)))
 
 (ERcum.p <-cum.co2fluxes %>% 
-  ggplot(., aes(jday, ERcum, color = Year)) +
+  ggplot(., aes(dayssinceJul1, ERcum, color = GSYear)) +
   geom_line(size =1)+
   ylab(bquote('Cumulative ER (g C' ~m^-2~')'))+
-  xlab("Julian day of year")+
+  xlab("Days since July 1st")+
   theme_classic()+ 
     theme(axis.title = element_text(size = 14),
-          axis.text = element_text(size = 13),
-          legend.position = "none"))
+          axis.text = element_text(size = 13)))
 
@@
 ```
+
+```{r}
+input.rearranged$season <- "" # add season variable
+
+# define seasons
+winter <- (input.rearranged$month == "Jun" | input.rearranged$month == "Jul" | input.rearranged$month == "Aug")
+spring <- (input.rearranged$month == "Sep" | input.rearranged$month == "Oct" | input.rearranged$month == "Nov")
+earlysummer <- (input.rearranged$month == "Dec")
+latesummer <- (input.rearranged$month == "Jan" | input.rearranged$month == "Feb")
+autumn <- (input.rearranged$month == "Mar" | input.rearranged$month == "Apr" | input.rearranged$month == "May")
+
+input.rearranged$season[winter] <- "Winter"
+input.rearranged$season[spring] <- "Spring"
+input.rearranged$season[earlysummer] <- "EarlySummer"
+input.rearranged$season[latesummer] <- "LateSummer"
+input.rearranged$season[autumn] <- "Autumn"
+
+input.rearranged$season <- factor(input.rearranged$season , levels=c('EarlySummer','LateSummer', 'Autumn', 'Winter', 'Spring'))
+```
+
+```{r}
+rainfall.SP <- input.rearranged %>% select(Precip, month, GSYear, season)
+
+rainfall <- rainfall_L %>% select(Precip, month, GSYear, season) %>% rbind(., rainfall.SP)
+
+rainfall %>%  mutate(Precip = replace_na(Precip, 0)) %>%
+  ddply(c("GSYear", "season"), summarise,
+  seasonal.total = sum(Precip)) %>%
+  ggplot(., aes(x = GSYear, y = seasonal.total, group = GSYear, fill = season)) +
+       #scale_x_discrete(limits = month.abb) +
+  geom_col() + 
+  ylab("Seasonal rainfall (mm)")+
+  xlab("Month")+
+  theme_classic()+
+    theme(axis.title = element_text(size = 14),
+          axis.text = element_text(size = 13),
+          legend.text = element_text(size = 13),
+          legend.title = element_text(size = 14))
+```

### 2022-06-15 scripts/Paper 1.Rmd
SWC plot amend

@@
 library(cowplot)
+library(viridis)
+library(zoo)
 
@@
 input.daily$month <- as.numeric(input.daily$month) 
-input.daily$month <- month.abb[input.daily$month]
+input.daily$month.name <- month.abb[input.daily$month]
+input.daily$date <- as.Date(with(input.daily,paste(Year,month,jday,sep="-")),"%Y-%m-%j")
 
@@
 input.rearranged <- rbind(Grow19.20,Grow20.21, Grow21.22)
+input.rearranged$monthyear <- as.yearmon(paste(input.rearranged$month, input.rearranged$Year), "%m %Y")
+
+start.time <- as.Date("07-01", "%m-%d")
+end.time <- as.Date("06-30", "%m-%d")
+start.end <- c(start.time, end.time)
 ```
@@
 ```{r Precipitation, echo=FALSE, message = FALSE, fig.width = 8, fig.height = 4}
-(SP.rain <- input.daily %>% mutate(Precip = replace_na(Precip, 0)) %>%
-  ddply(c("Year", "month"), summarise,
-  monthly.total = sum(Precip)) %>%
-  ggplot(., aes(x = month, y = monthly.total, group = Year, fill = Year)) +
-       #scale_x_discrete(limits = month.abb) +
-  geom_col(position = "dodge") + 
-  ylab("Monthly rainfall (mm)")+
-  xlab("Month")+
-   scale_x_discrete(limits = month.abb) +
-  theme_classic()+
-  theme(axis.title = element_text(size = 14),
-          axis.text = element_text(size = 13),
-          legend.text = element_text(size = 13),
-          legend.title = element_text(size = 14)))
-
 #below is precip data from liaweenee - it only goes up to Jan 2022 right now
@@
 rainfall_L$Site <- "L"
-rainfall_L <- rainfall_L %>% filter(month >= 6)
+rainfall_L <- rainfall_L %>% filter(month >= 7)
 rainfall_L$month <- as.numeric(rainfall_L$month) 
-rainfall_L$month<- month.abb[rainfall_L$month]
+rainfall_L$month.name<- month.abb[rainfall_L$month]
 rainfall_L$GSYear <- "19/20"
@@
 # define seasons
-winter <- (rainfall_L$month == "Jun" | rainfall_L$month == "Jul" | rainfall_L$month == "Aug")
-spring <- (rainfall_L$month == "Sep" | rainfall_L$month == "Oct" | rainfall_L$month == "Nov")
-earlysummer <- (rainfall_L$month == "Dec")
-latesummer <- (rainfall_L$month == "Jan" | rainfall_L$month == "Feb")
-autumn <- (rainfall_L$month == "Mar" | rainfall_L$month == "Apr" | rainfall_L$month == "May")
+winter <- (rainfall_L$month.name == "Jun" | rainfall_L$month.name == "Jul" | rainfall_L$month.name == "Aug")
+spring <- (rainfall_L$month.name == "Sep" | rainfall_L$month.name == "Oct" | rainfall_L$month.name == "Nov")
+summer <- (rainfall_L$month.name == "Dec" | rainfall_L$month.name == "Jan" | rainfall_L$month.name == "Feb")
+autumn <- (rainfall_L$month.name == "Mar" | rainfall_L$month.name == "Apr" | rainfall_L$month.name == "May")
 
@@
 rainfall_L$season[spring] <- "Spring"
-rainfall_L$season[earlysummer] <- "EarlySummer"
-rainfall_L$season[latesummer] <- "LateSummer"
+rainfall_L$season[summer] <- "Summer"
 rainfall_L$season[autumn] <- "Autumn"
 
-rainfall_L$season <- factor(rainfall_L$season , levels=c('EarlySummer','LateSummer', 'Autumn', 'Winter', 'Spring'))
-
-rainfall_L %>% mutate(Precip = replace_na(Precip, 0)) %>%
-  ddply(c("Year", "month"), summarise,
-  monthly.total = sum(Precip)) %>%
-  ggplot(., aes(x = month, y = monthly.total, group = Year, fill = Year)) +
-       scale_x_discrete(limits = month.abb) +
-  geom_col(position = "dodge") + 
-  ylab("Monthly rainfall (mm)")+
-  xlab("month")+
-  theme_classic()
-
-rainfall.SP <- input.daily %>% select(Precip, jday, month, Year)
-rainfall.SP$Site <- "SP"
-rainfall <- rbind(rainfall_L, rainfall.SP)
-
-rainfall %>%  mutate(Precip = replace_na(Precip, 0)) %>%
-  ddply(c("Year", "month"), summarise,
-  monthly.total = sum(Precip)) %>%
-  ggplot(., aes(x = month, y = monthly.total, group = Year, fill = Year)) +
-       scale_x_discrete(limits = month.abb) +
-  geom_col(position = "dodge") + 
-  ylab("Monthly rainfall (mm)")+
-  xlab("Month")+
-  theme_classic()+
-    theme(axis.title = element_text(size = 14),
-          axis.text = element_text(size = 13),
-          legend.text = element_text(size = 13),
-          legend.title = element_text(size = 14))
-
+rainfall_L$season <- factor(rainfall_L$season , levels=c('Summer', 'Autumn', 'Winter', 'Spring'))
 ```
 
-### Air and soil temperature
+```{r, fig.width=11, fig.height=4}
+rainfall.SP <- input.rearranged %>% select(Precip, month, GSYear, season, Year, month.name)
 
-Mean daily air temperature (top) and monthly (bottom)
-Mean daily air temperature
+rainfall <- rainfall_L %>% select(Precip, month, GSYear, season, Year, month.name) %>% rbind(., rainfall.SP)
 
-```{r Air temperature, echo=FALSE, message = FALSE, fig.width = 8, fig.height = 4}
-TA <- ggplot(input.daily, aes(x = jday, y = Ta.mean, group = Year)) +
-  geom_line(aes(color = Year), size =1)+
-    xlab("Julian day of year")+
-    ylab("Air temperature (°C)")+
-     #geom_ribbon(aes(ymin=Ta.min, ymax=Ta.max), alpha=.3, linetype=0) +
-  theme_classic()+
-    theme(axis.title = element_text(size = 14),
-          axis.text = element_text(size = 13),
-          legend.text = element_text(size = 13),
-          legend.title = element_text(size = 14))
+rainfall$monthyear <- as.yearmon(paste(rainfall$month, rainfall$Year), "%m %Y")
 
-(TS <- ggplot(input.daily, aes(x = jday, y = Ts.mean, group = Year)) +
-  geom_line(aes(color = Year), size =1)+
-    xlab("Julian day of year")+
-    ylab("Soil temperature (°C)")+
-     #geom_ribbon(aes(ymin=Ta.min, ymax=Ta.max), alpha=.3, linetype=0) +
+(rain <- rainfall %>%  mutate(Precip = replace_na(Precip, 0)) %>%
+  ddply(c("GSYear", "season"), summarise,
+  seasonal.total = sum(Precip)) %>%
+  ggplot(., aes(x = GSYear, y = seasonal.total, group = GSYear, fill = season)) +
+       #scale_x_discrete(limits = month.abb) +
+  geom_col() + 
+  ylab("Seasonal rainfall (mm)")+
+  xlab("Growing season year")+
   theme_classic()+
@@
 
-ggplotly(ggplot(input.daily, aes(x = jday, y = Ta.max, group = Year)) +
-  geom_line(aes(color = Year))+
-  theme_classic())
+(rainfall.p <-rainfall %>%  mutate(Precip = replace_na(Precip, 0)) %>%
+  ddply(c("monthyear", "Year"), summarise,
+  monthly.total = sum(Precip)) %>%
+  ggplot(., aes(x = monthyear, y = monthly.total)) +
+  geom_col(position = "dodge") +
+  scale_x_yearmon(n = 7, expand = c(0,0))+
+  ylab("Monthly rainfall (mm)")+
+  xlab("Date")+
+  theme_classic()+
+    theme(axis.title = element_text(size = 14),
+          axis.text = element_text(size = 13),
+          legend.text = element_text(size = 13),
+          legend.title = element_text(size = 14),
+          axis.text.x = element_text( vjust = 0.5)))
+rainfall.p
+tiff("rainfall.tiff", units="in", width=10, height=6,  res=300)
+print(rainfall.p)
+dev.off()
 
-ggplotly(ggplot(input.daily, aes(x = jday, y = Ta.min, group = Year)) +
-  geom_line(aes(color = Year))+
-  theme_classic())
+```
+
+### Air and soil temperature
+
+```{r Air temperature, echo=FALSE, message = FALSE, fig.width = 11, fig.height = 4}
+(TA <- ggplot(input.rearranged, aes(x = date, y = Ta.mean)) +
+   geom_point(size = 0.001)+
+   geom_line(size = 0.72)+
+        geom_ribbon(aes(ymin=Ta.min, ymax=Ta.max), alpha=.3, linetype=0) +
+    xlab("Date")+
+    ylab("Air temperature (°C)")+
+  theme_classic()+
+    theme(axis.title = element_text(size = 14),
+          axis.text = element_text(size = 13),
+          legend.text = element_text(size = 13),
+          legend.title = element_text(size = 14)))
+
+(TS <- ggplot(input.rearranged, aes(x = date, y = Ts.mean)) +
+   geom_point(size = 0.001)+
+   geom_line(size = 0.72)+
+        geom_ribbon(aes(ymin=Ts.min, ymax=Ts.max), alpha=.3, linetype=0) +
+    xlab("Date")+
+    ylab("Soil temperature (°C)")+
+  theme_classic()+
+    theme(axis.title = element_text(size = 14),
+          axis.text = element_text(size = 13),
+          legend.text = element_text(size = 13),
+          legend.title = element_text(size = 14)))
+
+TA
+tiff("TA.tiff", units="in", width=10, height=6,  res=300)
+print(TA)
+dev.off()
+
+TS
+tiff("TS.tiff", units="in", width=10, height=6,  res=300)
+print(TS)
+dev.off()
 ```
@@
 
-```{r, echo=FALSE, message = FALSE, fig.width = 8, fig.height = 4}
-(SWC <- ggplot(input.daily, aes(jday, SWC, group = Year)) +
-  geom_line(aes(color = Year), size = 1.5)+
-  xlab('Julian day of year') +
+```{r, echo=FALSE, message = FALSE, fig.width = 7, fig.height = 4}
+group.colors <- c("19/20" = "#333BFF", "20/21" = "#CC6600", "21/22" ="#9633FF")
+
+(SWC.20 <- input.rearranged %>% filter (GSYear == "19/20"| GSYear == "20/21" | GSYear == "21/22" ) %>% ggplot(., aes(x = as.Date(dayssinceJul1, origin = as.Date("07-01", "%m-%d")), SWC, group = GSYear)) +
+  geom_line(aes(color = GSYear), size = 1.5)+
+  # scale_x_continuous(limits = c(0, 365))+
+  xlab('Month') +
   ylab('SWC %') +
+   scale_x_date(breaks = "month", date_labels = "%b", limits = as.Date(c("07-01", "06-31"), "%m-%d"))+
+    scale_color_manual(values = group.colors)+
   theme_classic() + 
@@
           legend.title = element_text(size = 14)))
+
+SWC.20
+tiff("SWC22.tiff", units="in", width=10, height=6,  res=300)
+print(SWC.20)
+dev.off()
 ```
@@
 
-Fig1 <- plot_grid(SP.rain + theme(legend.position="none"), TA+ theme(legend.position="none"),
-             SWC+ theme(legend.position="none"), TS+ theme(legend.position="none"), ncol = 2, rel_heights = c(0.5, 0.5, 0.5, 0.5))
+Fig1 <- plot_grid(rainfall.p + theme(legend.position="none"), TA+ theme(legend.position="none"),
+             SWC.20+ theme(legend.position="none"), TS+ theme(legend.position="none"), ncol = 2, rel_heights = c(0.5, 0.5, 0.5, 0.5))
 
@@
 ```{r add seasons, include=FALSE}
-rainfall$season <- "" # add season variable
+#rainfall$season <- "" # add season variable
 
 # define seasons
-winter <- (rainfall$month == "Jun" | rainfall$month == "Jul" | rainfall$month == "Aug")
-spring <- (rainfall$month == "Sep" | rainfall$month == "Oct" | rainfall$month == "Nov")
-earlysummer <- (rainfall$month == "Dec")
-latesummer <- (rainfall$month == "Jan" | rainfall$month == "Feb")
-autumn <- (rainfall$month == "Mar" | rainfall$month == "Apr" | rainfall$month == "May")
+#winter <- (rainfall$month == "Jun" | rainfall$month == "Jul" | rainfall$month == "Aug")
+#spring <- (rainfall$month == "Sep" | rainfall$month == "Oct" | rainfall$month == "Nov")
+#summer <- (rainfall$month == "Dec" | rainfall$month == "Jan" | rainfall$month == "Feb")
+#autumn <- (rainfall$month == "Mar" | rainfall$month == "Apr" | rainfall$month == "May")
 
-rainfall$season[winter] <- "Winter"
-rainfall$season[spring] <- "Spring"
-rainfall$season[earlysummer] <- "EarlySummer"
-rainfall$season[latesummer] <- "LateSummer"
-rainfall$season[autumn] <- "Autumn"
+#rainfall$season[winter] <- "Winter"
+#rainfall$season[spring] <- "Spring"
+#rainfall$season[summer] <- "Summer"
+#rainfall$season[earlysummer] <- "EarlySummer"
+#rainfall$season[latesummer] <- "LateSummer"
+#rainfall$season[autumn] <- "Autumn"
 
-rainfall$season <- factor(rainfall$season , levels=c('EarlySummer','LateSummer', 'Autumn', 'Winter', 'Spring'))
+#rainfall$season <- factor(rainfall$season , levels=c('Summer', 'Autumn', 'Winter', 'Spring'))
 ```
@@
 cum.co2fluxes <- input.rearranged %>% #input.daily %>%
-  select(NEE_LT.gC, GPP_LT.gC, ER_LT.gC, dayssinceJul1, GSYear) %>% 
+  select(NEE_LT.gC, GPP_LT.gC, ER_LT.gC, dayssinceJul1, GSYear, season) %>% 
   group_by(GSYear) %>% 
@@
 # define seasons
-winter <- (input.rearranged$month == "Jun" | input.rearranged$month == "Jul" | input.rearranged$month == "Aug")
-spring <- (input.rearranged$month == "Sep" | input.rearranged$month == "Oct" | input.rearranged$month == "Nov")
-earlysummer <- (input.rearranged$month == "Dec")
-latesummer <- (input.rearranged$month == "Jan" | input.rearranged$month == "Feb")
-autumn <- (input.rearranged$month == "Mar" | input.rearranged$month == "Apr" | input.rearranged$month == "May")
+winter <- (input.rearranged$month.name == "Jun" | input.rearranged$month.name == "Jul" | input.rearranged$month.name == "Aug")
+spring <- (input.rearranged$month.name == "Sep" | input.rearranged$month.name == "Oct" | input.rearranged$month.name == "Nov")
+summer <- (input.rearranged$month.name == "Dec" | input.rearranged$month.name == "Jan" | input.rearranged$month.name == "Feb")
+autumn <- (input.rearranged$month.name == "Mar" | input.rearranged$month.name == "Apr" | input.rearranged$month.name == "May")
 
@@
 input.rearranged$season[spring] <- "Spring"
-input.rearranged$season[earlysummer] <- "EarlySummer"
-input.rearranged$season[latesummer] <- "LateSummer"
+input.rearranged$season[summer] <- "Summer"
+#input.rearranged$season[latesummer] <- "LateSummer"
 input.rearranged$season[autumn] <- "Autumn"
 
-input.rearranged$season <- factor(input.rearranged$season , levels=c('EarlySummer','LateSummer', 'Autumn', 'Winter', 'Spring'))
+input.rearranged$season <- factor(input.rearranged$season , levels=c('Summer', 'Autumn', 'Winter', 'Spring'))
 ```
@@
 ```{r}
-rainfall.SP <- input.rearranged %>% select(Precip, month, GSYear, season)
-
-rainfall <- rainfall_L %>% select(Precip, month, GSYear, season) %>% rbind(., rainfall.SP)
-
-rainfall %>%  mutate(Precip = replace_na(Precip, 0)) %>%
+(GPPcum.p <-cum.co2fluxes %>% 
    ddply(c("GSYear", "season"), summarise,
-  seasonal.total = sum(Precip)) %>%
+  seasonal.total = cumsum(GPP_LT.gC)) %>%
    ggplot(., aes(x = GSYear, y = seasonal.total, group = GSYear, fill = season)) +
-       #scale_x_discrete(limits = month.abb) +
   geom_col() + 
-  ylab("Seasonal rainfall (mm)")+
-  xlab("Month")+
+  ylab("Total GPP")+
+  xlab("Growing season year")+
   theme_classic()+
@@
           legend.text = element_text(size = 13),
-          legend.title = element_text(size = 14))
+          legend.title = element_text(size = 14)))
+
+(ERcum.p <-cum.co2fluxes %>% 
+   ddply(c("GSYear", "season"), summarise,
+  seasonal.total = cumsum(ER_LT.gC)) %>%
+   ggplot(., aes(x = GSYear, y = seasonal.total, group = GSYear, fill = season)) +
+  geom_col() + 
+  ylab("Total ER")+
+  xlab("Growing season year")+
+  theme_classic()+
+    theme(axis.title = element_text(size = 14),
+          axis.text = element_text(size = 13),
+          legend.text = element_text(size = 13),
+          legend.title = element_text(size = 14)))
 ```
+
+```{r, fig.height=10, fig.width = 6}
+
+(Fig3 <- plot_grid(rain,
+             GPPcum.p, ERcum.p, nrow =3))
+
+```

### 2022-06-16 scripts/Paper 1.Rmd
boring x axis

@@
 
+```{r}
+input.daily$dayssinceJun1 <- ""
+
+Grow19.20 <- input.daily[1:164,]
+Grow19.20$dayssinceJun1 <- 202:365
+Grow19.20$GSYear <- "19/20"
+
+Grow20.21 <- input.daily[165:529,]
+Grow20.21$dayssinceJun1 <- 1:365
+Grow20.21$GSYear <- "20/21"
+
+Grow21.22 <- input.daily[530:907,]
+Grow21.22$dayssinceJun1 <-1:378
+Grow21.22$GSYear <- "21/22"
+
+input.rearranged <- rbind(Grow19.20,Grow20.21, Grow21.22)
+input.rearranged$monthyear <- as.yearmon(paste(input.rearranged$month, input.rearranged$Year), "%m %Y")
+
+start.time <- as.Date("06-01", "%m-%d")
+end.time <- as.Date("06-30", "%m-%d")
+start.end <- c(start.time, end.time)
+```
+
+```{r}
+input.rearranged$season <- "" # add season variable
+
+# define seasons
+winter <- (input.rearranged$month.name == "Jun" | input.rearranged$month.name == "Jul" | input.rearranged$month.name == "Aug")
+spring <- (input.rearranged$month.name == "Sep" | input.rearranged$month.name == "Oct" | input.rearranged$month.name == "Nov")
+summer <- (input.rearranged$month.name == "Dec" | input.rearranged$month.name == "Jan" | input.rearranged$month.name == "Feb")
+autumn <- (input.rearranged$month.name == "Mar" | input.rearranged$month.name == "Apr" | input.rearranged$month.name == "May")
+
+input.rearranged$season[winter] <- "Winter"
+input.rearranged$season[spring] <- "Spring"
+input.rearranged$season[summer] <- "Summer"
+#input.rearranged$season[latesummer] <- "LateSummer"
+input.rearranged$season[autumn] <- "Autumn"
+
+input.rearranged$season <- factor(input.rearranged$season , levels=c('Summer', 'Autumn', 'Winter', 'Spring'))
+```
+
 ## Results {.tabset}
@@
 rainfall_L$GSYear <- "19/20"
-
-input.rearranged$season <- "" # add season variable
 
@@
 
-(SWC.20 <- input.rearranged %>% filter (GSYear == "19/20"| GSYear == "20/21" | GSYear == "21/22" ) %>% ggplot(., aes(x = as.Date(dayssinceJul1, origin = as.Date("07-01", "%m-%d")), SWC, group = GSYear)) +
+(SWC.20 <- input.rearranged %>% filter (GSYear == "19/20" ) %>% ggplot(., aes(x = as.Date(dayssinceJun1, origin = as.Date("06-01", "%m-%d")), SWC, group = GSYear)) +
   geom_line(aes(color = GSYear), size = 1.5)+
@@
   ylab('SWC %') +
-   scale_x_date(breaks = "month", date_labels = "%b", limits = as.Date(c("07-01", "06-31"), "%m-%d"))+
+   scale_x_date(breaks = "month", date_labels = "%b", limits = as.Date(c("06-01", "05-31"), "%m-%d"))+
     scale_color_manual(values = group.colors)+
@@
 SWC.20
-tiff("SWC22.tiff", units="in", width=10, height=6,  res=300)
+tiff("SWC20.tiff", units="in", width=10, height=6,  res=300)
 print(SWC.20)
 dev.off()
-```
-
-```{r, fig.width = 10, fig.height = 6}
-Legend.met<- get_legend(SP.rain+ theme(legend.position = 'right'))
-
-Fig1 <- plot_grid(rainfall.p + theme(legend.position="none"), TA+ theme(legend.position="none"),
-             SWC.20+ theme(legend.position="none"), TS+ theme(legend.position="none"), ncol = 2, rel_heights = c(0.5, 0.5, 0.5, 0.5))
-
-Fig1
-tiff("Fig1.tiff", units="in", width=10, height=6,  res=300)
-print(Fig1)
-dev.off()
-
-Legend.met
 ```
@@
 ```{r seasonal NEE}
-NEE.summary <- input.daily %>% ddply(c("Year", "month"), summarise,
+NEE.summary <- input.rearranged %>% ddply(c("GSYear", "month.name"), summarise,
                                        monthly.sum = sum(NEE_LT.gC))
+NEE.summary$month.name <- factor(NEE.summary$month.name, levels=c("Jul", "Aug", "Sep", "Oct", "Nov", "Dec", "Jan", "Feb", "Mar", "Apr", "May", "Jun"))
 
-GPP.summary <- input.daily %>% ddply(c("Year", "month"), summarise,
-                                       monthly.sum = sum(GPP_LT.gC))
-
-ER.summary <- input.daily %>% ddply(c("Year", "month"), summarise,
-                                       monthly.sum = sum(ER_LT.gC))
-
-Ts.summary <- input.daily %>% ddply(c("Year", "month"), summarise,
-                                       monthly.mean = mean(Ts.mean))
-
-# check when switches from sink to source
-
-NEE.summary %>% 
-  ggplot(., aes(x = month, y = monthly.sum, group = Year, fill = Site)) +
-  geom_col(position = "dodge", aes(fill = Year)) + 
-         scale_x_discrete(limits = month.abb) +
-
+(NEE.bar <- NEE.summary  %>%
+  ggplot(., aes(x = month.name, y = monthly.sum, group = GSYear, fill = GSYear)) +
+  geom_col(position = "dodge", aes(fill = GSYear)) + 
+         #scale_x_discrete(limits = start.end)+
   ylab("Monthly NEE")+
   xlab("month")+
-  theme_classic()
+  theme_classic())
 
-GPP.summary %>%
-  ggplot(., aes(x = month, y = monthly.sum, group = Year, fill = Site)) +
-  geom_col(position = "dodge", aes(fill = Year)) + 
+NEE.bar
+tiff("NEEbar.tiff", units="in", width=10, height=6,  res=300)
+print(NEE.bar)
+dev.off()
+```
+
+```{r}
+GPP.summary <- input.rearranged %>% ddply(c("GSYear", "season"), summarise,
+                                       monthly.sum = sum(GPP_LT.gC))
+#GPP.summary$month.name <- factor(GPP.summary$month.name, levels=c("Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec", "Jan", "Feb", "Mar", #"Apr", "May"))
+
+(GPP.bar <- GPP.summary  %>%
+  ggplot(., aes(x = season, y = monthly.sum, group = GSYear, fill = GSYear)) +
+  geom_col(position = "dodge", aes(fill = GSYear)) + 
+         #scale_x_discrete(limits = start.end)+
   ylab("Monthly GPP")+
   xlab("month")+
-  theme_classic()
+  theme_classic())
+```
 
-ER.summary %>%
-  ggplot(., aes(x = month, y = monthly.sum, group = Year, fill = Site)) +
-  geom_col(position = "dodge", aes(fill = Year)) + 
+```{r}
+ER.summary <- input.rearranged %>% ddply(c("GSYear", "season"), summarise,
+                                       monthly.sum = sum(ER_LT.gC))
+#ER.summary$month.name <- factor(ER.summary$month.name, levels=c("Jul", "Aug", "Sep", "Oct", "Nov", "Dec", "Jan", "Feb", "Mar", "Apr", "May", "Jun"))
+
+(ER.bar <- ER.summary  %>%
+  ggplot(., aes(x = season, y = monthly.sum, group = GSYear, fill = GSYear)) +
+  geom_col(position = "dodge", aes(fill = GSYear)) + 
+         #scale_x_discrete(limits = start.end)+
   ylab("Monthly ER")+
   xlab("month")+
-  theme_classic()
-
-Ts.summary %>%
-  ggplot(., aes(x = month, y = monthly.mean, group = Year, fill = Site)) +
-  geom_col(position = "dodge", aes(fill = Year)) + 
-  ylab("Monthly ER")+
-  xlab("month")+
-  theme_classic()
+  theme_classic())
 ```
@@
 (NEEcum.p <-cum.co2fluxes %>% 
-  ggplot(., aes(dayssinceJul1, NEEcum, color = GSYear)) +
+  ggplot(., aes(x = as.Date(dayssinceJul1, origin = as.Date("07-01", "%m-%d")), NEEcum, color = GSYear)) +
   geom_line(size = 1)+
-  ylab(bquote('Cumulative NEE (g C' ~m^-2~')'))+
+  ylab(bquote('Cumulative NEE (g C ' ~m^-2~')'))+
   xlab("Days since July 1st")+
+       scale_x_date(breaks = "month", date_labels = "%b", limits = as.Date(c("07-01", "06-31"), "%m-%d"))+
   theme_classic()+ 
@@
 
-(NEE.time <- input.daily %>% 
-  ggplot(., aes(jday, NEE_LT.gC, color = Year)) +
-  geom_line(size = 1)+
-  ylab(bquote('Cumulative NEE (g C' ~m^-2~ day^-1*')'))+
-  xlab("Days since July 1st")+
-  theme_classic()+ 
-    theme(axis.title = element_text(size = 14),
-          axis.text = element_text(size = 13),
-          legend.position = "none"))
-
-(NEE.bar <- NEE.summary %>% 
-  ggplot(., aes(x = month, y = monthly.sum, group = Year, fill = Site)) +
-  geom_col(position = "dodge", aes(fill = Year)) + 
-         scale_x_discrete(limits = month.abb) +
-  ylab(bquote('Total monthly NEE (g C' ~m^-2~')'))+
-  xlab("Month")+
-  theme_classic() + 
-    theme(axis.title = element_text(size = 14),
-          axis.text = element_text(size = 13),
-          legend.position = "none"))
+NEEcum.p
+tiff("NEEcum.tiff", units="in", width=10, height=6,  res=300)
+print(NEEcum.p)
+dev.off()
 
@@
   geom_line(size = 1)+
-  ylab(bquote('Cumulative GPP (g C' ~m^-2~')'))+
+  ylab(bquote('Cumulative GPP (g C ' ~m^-2~')'))+
   xlab("Days since July 1st")+
@@
 ```{r}
-input.rearranged$season <- "" # add season variable
-
-# define seasons
-winter <- (input.rearranged$month.name == "Jun" | input.rearranged$month.name == "Jul" | input.rearranged$month.name == "Aug")
-spring <- (input.rearranged$month.name == "Sep" | input.rearranged$month.name == "Oct" | input.rearranged$month.name == "Nov")
-summer <- (input.rearranged$month.name == "Dec" | input.rearranged$month.name == "Jan" | input.rearranged$month.name == "Feb")
-autumn <- (input.rearranged$month.name == "Mar" | input.rearranged$month.name == "Apr" | input.rearranged$month.name == "May")
-
-input.rearranged$season[winter] <- "Winter"
-input.rearranged$season[spring] <- "Spring"
-input.rearranged$season[summer] <- "Summer"
-#input.rearranged$season[latesummer] <- "LateSummer"
-input.rearranged$season[autumn] <- "Autumn"
-
-input.rearranged$season <- factor(input.rearranged$season , levels=c('Summer', 'Autumn', 'Winter', 'Spring'))
-```
-
-```{r}
 (GPPcum.p <-cum.co2fluxes %>% 
    ddply(c("GSYear", "season"), summarise,
-  seasonal.total = cumsum(GPP_LT.gC)) %>%
+  seasonal.total = cumsum(GPP_LT.gC)) %>% filter(season == "Winter") %>%
    ggplot(., aes(x = GSYear, y = seasonal.total, group = GSYear, fill = season)) +
@@
   ylab("Total GPP")+
+  xlab("Growing season year")+
+   scale_y_continuous(limits = c(0,60000))+
+  theme_classic()+
+    theme(axis.title = element_text(size = 14),
+          axis.text = element_text(size = 13),
+          legend.text = element_text(size = 13),
+          legend.title = element_text(size = 14)))
+
+GPPcum.p
+tiff("GPP.tiff", units="in", width=10, height=6,  res=300)
+print(GPPcum.p)
+dev.off()
+
+(ERcum.p <-cum.co2fluxes %>% 
+   ddply(c("GSYear", "season"), summarise,
+  seasonal.total = cumsum(ER_LT.gC)) %>% filter(season == "Summer") %>%
+   ggplot(., aes(x = GSYear, y = seasonal.total, group = GSYear, fill = season)) +
+  geom_col() + 
+       scale_y_continuous(limits = c(0,60000))+
+  ylab("Total ER")+
   xlab("Growing season year")+
@@
 
-(ERcum.p <-cum.co2fluxes %>% 
-   ddply(c("GSYear", "season"), summarise,
-  seasonal.total = cumsum(ER_LT.gC)) %>%
-   ggplot(., aes(x = GSYear, y = seasonal.total, group = GSYear, fill = season)) +
-  geom_col() + 
-  ylab("Total ER")+
-  xlab("Growing season year")+
-  theme_classic()+
-    theme(axis.title = element_text(size = 14),
-          axis.text = element_text(size = 13),
-          legend.text = element_text(size = 13),
-          legend.title = element_text(size = 14)))
+ERcum.p
+tiff("ER.tiff", units="in", width=10, height=6,  res=300)
+print(ERcum.p)
+dev.off()
 ```
-
-```{r, fig.height=10, fig.width = 6}
-
-(Fig3 <- plot_grid(rain,
-             GPPcum.p, ERcum.p, nrow =3))
-
-```

### 2022-07-05 scripts/Paper 1.Rmd
update post conference; ET

@@
 
-input <- input %>% select(xlDateTime, Fe, Fg_Av, Fh, Fld, Flu, Fn, Fsu, Fsd, Precip, RH, Sws, Ta, Ts, VPD, Wd_SONIC_Av, Ws_SONIC_Av,ER_LT_all, GPP_LT,GPP_SOLO, NEE_LT ) # select met variables (add more as needed)
-colnames(input) <- c('Timestamp', 'LE', 'G', 'H', 'LWin', 'LWout', 'NETRAD', 'SWout', 'SWin', 'Precip', 'RH', 'SWC', 'Ta', 'Ts', 'VPD', 'WD', 'WS', 'ER_LT', 'GPP_LT', 'GPP_SOLO', 'NEE_LT')
+input <- input %>% select(xlDateTime, Fe, Fg_Av, Fh, Fld, Flu, Fn, Fsu, Fsd, Precip, RH, Sws, Ta, Ts, VPD, Wd_SONIC_Av, Ws_SONIC_Av,ER_LT_all, GPP_LT,GPP_SOLO, NEE_LT, ET ) # select met variables (add more as needed)
+colnames(input) <- c('Timestamp', 'LE', 'G', 'H', 'LWin', 'LWout', 'NETRAD', 'SWout', 'SWin', 'Precip', 'RH', 'SWC', 'Ta', 'Ts', 'VPD', 'WD', 'WS', 'ER_LT', 'GPP_LT', 'GPP_SOLO', 'NEE_LT', 'ET')
 
@@
 input$month <- as.factor(input$month)
+input$ET <-as.numeric(input$ET)
 ```
@@
         VPD = mean(VPD, na.rm = TRUE),
+        ET = mean(ET, na.rm = TRUE) * 86400,
         NEE_LT = mean(NEE_LT, na.rm = TRUE), #daily average umol m-2 s-1
@@
 
-input.daily$dayssinceJul1 <- ""
-
-Grow19.20 <- input.daily[1:194,]
-Grow19.20$dayssinceJul1 <- 173:366
-Grow19.20$GSYear <- "19/20"
-
-Grow20.21 <- input.daily[195:559,]
-Grow20.21$dayssinceJul1 <- 1:365
-Grow20.21$GSYear <- "20/21"
-
-Grow21.22 <- input.daily[560:907,]
-Grow21.22$dayssinceJul1 <-1:348
-Grow21.22$GSYear <- "21/22"
-
-input.rearranged <- rbind(Grow19.20,Grow20.21, Grow21.22)
-input.rearranged$monthyear <- as.yearmon(paste(input.rearranged$month, input.rearranged$Year), "%m %Y")
-
-start.time <- as.Date("07-01", "%m-%d")
-end.time <- as.Date("06-30", "%m-%d")
-start.end <- c(start.time, end.time)
 ```
@@
 
-start.time <- as.Date("06-01", "%m-%d")
-end.time <- as.Date("06-30", "%m-%d")
+start.time <- as.Date("2020-06-01", "%m-%d")
+end.time <- as.Date("2022-05-31", "%m-%d")
 start.end <- c(start.time, end.time)
@@
 rainfall_L$Site <- "L"
-rainfall_L <- rainfall_L %>% filter(month >= 7)
+rainfall_L <- rainfall_L %>% filter(month >= 6)
 rainfall_L$month <- as.numeric(rainfall_L$month) 
@@
 ```{r, fig.width=11, fig.height=4}
+season.colors <- c("Summer" = "#E69F00", "Autumn" = "#D55E00", "Winter" ="#0072B2", "Spring" = "#CC79A7")
+
 rainfall.SP <- input.rearranged %>% select(Precip, month, GSYear, season, Year, month.name)
@@
 
-(rain <- rainfall %>%  mutate(Precip = replace_na(Precip, 0)) %>%
+(rainfall.season <- rainfall %>%  mutate(Precip = replace_na(Precip, 0)) %>%
   ddply(c("GSYear", "season"), summarise,
@@
        #scale_x_discrete(limits = month.abb) +
-  geom_col() + 
+  geom_col(aes(fill = season)) +
+        scale_fill_manual(values = season.colors)+
   ylab("Seasonal rainfall (mm)")+
@@
           legend.title = element_text(size = 14)))
+
+rainfall.season
+tiff("rain.tiff", units="in", width=10, height=6,  res=300)
+print(rainfall.season)
+dev.off()
 
@@
 
+rainfall.summary <- rainfall %>%  mutate(Precip = replace_na(Precip, 0)) %>%
+  ddply(c("GSYear", "season"), summarise,
+  seasonal.total = sum(Precip))
 ```
@@
 
-```{r Air temperature, echo=FALSE, message = FALSE, fig.width = 11, fig.height = 4}
+```{r Air temperature, echo=FALSE, message = FALSE, fig.width = 13, fig.height = 3}
 (TA <- ggplot(input.rearranged, aes(x = date, y = Ta.mean)) +
@@
         geom_ribbon(aes(ymin=Ta.min, ymax=Ta.max), alpha=.3, linetype=0) +
+
     xlab("Date")+
@@
 
+```{r fig.width=7, fig.height=5}
+TA.summary <- input.rearranged %>% ddply(c("GSYear", "season"), summarise,
+                                       mean.TA = mean(Ta.mean),
+                                       mean.TS = mean(Ts.mean))
+#ER.summary$month.name <- factor(ER.summary$month.name, levels=c("Jul", "Aug", "Sep", "Oct", "Nov", "Dec", "Jan", "Feb", "Mar", "Apr", "May", "Jun"))
+
+TA.summary$season <- factor(TA.summary$season, levels=c("Winter", "Spring", "Summer", "Autumn"))
+
+(TA.sum.p <-TA.summary %>% 
+  ggplot(., aes(x = GSYear, y = mean.TA), group = season) +
+  geom_col(position = position_dodge2(width = 0.9, preserve = "single"), aes(fill = season)) +
+                scale_fill_manual(values = season.colors)+
+  ylab("Air temperature (°C)")+
+  xlab("Date")+
+  theme_classic()+
+    theme(axis.title = element_text(size = 14),
+          axis.text = element_text(size = 13),
+          legend.text = element_text(size = 13),
+          legend.title = element_text(size = 14),
+          axis.text.x = element_text( vjust = 0.5)))
+
+TA.sum.p
+tiff("TAbar.tiff", units="in", width=10, height=6,  res=300)
+print(TA.sum.p)
+dev.off()
+
+(TS.sum.p <-TA.summary %>% 
+  ggplot(., aes(x = GSYear, y = mean.TS), group = season) +
+  geom_col(position = position_dodge2(width = 0.9, preserve = "single"), aes(fill = season)) +
+                    scale_fill_manual(values = season.colors)+
+  ylab("Soil temperature (°C)")+
+  xlab("Date")+
+  theme_classic()+
+    theme(axis.title = element_text(size = 14),
+          axis.text = element_text(size = 13),
+          legend.text = element_text(size = 13),
+          legend.title = element_text(size = 14),
+          axis.text.x = element_text( vjust = 0.5)))
+
+TS.sum.p
+tiff("TSbar.tiff", units="in", width=10, height=6,  res=300)
+print(TS.sum.p)
+dev.off()
+
+```
+```{r, fig.width=13, fig.height=5}
+group.colour <- c("19/20" = "#E69F00", "20/21" = "#009E73", "21/22" ="#D55E00")
+
+(ET.p <- ggplot(input.rearranged, aes(x = dayssinceJun1, y = ET, group = GSYear)) +
+  geom_line(aes(color = GSYear), size = 1)+
+    scale_color_manual(values = group.colour) +
+ # scale_x_date(date_labels = "%b", date_breaks = "1 month") +
+  xlab("Days since June 1st")+
+   ylab("ET (mm/day)")+
+  theme_classic())+
+    theme(axis.title = element_text(size = 14),
+          axis.text = element_text(size = 13),
+          legend.text = element_text(size = 13),
+          legend.title = element_text(size = 14))
+```
+
 ### VPD
 
-```{r VPD, echo=FALSE, message = FALSE, fig.width = 10, fig.height = 4}
-ggplotly(ggplot(input.daily, aes(x = as.Date(jday, origin = ("2020-01-01")), y = VPD, group = Year)) +
-  geom_line(aes(color = Year))+
-  scale_x_date(date_labels = "%b", date_breaks = "1 month") +
-  xlab("Month")+
-  theme_classic())
+```{r VPD, echo=FALSE, message = FALSE, fig.width = 9, fig.height = 4}
+
+(VPD.p <- ggplot(input.rearranged, aes(x = dayssinceJun1, y = VPD, group = GSYear)) +
+  geom_line(aes(color = GSYear), size = 1)+
+    scale_color_manual(values = group.colour) +
+ # scale_x_date(date_labels = "%b", date_breaks = "1 month") +
+  xlab("Days since June 1st")+
+   ylab("VPD (kPa")+
+  theme_classic())+
+    theme(axis.title = element_text(size = 14),
+          axis.text = element_text(size = 13),
+          legend.text = element_text(size = 13),
+          legend.title = element_text(size = 14))
+
+VPD.p
+tiff("VPD.tiff", units="in", width=10, height=6,  res=300)
+print(VPD.p)
+dev.off()
+
 ```
@@
 ```{r, echo=FALSE, message = FALSE, fig.width = 7, fig.height = 4}
-group.colors <- c("19/20" = "#333BFF", "20/21" = "#CC6600", "21/22" ="#9633FF")
 
-(SWC.20 <- input.rearranged %>% filter (GSYear == "19/20" ) %>% ggplot(., aes(x = as.Date(dayssinceJun1, origin = as.Date("06-01", "%m-%d")), SWC, group = GSYear)) +
-  geom_line(aes(color = GSYear), size = 1.5)+
-  # scale_x_continuous(limits = c(0, 365))+
-  xlab('Month') +
-  ylab('SWC %') +
-   scale_x_date(breaks = "month", date_labels = "%b", limits = as.Date(c("06-01", "05-31"), "%m-%d"))+
-    scale_color_manual(values = group.colors)+
+input.rearranged$dayssinceJun1 <- as.numeric(input.rearranged$dayssinceJun1)
+
+(SWC.20 <- input.rearranged  %>% filter(GSYear == "19/20" ) %>% ggplot(., aes(dayssinceJun1, SWC), group = GSYear) +
+  geom_line(aes(color = GSYear), size = 1)+
+   scale_x_continuous(limits = c(1, 365))+
+  xlab('Days since June 1st') +
+        ylab(bquote('SWC ('~m^3~'/'~m^-3~')'))+
+
+#  ylab('SWC') +
+  # scale_x_continuous()+
+    scale_color_manual(values=group.colour)+
   theme_classic() + 
@@
           axis.text = element_text(size = 13),
-          legend.text = element_text(size = 13),
-          legend.title = element_text(size = 14)))
+          legend.position = "none"))
 
@@
                                        monthly.sum = sum(NEE_LT.gC))
-NEE.summary$month.name <- factor(NEE.summary$month.name, levels=c("Jul", "Aug", "Sep", "Oct", "Nov", "Dec", "Jan", "Feb", "Mar", "Apr", "May", "Jun"))
+NEE.summary$month.name <- factor(NEE.summary$month.name, levels=c("Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec", "Jan", "Feb", "Mar", "Apr", "May"))
 
@@
   ggplot(., aes(x = month.name, y = monthly.sum, group = GSYear, fill = GSYear)) +
-  geom_col(position = "dodge", aes(fill = GSYear)) + 
+  geom_col(position = position_dodge2(width = 0.9, preserve = "single"), aes(fill = GSYear)) + 
+    scale_fill_manual(values = group.colour)+
          #scale_x_discrete(limits = start.end)+
-  ylab("Monthly NEE")+
-  xlab("month")+
-  theme_classic())
+    ylab(bquote('Monthly NEE (g C ' ~m^-2~')'))+
+  xlab("Month")+
+  theme_classic())+
+   theme(axis.title = element_text(size = 15),
+          axis.text = element_text(size = 14),
+          legend.text = element_text(size = 13),
+          legend.title = element_text(size = 14))
 
@@
                                        monthly.sum = sum(GPP_LT.gC))
+GPP.summary$season <- factor(GPP.summary$season, levels=c("Winter", "Spring", "Summer", "Autumn"))
+
+GPP.summary <- input.rearranged %>% ddply(c("GSYear"), summarise,
+                                       monthly.sum = sum(GPP_LT.gC))
 #GPP.summary$month.name <- factor(GPP.summary$month.name, levels=c("Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec", "Jan", "Feb", "Mar", #"Apr", "May"))
@@
   theme_classic())
+
+GPP.bar
+tiff("GPPbar.tiff", units="in", width=10, height=6,  res=300)
+print(GPP.bar)
+dev.off()
 ```
@@
                                        monthly.sum = sum(ER_LT.gC))
+
+#ER.summary <- input.rearranged %>% ddply(c("GSYear"), summarise,
+ #                                      monthly.sum = sum(ER_LT.gC))
+
 #ER.summary$month.name <- factor(ER.summary$month.name, levels=c("Jul", "Aug", "Sep", "Oct", "Nov", "Dec", "Jan", "Feb", "Mar", "Apr", "May", "Jun"))
+
+ER.summary$season <- factor(ER.summary$season, levels=c("Winter", "Spring", "Summer", "Autumn"))
 
@@
   theme_classic())
+
+ER.bar
+tiff("ERbar.tiff", units="in", width=10, height=6,  res=300)
+print(ER.bar)
+dev.off()
 ```
 
-```{r cumulative fluxes, fig.width = 10, fig.height = 6}
+```{r cumulative fluxes, fig.width = 7, fig.height = 4}
 cum.co2fluxes <- input.rearranged %>% #input.daily %>%
-  select(NEE_LT.gC, GPP_LT.gC, ER_LT.gC, dayssinceJul1, GSYear, season) %>% 
-  group_by(GSYear) %>% 
+  select(NEE_LT.gC, GPP_LT.gC, ER_LT.gC, dayssinceJun1, GSYear, season) %>% 
+  group_by(GSYear, season) %>% 
   mutate(NEEcum = cumsum(NEE_LT.gC),
@@
 
+cum.co2fluxes$season <- factor(cum.co2fluxes$season, levels=c("Winter", "Spring", "Summer", "Autumn"))
+
 (NEEcum.p <-cum.co2fluxes %>% 
-  ggplot(., aes(x = as.Date(dayssinceJul1, origin = as.Date("07-01", "%m-%d")), NEEcum, color = GSYear)) +
-  geom_line(size = 1)+
+  ggplot(., aes(dayssinceJun1, NEEcum, group = GSYear, color = GSYear)) +
+  geom_line(size = 1, aes(color = GSYear))+
+    scale_color_manual(values = group.colour)+
+       scale_x_continuous(limits = c(1, 365))+
   ylab(bquote('Cumulative NEE (g C ' ~m^-2~')'))+
-  xlab("Days since July 1st")+
-       scale_x_date(breaks = "month", date_labels = "%b", limits = as.Date(c("07-01", "06-31"), "%m-%d"))+
+  xlab("Days since June 1st")+
   theme_classic()+ 
@@
 (GPPcum.p <-cum.co2fluxes %>% 
-  ggplot(., aes(dayssinceJul1, GPPcum, color = GSYear)) +
+  ggplot(., aes(dayssinceJun1, GPPcum, color = GSYear)) +
   geom_line(size = 1)+
+        scale_color_manual(values = group.colour)+
+       scale_x_continuous(limits = c(1, 365))+
   ylab(bquote('Cumulative GPP (g C ' ~m^-2~')'))+
-  xlab("Days since July 1st")+
+  xlab("Days since June 1st")+
   theme_classic()+ 
@@
 
-(ERcum.p <-cum.co2fluxes %>% 
-  ggplot(., aes(dayssinceJul1, ERcum, color = GSYear)) +
-  geom_line(size =1)+
-  ylab(bquote('Cumulative ER (g C' ~m^-2~')'))+
-  xlab("Days since July 1st")+
+GPPcum.p
+tiff("GPPcum.tiff", units="in", width=10, height=6,  res=300)
+print(GPPcum.p)
+dev.off()
+
+(GPPtime.p <-input.rearranged %>% filter(GPP_LT.gC>0) %>%
+  ggplot(., aes(dayssinceJun1, GPP_LT.gC, color = GSYear)) +
+  geom_line(size = 1)+
+        scale_color_manual(values = group.colour)+
+       scale_x_continuous(limits = c(1, 365))+
+
+  ylab(bquote(' GPP (g C ' ~m^-2~')'))+
+  xlab("Days since June 1st")+
   theme_classic()+ 
@@
           axis.text = element_text(size = 13)))
+
+GPPtime.p
+tiff("GPPtime.tiff", units="in", width=10, height=6,  res=300)
+print(GPPtime.p)
+dev.off()
+
+(ERcum.p <-cum.co2fluxes %>% 
+  ggplot(., aes(dayssinceJun1, ERcum, color = GSYear)) +
+  geom_line(size =1)+
+        scale_color_manual(values = group.colour)+
+       scale_x_continuous(limits = c(1, 365))+
+
+  ylab(bquote('Cumulative ER (g C' ~m^-2~')'))+
+  xlab("Days since June 1st")+
+  theme_classic()+ 
+    theme(axis.title = element_text(size = 14),
+          axis.text = element_text(size = 13)))
+
+ERcum.p
+tiff("ERcum.tiff", units="in", width=10, height=6,  res=300)
+print(ERcum.p)
+dev.off()
+
+(ERtime.p <-input.rearranged %>% 
+  ggplot(., aes(dayssinceJun1, ER_LT.gC, color = GSYear)) +
+  geom_line(size = 1)+
+        scale_color_manual(values = group.colour)+
+       scale_x_continuous(limits = c(1, 365))+
+
+  ylab(bquote('ER (g C ' ~m^-2~')'))+
+  xlab("Days since June 1st")+
+  theme_classic()+ 
+    theme(axis.title = element_text(size = 14),
+          axis.text = element_text(size = 13)))
+
+ERtime.p
+tiff("ERtime.tiff", units="in", width=10, height=6,  res=300)
+print(ERtime.p)
+dev.off()
 
@@
 ```{r}
-(GPPcum.p <-cum.co2fluxes %>% 
+GPP.summary<- cum.co2fluxes %>% select(GPP_LT.gC,dayssinceJun1, GSYear, season) %>% 
+  group_by(GSYear, season) %>% 
    ddply(c("GSYear", "season"), summarise,
-  seasonal.total = cumsum(GPP_LT.gC)) %>% filter(season == "Winter") %>%
-   ggplot(., aes(x = GSYear, y = seasonal.total, group = GSYear, fill = season)) +
-  geom_col() + 
-  ylab("Total GPP")+
-  xlab("Growing season year")+
-   scale_y_continuous(limits = c(0,60000))+
-  theme_classic()+
+  seasonal.total = cumsum(GPP_LT.gC))
+
+cum.co2fluxes$season <- factor(cum.co2fluxes$season, levels=c("Autumn", "Summer", "Spring", "Winter"))
+
+(GPP.bar.s <- cum.co2fluxes  %>%
+  ggplot(., aes(x = GSYear, y = GPP_LT.gC, group = season, fill = season)) +
+  geom_col(aes(fill = season)) + 
+         #scale_x_discrete(limits = start.end)+
+  xlab("month")+
+         ylab(bquote('Total seasonal GPP (g C ' ~m^-2~')'))+
+    scale_fill_manual(values = season.colors)+
+  theme_classic()) +
   theme(axis.title = element_text(size = 14),
@@
           legend.text = element_text(size = 13),
-          legend.title = element_text(size = 14)))
+          legend.title = element_text(size = 14))
 
-GPPcum.p
-tiff("GPP.tiff", units="in", width=10, height=6,  res=300)
-print(GPPcum.p)
+GPP.bar.s
+tiff("GPPbar.tiff", units="in", width=10, height=6,  res=300)
+print(GPP.bar.s)
 dev.off()
 
-(ERcum.p <-cum.co2fluxes %>% 
+GPP.summary <- cum.co2fluxes %>% ddply(c("GSYear", "season"), summarise,
+                                       monthly.sum = sum(GPP_LT.gC))
+
+(ER.bar.s <- cum.co2fluxes  %>%
+  ggplot(., aes(x = GSYear, y = ER_LT.gC, group = season, fill = season)) +
+  geom_col(aes(fill = season)) + 
+         #scale_x_discrete(limits = start.end)+
+  xlab("month")+
+         ylab(bquote('Total seasonal ER (g C ' ~m^-2~')'))+
+    scale_fill_manual(values = season.colors)+
+  theme_classic()) +
+  theme(axis.title = element_text(size = 14),
+          axis.text = element_text(size = 13),
+          legend.text = element_text(size = 13),
+          legend.title = element_text(size = 14))
+
+ER.bar.s
+tiff("ERbar.tiff", units="in", width=10, height=6,  res=300)
+print(ER.bar.s)
+dev.off()
+
+ER.summary <- cum.co2fluxes %>% ddply(c("GSYear", "season"), summarise,
+                                       monthly.sum = sum(ER_LT.gC))
+
+```
+```{r}
+
+rainfall$season <- factor(rainfall$season, levels=c("Winter", "Spring", "Summer", "Autumn"))
+
+(rain <- rainfall %>%  mutate(Precip = replace_na(Precip, 0)) %>%
   ddply(c("GSYear", "season"), summarise,
-  seasonal.total = cumsum(ER_LT.gC)) %>% filter(season == "Summer") %>%
+  seasonal.total = sum(Precip)) %>%
   ggplot(., aes(x = GSYear, y = seasonal.total, group = GSYear, fill = season)) +
+       #scale_x_discrete(limits = month.abb) +
   geom_col() + 
-       scale_y_continuous(limits = c(0,60000))+
-  ylab("Total ER")+
+  ylab("Seasonal rainfall (mm)")+
   xlab("Growing season year")+
@@
           legend.title = element_text(size = 14)))
-
-ERcum.p
-tiff("ER.tiff", units="in", width=10, height=6,  res=300)
-print(ERcum.p)
-dev.off()
 ```

### 2022-07-07 scripts/Paper 1.Rmd
ET

@@
 
-input <- input %>% select(xlDateTime, Fe, Fg_Av, Fh, Fld, Flu, Fn, Fsu, Fsd, Precip, RH, Sws, Ta, Ts, VPD, Wd_SONIC_Av, Ws_SONIC_Av,ER_LT_all, GPP_LT,GPP_SOLO, NEE_LT, ET ) # select met variables (add more as needed)
+input <- input %>% select(xlDateTime, Fe, Fg_Av, Fh, Fld, Flu, Fn, Fsu, Fsd, Precip, RH, Sws, Ta, Ts, VPD, Wd_SONIC_Av, Ws_SONIC_Av,ER_LT_all, GPP_LT,GPP_SOLO, NEE_LT, ET_EF ) # select met variables (add more as needed)
 colnames(input) <- c('Timestamp', 'LE', 'G', 'H', 'LWin', 'LWout', 'NETRAD', 'SWout', 'SWin', 'Precip', 'RH', 'SWC', 'Ta', 'Ts', 'VPD', 'WD', 'WS', 'ER_LT', 'GPP_LT', 'GPP_SOLO', 'NEE_LT', 'ET')
@@
 input$month <- as.factor(input$month)
-input$ET <-as.numeric(input$ET)
 ```
@@
         VPD = mean(VPD, na.rm = TRUE),
-        ET = mean(ET, na.rm = TRUE) * 86400,
+        ET = mean(ET, na.rm = TRUE),
         NEE_LT = mean(NEE_LT, na.rm = TRUE), #daily average umol m-2 s-1
@@
 ```
-```{r, fig.width=13, fig.height=5}
-group.colour <- c("19/20" = "#E69F00", "20/21" = "#009E73", "21/22" ="#D55E00")
-
-(ET.p <- ggplot(input.rearranged, aes(x = dayssinceJun1, y = ET, group = GSYear)) +
-  geom_line(aes(color = GSYear), size = 1)+
-    scale_color_manual(values = group.colour) +
- # scale_x_date(date_labels = "%b", date_breaks = "1 month") +
-  xlab("Days since June 1st")+
-   ylab("ET (mm/day)")+
-  theme_classic())+
-    theme(axis.title = element_text(size = 14),
-          axis.text = element_text(size = 13),
-          legend.text = element_text(size = 13),
-          legend.title = element_text(size = 14))
-```
 
@@
 ```{r VPD, echo=FALSE, message = FALSE, fig.width = 9, fig.height = 4}
-
 (VPD.p <- ggplot(input.rearranged, aes(x = dayssinceJun1, y = VPD, group = GSYear)) +
@@
 ```{r, echo=FALSE, message = FALSE, fig.width = 7, fig.height = 4}
+group.colour <- c("19/20" = "#E69F00", "20/21" = "#009E73", "21/22" ="#D55E00")
 
@@
                                        monthly.sum = sum(GPP_LT.gC))
-GPP.summary$season <- factor(GPP.summary$season, levels=c("Winter", "Spring", "Summer", "Autumn"))
 
@@
 #GPP.summary$month.name <- factor(GPP.summary$month.name, levels=c("Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec", "Jan", "Feb", "Mar", #"Apr", "May"))
+GPP.summary$season <- factor(GPP.summary$season, levels=c("Winter", "Spring", "Summer", "Autumn"))
 

### 2022-07-13 scripts/Paper 1.Rmd
Add ET conversion to daily

@@
 
-input <- input %>% select(xlDateTime, Fe, Fg_Av, Fh, Fld, Flu, Fn, Fsu, Fsd, Precip, RH, Sws, Ta, Ts, VPD, Wd_SONIC_Av, Ws_SONIC_Av,ER_LT_all, GPP_LT,GPP_SOLO, NEE_LT, ET_EF ) # select met variables (add more as needed)
+input <- input %>% select(xlDateTime, Fe, Fg_Av, Fh, Fld, Flu, Fn, Fsu, Fsd, Precip, RH, Sws, Ta, Ts, VPD, Wd_SONIC_Av, Ws_SONIC_Av,ER_LT_all, GPP_LT,GPP_SOLO, NEE_LT, ET) # select met variables (add more as needed)
 colnames(input) <- c('Timestamp', 'LE', 'G', 'H', 'LWin', 'LWout', 'NETRAD', 'SWout', 'SWin', 'Precip', 'RH', 'SWC', 'Ta', 'Ts', 'VPD', 'WD', 'WS', 'ER_LT', 'GPP_LT', 'GPP_SOLO', 'NEE_LT', 'ET')
@@
 input$Timestamp <- as.POSIXct(input$Timestamp, format= "%d/%m/%Y %H:%M") # change from character to POSIXct
-input[,2:21] <- as.data.frame(sapply(input[,2:21], as.numeric)) # convert data frame from character to numeric
+input[,2:22] <- as.data.frame(sapply(input[,2:22], as.numeric)) # convert data frame from character to numeric
 
@@
         VPD = mean(VPD, na.rm = TRUE),
-        ET = mean(ET, na.rm = TRUE),
+        ET = mean(ET, na.rm = TRUE)* 86400,#daily total ET
         NEE_LT = mean(NEE_LT, na.rm = TRUE), #daily average umol m-2 s-1

### 2022-07-13 scripts/Paper 1.Rmd
add et plot

@@
 ```{r VPD, echo=FALSE, message = FALSE, fig.width = 9, fig.height = 4}
+group.colour <- c("19/20" = "#E69F00", "20/21" = "#009E73", "21/22" ="#D55E00")
+
 (VPD.p <- ggplot(input.rearranged, aes(x = dayssinceJun1, y = VPD, group = GSYear)) +
@@
 VPD.p
-tiff("VPD.tiff", units="in", width=10, height=6,  res=300)
-print(VPD.p)
-dev.off()
+#("VPD.tiff", units="in", width=10, height=6,  res=300)
+#print(VPD.p)
+#dev.off()
+
+```
+
+### ET
+
+```{r VPD, echo=FALSE, message = FALSE, fig.width = 9, fig.height = 4}
+
+(ET.p <- ggplot(input.rearranged, aes(x = dayssinceJun1, y = ET, group = GSYear)) +
+  geom_line(aes(color = GSYear), size = 1)+
+    scale_color_manual(values = group.colour) +
+ # scale_x_date(date_labels = "%b", date_breaks = "1 month") +
+  xlab("Days since June 1st")+
+   ylab("ET (mm day-1)")+
+  theme_classic())+
+    theme(axis.title = element_text(size = 14),
+          axis.text = element_text(size = 13),
+          legend.text = element_text(size = 13),
+          legend.title = element_text(size = 14))
+
+ggplotly(ET.p)
+
+#("ET.tiff", units="in", width=10, height=6,  res=300)
+#print(ET.p)
+#dev.off()
 
@@
 ```{r, echo=FALSE, message = FALSE, fig.width = 7, fig.height = 4}
-group.colour <- c("19/20" = "#E69F00", "20/21" = "#009E73", "21/22" ="#D55E00")
 
@@
 SWC.20
-tiff("SWC20.tiff", units="in", width=10, height=6,  res=300)
-print(SWC.20)
-dev.off()
-```
-
-```{r add seasons, include=FALSE}
-#rainfall$season <- "" # add season variable
-
-# define seasons
-#winter <- (rainfall$month == "Jun" | rainfall$month == "Jul" | rainfall$month == "Aug")
-#spring <- (rainfall$month == "Sep" | rainfall$month == "Oct" | rainfall$month == "Nov")
-#summer <- (rainfall$month == "Dec" | rainfall$month == "Jan" | rainfall$month == "Feb")
-#autumn <- (rainfall$month == "Mar" | rainfall$month == "Apr" | rainfall$month == "May")
-
-#rainfall$season[winter] <- "Winter"
-#rainfall$season[spring] <- "Spring"
-#rainfall$season[summer] <- "Summer"
-#rainfall$season[earlysummer] <- "EarlySummer"
-#rainfall$season[latesummer] <- "LateSummer"
-#rainfall$season[autumn] <- "Autumn"
-
-#rainfall$season <- factor(rainfall$season , levels=c('Summer', 'Autumn', 'Winter', 'Spring'))
+#tiff("SWC20.tiff", units="in", width=10, height=6,  res=300)
+#print(SWC.20)
+#dev.off()
 ```

### 2022-07-15 scripts/Paper 1.Rmd
add windrose md

@@
 
-GPP.summary <- input.rearranged %>% ddply(c("GSYear"), summarise,
-                                       monthly.sum = sum(GPP_LT.gC))
+#GPP.summary <- input.rearranged %>% ddply(c("GSYear"), summarise,
+ #                                      monthly.sum = sum(GPP_LT.gC))
 #GPP.summary$month.name <- factor(GPP.summary$month.name, levels=c("Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec", "Jan", "Feb", "Mar", #"Apr", "May"))
@@
 ```
+
 ```{r}
@@
 ```
+
+```{r}
+(ETGPP.p <- ggplot(input.rearranged, aes(x = ET, y = GPP_LT), color = GSYear) +
+  geom_point(aes(color = GSYear))+
+   geom_smooth(aes(color = GSYear), method = "lm")+
+    #scale_color_manual(values = group.colour) +
+ # scale_x_date(date_labels = "%b", date_breaks = "1 month") +
+  xlab("Daily ET (mm)")+
+   ylab("GPP")+
+  theme_classic())+
+    theme(axis.title = element_text(size = 14),
+          axis.text = element_text(size = 13),
+          legend.text = element_text(size = 13),
+          legend.title = element_text(size = 14))
+```

### 2022-07-15 scripts/windrose.Rmd
add windrose md

---
title: "Wind Rose"
author: "Marion Nyberg"
date: '2022-07-15'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r setup, include=FALSE}
library(data.table)
library(janitor)
library(plotly)
library(plyr)
library(dplyr)
library(knitr)
library(tidyverse)
#library(devtools)
library(openair)
library(tidyr)
library(naniar)
library(forecast)
library(kableExtra)
library(htmltools)
library(ggpubr)
library(rstatix)
library(broom)
library(gtable)
library(gridExtra)
library(cowplot)
library(viridis)
library(zoo)
library(clifro)
library(lattice)

rm(list = ls())
#wd <- ("R:/SET/PlantSci/Shared Work Spaces/Ecology/Flux/SP_data")
#setwd(wd)
#knitr::opts_knit$set(root.dir = wd)
```

Below are conversion factors and functions used in the markdown file:

```{r functions and conversions}
d.avg <- 1800 * 48 #60 secs * 60 mins * 24 hours (# of secs in day)
co2_conv <- 12.01/(10^6)

tidy.csv <- function(x){
  input <- x[-c(1,2),] %>%
    row_to_names(., 1)
}

gofC.f <- function(x){ # function to convert to mean 30 minute to g of C
  (x*d.avg)*co2_conv
}

gtomg.f <- function(x){ # function to convert from g to mg
  x*1000
}
```

```{r read data and some data class cleaning, include=FALSE}
input <- fread("R:/SET/PlantSci/Shared Work Spaces/Ecology/Flux/SP_data/PFP/L6/SilverPlains_L6.csv", header = FALSE, na.strings = "-9999") 
input <- tidy.csv(input)

input <- input %>% select(xlDateTime, Fe, Fg_Av, Fh, Fld, Flu, Fn, Fsu, Fsd, Precip, RH, Sws, Ta, Ts, VPD, Wd_SONIC_Av, Ws_SONIC_Av,ER_LT_all, GPP_LT,GPP_SOLO, NEE_LT, ET) # select met variables (add more as needed)
colnames(input) <- c('Timestamp', 'LE', 'G', 'H', 'LWin', 'LWout', 'NETRAD', 'SWout', 'SWin', 'Precip', 'RH', 'SWC', 'Ta', 'Ts', 'VPD', 'WD', 'WS', 'ER_LT', 'GPP_LT', 'GPP_SOLO', 'NEE_LT', 'ET')

input$Timestamp <- as.POSIXct(input$Timestamp, format= "%d/%m/%Y %H:%M") # change from character to POSIXct
input[,2:22] <- as.data.frame(sapply(input[,2:22], as.numeric)) # convert data frame from character to numeric

input$jday <-yday(input$Timestamp) # add jday
input$Year <- year(input$Timestamp) # extract year
input$Year <- as.factor(input$Year) # convert year from integer to factor
input$month <- month(as.POSIXct(input$Timestamp)) # extract month
input$month <- as.factor(input$month)
input$hour <- format(input$Timestamp, format = "%H")
input$hour <- as.numeric(input$hour)

# create index for time of day - morn, aft, night
input$TOD <- ""
ind.morn<- (input$hour >= 06 & input$hour < 12)
ind.aft<- (input$hour >= 12 & input$hour < 18)
ind.night<- (input$hour >= 18 | input$hour < 6)

input$TOD[ind.morn] <- "morn"
input$TOD[ind.aft] <- "aft"
input$TOD[ind.night] <- "night"

input <- input[-c(13835, 13836, 31307, 31308)]
```

```{r add seasons, include=FALSE}
# maybe this would be better as GS/NGS?

input$season <- "" # add season variable

# define seasons
winter <- (input$month == "6" | input$month == "7" | input$month == "8")
spring <- (input$month == "9" | input$month == "10" | input$month == "11")
summer <- (input$month == "12" | input$month == "1" | input$month == "2")
autumn <- (input$month == "3" | input$month == "4" | input$month == "5")

input$season[winter] <- "Winter"
input$season[spring] <- "Spring"
input$season[summer] <- "Summer"
input$season[autumn] <- "Autumn"

season_levelorder <-  c('Summer', 'Autumn', 'Winter', 'Spring') 
```

### Wind direction and speed

```{r Wind direction, echo=FALSE, message = FALSE, fig.height=21, fig.width=12}
input$Month.WR <- input$month
#plot_ly(input, x = ~jday, y = ~WD, split = ~Year, name = ~Year, type = 'scatter', mode = 'lines')
windRose(input, ws = "WS", wd = "WD", type = "Year")

input%>%filter(month == "1") %>%
  windRose(., ws = "WS", wd = "WD", type = "TOD")

Windrose <- windRose(input, ws = "WS", wd = "WD", type = c("TOD","Month.WR"), aspect = "fill")

Windrose
jpeg("Windrose.jpeg", units="in", width=7, height=23,  res=300)
print(Windrose)
dev.off()

input %>% filter(season == "Autumn") %>%
  windRose(., ws = "WS", wd = "WD")

input %>% filter(season == "Winter") %>%
  windRose(., ws = "WS", wd = "WD")

input%>% filter(season == "Spring") %>%
  windRose(., ws = "WS", wd = "WD")
```

```{r}
# alternative way: https://www.r-bloggers.com/2016/06/plot-a-wind-rose-in-r/

# choose bin size (degrees/bin)
deg <- 30 
# define the range of each bin
dir.breaks <- seq(0-(deg/2), 360+(deg/2), deg)
# assign each direction to a bin range
dir.binned <- cut(input$WD,
                       breaks = dir.breaks,
                       ordered_result = TRUE)
# generate pretty lables
dir.labels <- as.character(c(seq(0, 360-deg, by = deg), 0))
# replace ranges with pretty bin lables
levels(dir.binned) <- dir.labels
# Assign bin names to the original data set
input$dir.binned <- dir.binned

thm <- theme_bw() + 
    theme(axis.text.x = element_text(size=8, face = "plain"),
          axis.text.y = element_text(size=8, face = "plain"),
          axis.title.x = element_blank(),
          axis.title.y = element_text(size=8, face = "plain", hjust = 0.9, vjust = 1.3),
          panel.border = element_blank(),
          panel.grid  = element_blank())

summary(dir.binned) # see which bin is most common

# initialise the plot
plt.dirrose <- ggplot() +
    # since the plot background is blank we'll add a series of horizontal lines, at 5000 count intervals, up to 25000.
    geom_hline(yintercept = seq(0, 150, by = 25), colour = "grey60", size = 0.3) +
    # Now we add a darker horizontal line as the top border at 30000.
    geom_hline(yintercept = 150, colour = "black", size = 0.3) +
    # We want 12 vertical lines representing the centers of the 30° ranges.
    geom_vline(xintercept = c(seq(1,12,1)), colour = "grey60", size = 0.3) +
    # On top of everything we place the histogram bars.
    geom_bar(data = input, aes(x = dir.binned), width = 1, colour="black", size = 0.3, alpha=0.5) + 
    # Add the x-axis labels
    scale_x_discrete( drop = FALSE, labels = c(0, "", "", 90, "", "", 180, "", "", 270, "", "")) +
    # Add the y-axis labels
    scale_y_continuous(limits = c(0, 150), expand = c(0, 0), 
                       breaks = c(0, 25, 50, 75, 100, 125, 150), 
                       labels = c(0, 25, 50, 75, 100, 125, 150)) +
    # Add the axis titles
    labs(x = 'Outward step bearing (°)', y = 'Count of outward steps (x10³)') +
    # If you only use the plot code up till here you will get a histogram.
    # the next line wraps the histogram into a windrose
    coord_polar(start = -(deg/2)*(pi/180)) +
    # apply theme
    thm
plt.dirrose
```

```{r wind and fluxes, fig.width= 10}
# calculate an average wind pattern as in Griebel, A., et al., 2016
# wind pattern (WP) is equivalent to a standardized wind sector contribution, based on some temporal average

# there is way tooo much code here and I need to tidy it a lot and also do by season as well as year.

# define wind sectors
NE <- input.daily$WD >0 & input.daily$WD <= 90
SE <- input.daily$WD >90 & input.daily$WD <= 180
SW <- input.daily$WD >180 & input.daily$WD <= 270
NW <- input.daily$WD >270 & input.daily$WD <= 360

# adding wind sectors to daily df
input.daily$wind.sector <- ""
input.daily$wind.sector <- ifelse(input.daily$WD >0 & input.daily$WD <= 90, "NE", input.daily$wind.sector)
input.daily$wind.sector <- ifelse(input.daily$WD >90 & input.daily$WD <= 180, "SE", input.daily$wind.sector)
input.daily$wind.sector <- ifelse(input.daily$WD >180 & input.daily$WD <= 270, "SW", input.daily$wind.sector)
input.daily$wind.sector <- ifelse(input.daily$WD >270 & input.daily$WD <= 360, "NW", input.daily$wind.sector)

# calculate number of occurrences (n) per wind sector (j)
# need to make function to do this
NE.n <- input.daily %>% filter(Year == 2020 | Year == 2021) %>% filter(wind.sector == "NE") %>% nrow()
NE.n.2021 <- input.daily %>% filter(wind.sector == "NE" & Year == "2021") %>% nrow()
NE.n.2020 <- input.daily %>% filter(wind.sector == "NE" & Year == "2020") %>% nrow()

SE.n <- input.daily %>% filter(Year == 2020 | Year == 2021) %>% filter(wind.sector == "SE") %>% nrow()
SE.n.2021 <- input.daily %>% filter(wind.sector == "SE" & Year == "2021") %>% nrow()
SE.n.2020 <- input.daily %>% filter(wind.sector == "SE" & Year == "2020") %>% nrow()

NW.n <- input.daily %>% filter(Year == 2020 | Year == 2021) %>% filter(wind.sector == "NW") %>% nrow()
NW.n.2021 <- input.daily %>% filter(wind.sector == "NW" & Year == "2021") %>% nrow()
NW.n.2020 <- input.daily %>% filter(wind.sector == "NW" & Year == "2020") %>% nrow()

SW.n <- input.daily %>% filter(Year == 2020 | Year == 2021) %>% filter(wind.sector == "SW") %>% nrow()
SW.n.2021 <- input.daily %>% filter(wind.sector == "SW" & Year == "2021") %>% nrow()
SW.n.2020 <- input.daily %>% filter(wind.sector == "SW" & Year == "2020") %>% nrow()

# number of occurrences per wind sector divided by number of years (N). N is 2.1 because I did number of days divided by 365 to get the number of years (maybe better to filter to where I have only 2 full years)
WP.NE <- NE.n/2.1
WP.SE <- SE.n/2.1
WP.NW <- NW.n/2.1
WP.SW <- SW.n/2.1

# average carbon flux from each sector during each year
NE.co2.2021 <- input.daily %>% filter(wind.sector == "NE" & Year == "2021") %>% select(Fco2) %>%
  summarise(sum(Fco2)) # 5 obs 
NW.co2.2021 <- input.daily %>% filter(wind.sector == "NW" & Year == "2021") %>% select(Fco2) %>%
  summarise(sum(Fco2)) # 132 obs summarise(sum(Fco2)) 
NE.co2.2020 <- input.daily %>% filter(wind.sector == "NE" & Year == "2020") %>% select(Fco2) %>%
  summarise(sum(Fco2)) # 4 obs summarise(sum(Fco2)) 
NW.co2.2020 <- input.daily %>% filter(wind.sector == "NW" & Year == "2020") %>% select(Fco2) %>%  #140 obs
summarise (sum(Fco2))

SE.co2.2021 <- input.daily %>% filter(wind.sector == "SE" & Year == "2021") %>% select(Fco2) %>%
  summarise(sum(Fco2)) 
SW.co2.2021 <- input.daily %>% filter(wind.sector == "SW" & Year == "2021") %>% select(Fco2) %>%
  summarise(sum(Fco2)) 
SE.co2.2020 <- input.daily %>% filter(wind.sector == "SE" & Year == "2020") %>% select(Fco2) %>%
  summarise(sum(Fco2)) 
SW.co2.2020 <- input.daily %>% filter(wind.sector == "SW" & Year == "2020") %>% select(Fco2) %>%  
summarise (sum(Fco2))

# need to rename direction variable

NEco2.2020 <- -0.48/4
NEco2.2021 <- -2.09/5
NWco2.2020 <- 46.34/140
NWco2.2021 <- 30.67/132

SEco2.2020 <- -14.4/57
SEco2.2021 <- -49.31/55
SWco2.2020 <- -23.22/162
SWco2.2021 <- -82.32/169

Avg.wind.co2 <- data.frame(NEco2.2020, NEco2.2021, NWco2.2020, NWco2.2021,SEco2.2020, SEco2.2021,SWco2.2020, SWco2.2021) %>% pivot_longer(cols = NEco2.2020:SWco2.2021, names_to = "Windsec", )
Avg.wind.co2$Year <- ""
Avg.wind.co2$Year <- c("2020", "2021", "2020", "2021", "2020", "2021","2020", "2021")

Avg.wind.co2 %>% ggplot(aes(Windsec, value, group = Year)) + geom_line(aes(group = Year, colour = Year))

# NW is on  average a CO2 source and SE largest CO2 sinks
```

### 2022-08-01 scripts/Paper 1.Rmd
add detailed seasons, remove scale_color_manual(need to put new in with new year)

@@
         Precip = sum(Precip, na.rm = TRUE),
-        SWin = sum(SWin),
+        SWin = sum(SWin, na.rm=TRUE),
         Ta.mean = mean(Ta, na.rm = TRUE),
@@
 
-Grow21.22 <- input.daily[530:907,]
-Grow21.22$dayssinceJun1 <-1:378
+Grow21.22 <- input.daily[530:894,]
+Grow21.22$dayssinceJun1 <-1:365
 Grow21.22$GSYear <- "21/22"
 
-input.rearranged <- rbind(Grow19.20,Grow20.21, Grow21.22)
+Grow22.23 <- input.daily[895:945,]
+Grow22.23$dayssinceJun1 <-1:51
+Grow22.23$GSYear <- "22/23"
+
+input.rearranged <- rbind(Grow19.20,Grow20.21, Grow21.22, Grow22.23)
 input.rearranged$monthyear <- as.yearmon(paste(input.rearranged$month, input.rearranged$Year), "%m %Y")
@@
 ```{r}
-input.rearranged$season <- "" # add season variable
+#input.rearranged$season <- "" # add season variable
 
 # define seasons
-winter <- (input.rearranged$month.name == "Jun" | input.rearranged$month.name == "Jul" | input.rearranged$month.name == "Aug")
-spring <- (input.rearranged$month.name == "Sep" | input.rearranged$month.name == "Oct" | input.rearranged$month.name == "Nov")
-summer <- (input.rearranged$month.name == "Dec" | input.rearranged$month.name == "Jan" | input.rearranged$month.name == "Feb")
-autumn <- (input.rearranged$month.name == "Mar" | input.rearranged$month.name == "Apr" | input.rearranged$month.name == "May")
+#winter <- (input.rearranged$month.name == "Jun" | input.rearranged$month.name == "Jul" | input.rearranged$month.name == "Aug")
+#spring <- (input.rearranged$month.name == "Sep" | input.rearranged$month.name == "Oct" | input.rearranged$month.name == "Nov")
+#summer <- (input.rearranged$month.name == "Dec" | input.rearranged$month.name == "Jan" | input.rearranged$month.name == "Feb")
+#autumn <- (input.rearranged$month.name == "Mar" | input.rearranged$month.name == "Apr" | input.rearranged$month.name == "May")
 
-input.rearranged$season[winter] <- "Winter"
-input.rearranged$season[spring] <- "Spring"
-input.rearranged$season[summer] <- "Summer"
+#input.rearranged$season[winter] <- "Winter"
+#input.rearranged$season[spring] <- "Spring"
+#input.rearranged$season[summer] <- "Summer"
 #input.rearranged$season[latesummer] <- "LateSummer"
-input.rearranged$season[autumn] <- "Autumn"
+#input.rearranged$season[autumn] <- "Autumn"
 
-input.rearranged$season <- factor(input.rearranged$season , levels=c('Summer', 'Autumn', 'Winter', 'Spring'))
+#input.rearranged$season <- factor(input.rearranged$season , levels=c('Summer', 'Autumn', 'Winter', 'Spring'))
+```
+
+```{r six seasons}
+#This needs better confines - e.g. month where temps are > or < something
+
+input.rearranged$season.detail <- "" # add season variable
+
+# define seasons
+earlywinter <- (input.rearranged$month.name == "Jun" | input.rearranged$month.name == "May")
+latewinter <- (input.rearranged$month.name == "Jul" | input.rearranged$month.name == "Aug")
+spring <- (input.rearranged$month.name == "Sep" | input.rearranged$month.name == "Oct")
+earlysummer <- (input.rearranged$month.name == "Dec" | input.rearranged$month.name == "Nov")
+latesummer <- (input.rearranged$month.name == "Jan" | input.rearranged$month.name == "Feb")
+autumn <- (input.rearranged$month.name == "Mar" | input.rearranged$month.name == "Apr")
+
+input.rearranged$season.detail[latewinter] <- "LateWinter"
+input.rearranged$season.detail[earlywinter] <- "EarlyWinter"
+input.rearranged$season.detail[spring] <- "Spring"
+input.rearranged$season.detail[earlysummer] <- "EarlySummer"
+input.rearranged$season.detail[latesummer] <- "LateSummer"
+input.rearranged$season.detail[autumn] <- "Autumn"
+
+input.rearranged$season.detail <- factor(input.rearranged$season , levels=c('EarlySummer', 'LateSummer', 'Autumn', 'EarlyWinter', 'LateWinter', 'Spring'))
 ```
@@
 # define seasons
-winter <- (rainfall_L$month.name == "Jun" | rainfall_L$month.name == "Jul" | rainfall_L$month.name == "Aug")
-spring <- (rainfall_L$month.name == "Sep" | rainfall_L$month.name == "Oct" | rainfall_L$month.name == "Nov")
-summer <- (rainfall_L$month.name == "Dec" | rainfall_L$month.name == "Jan" | rainfall_L$month.name == "Feb")
-autumn <- (rainfall_L$month.name == "Mar" | rainfall_L$month.name == "Apr" | rainfall_L$month.name == "May")
+#winter <- (rainfall_L$month.name == "Jun" | rainfall_L$month.name == "Jul" | rainfall_L$month.name == "Aug")
+#spring <- (rainfall_L$month.name == "Sep" | rainfall_L$month.name == "Oct" | rainfall_L$month.name == "Nov")
+#summer <- (rainfall_L$month.name == "Dec" | rainfall_L$month.name == "Jan" | rainfall_L$month.name == "Feb")
+#autumn <- (rainfall_L$month.name == "Mar" | rainfall_L$month.name == "Apr" | rainfall_L$month.name == "May")
 
-rainfall_L$season[winter] <- "Winter"
-rainfall_L$season[spring] <- "Spring"
-rainfall_L$season[summer] <- "Summer"
-rainfall_L$season[autumn] <- "Autumn"
+#rainfall_L$season[winter] <- "Winter"
+#rainfall_L$season[spring] <- "Spring"
+#rainfall_L$season[summer] <- "Summer"
+#rainfall_L$season[autumn] <- "Autumn"
 
-rainfall_L$season <- factor(rainfall_L$season , levels=c('Summer', 'Autumn', 'Winter', 'Spring'))
+#rainfall_L$season <- factor(rainfall_L$season , levels=c('Summer', 'Autumn', 'Winter', 'Spring'))
+
+# define seasons
+earlywinter <- (rainfall_L$month.name == "Jun" | rainfall_L$month.name == "May")
+latewinter <- (rainfall_L$month.name == "Jul" | rainfall_L$month.name == "Aug")
+spring <- (rainfall_L$month.name == "Sep" | rainfall_L$month.name == "Oct")
+earlysummer <- (rainfall_L$month.name == "Dec" | rainfall_L$month.name == "Nov")
+latesummer <- (rainfall_L$month.name == "Jan" | rainfall_L$month.name == "Feb")
+autumn <- (rainfall_L$month.name == "Mar" | rainfall_L$month.name == "Apr")
+
+rainfall_L$season.detail[latewinter] <- "LateWinter"
+rainfall_L$season.detail[earlywinter] <- "EarlyWinter"
+rainfall_L$season.detail[spring] <- "Spring"
+rainfall_L$season.detail[earlysummer] <- "EarlySummer"
+rainfall_L$season.detail[latesummer] <- "LateSummer"
+rainfall_L$season.detail[autumn] <- "Autumn"
+
+rainfall_L$season.detail <- factor(rainfall_L$season , levels=c('EarlyWinter', 'LateWinter', 'Spring', "EarlySummer", "LateSummer", "Autumn"))
 ```
@@
 ```{r, fig.width=11, fig.height=4}
-season.colors <- c("Summer" = "#E69F00", "Autumn" = "#D55E00", "Winter" ="#0072B2", "Spring" = "#CC79A7")
+#season.colors <- c("Summer" = "#E69F00", "Autumn" = "#D55E00", "Winter" ="#0072B2", "Spring" = "#CC79A7")
 
-rainfall.SP <- input.rearranged %>% select(Precip, month, GSYear, season, Year, month.name)
+rainfall.SP <- input.rearranged %>% select(Precip, month, GSYear, season.detail, Year, month.name)
 
-rainfall <- rainfall_L %>% select(Precip, month, GSYear, season, Year, month.name) %>% rbind(., rainfall.SP)
+rainfall <- rainfall_L %>% select(Precip, month, GSYear, season.detail, Year, month.name) %>% rbind(., rainfall.SP)
 
@@
 (rainfall.season <- rainfall %>%  mutate(Precip = replace_na(Precip, 0)) %>%
-  ddply(c("GSYear", "season"), summarise,
+  ddply(c("GSYear", "season.detail"), summarise,
   seasonal.total = sum(Precip)) %>%
-  ggplot(., aes(x = GSYear, y = seasonal.total, group = GSYear, fill = season)) +
+  ggplot(., aes(x = GSYear, y = seasonal.total, group = GSYear, fill = season.detail)) +
        #scale_x_discrete(limits = month.abb) +
-  geom_col(aes(fill = season)) +
-        scale_fill_manual(values = season.colors)+
+  geom_col(aes(fill = season.detail)) +
+        #scale_fill_manual(values = season.colors)+
   ylab("Seasonal rainfall (mm)")+
@@
 rainfall.summary <- rainfall %>%  mutate(Precip = replace_na(Precip, 0)) %>%
-  ddply(c("GSYear", "season"), summarise,
+  ddply(c("GSYear", "season.detail"), summarise,
   seasonal.total = sum(Precip))

### 2022-08-01 scripts/Paper 1.Rmd
remove commit figs to this

@@
 rainfall.p
-tiff("rainfall.tiff", units="in", width=10, height=6,  res=300)
-print(rainfall.p)
-dev.off()
+#tiff("rainfall.tiff", units="in", width=10, height=6,  res=300)
+#print(rainfall.p)
+#dev.off()
 
@@
 TA
-tiff("TA.tiff", units="in", width=10, height=6,  res=300)
-print(TA)
-dev.off()
+#tiff("TA.tiff", units="in", width=10, height=6,  res=300)
+#print(TA)
+#dev.off()
 
 TS
-tiff("TS.tiff", units="in", width=10, height=6,  res=300)
-print(TS)
-dev.off()
+#tiff("TS.tiff", units="in", width=10, height=6,  res=300)
+#print(TS)
+#dev.off()
 ```
@@
 TA.sum.p
-tiff("TAbar.tiff", units="in", width=10, height=6,  res=300)
-print(TA.sum.p)
-dev.off()
+#tiff("TAbar.tiff", units="in", width=10, height=6,  res=300)
+#print(TA.sum.p)
+#dev.off()
 
@@
 TS.sum.p
-tiff("TSbar.tiff", units="in", width=10, height=6,  res=300)
-print(TS.sum.p)
-dev.off()
+#tiff("TSbar.tiff", units="in", width=10, height=6,  res=300)
+#print(TS.sum.p)
+#dev.off()
 
@@
   geom_line(aes(color = GSYear), size = 1)+
-    scale_color_manual(values = group.colour) +
+    #scale_color_manual(values = group.colour) +
  # scale_x_date(date_labels = "%b", date_breaks = "1 month") +
@@
   # scale_x_continuous()+
-    scale_color_manual(values=group.colour)+
+    #scale_color_manual(values=group.colour)+
   theme_classic() + 
@@
 NEE.bar
-tiff("NEEbar.tiff", units="in", width=10, height=6,  res=300)
-print(NEE.bar)
-dev.off()
+#tiff("NEEbar.tiff", units="in", width=10, height=6,  res=300)
+#print(NEE.bar)
+#dev.off()
 ```
@@
 GPP.bar
-tiff("GPPbar.tiff", units="in", width=10, height=6,  res=300)
-print(GPP.bar)
-dev.off()
+#tiff("GPPbar.tiff", units="in", width=10, height=6,  res=300)
+#print(GPP.bar)
+#dev.off()
 ```
@@
 ER.bar
-tiff("ERbar.tiff", units="in", width=10, height=6,  res=300)
-print(ER.bar)
-dev.off()
+#tiff("ERbar.tiff", units="in", width=10, height=6,  res=300)
+#print(ER.bar)
+#dev.off()
 ```
@@
 NEEcum.p
-tiff("NEEcum.tiff", units="in", width=10, height=6,  res=300)
-print(NEEcum.p)
-dev.off()
+#tiff("NEEcum.tiff", units="in", width=10, height=6,  res=300)
+#print(NEEcum.p)
+#dev.off()
 
@@
 GPPcum.p
-tiff("GPPcum.tiff", units="in", width=10, height=6,  res=300)
-print(GPPcum.p)
-dev.off()
+#tiff("GPPcum.tiff", units="in", width=10, height=6,  res=300)
+#print(GPPcum.p)
+#dev.off()
 
@@
 GPPtime.p
-tiff("GPPtime.tiff", units="in", width=10, height=6,  res=300)
-print(GPPtime.p)
-dev.off()
+#tiff("GPPtime.tiff", units="in", width=10, height=6,  res=300)
+#print(GPPtime.p)
+#dev.off()
 
@@
 ERcum.p
-tiff("ERcum.tiff", units="in", width=10, height=6,  res=300)
-print(ERcum.p)
-dev.off()
+#tiff("ERcum.tiff", units="in", width=10, height=6,  res=300)
+#print(ERcum.p)
+#dev.off()
 
@@
 ERtime.p
-tiff("ERtime.tiff", units="in", width=10, height=6,  res=300)
-print(ERtime.p)
-dev.off()
+#tiff("ERtime.tiff", units="in", width=10, height=6,  res=300)
+#print(ERtime.p)
+#dev.off()
 
@@
 Fig2
-tiff("Fig2.tiff", units="in", width=10, height=6,  res=300)
-print(Fig2)
-dev.off()
+#tiff("Fig2.tiff", units="in", width=10, height=6,  res=300)
+#print(Fig2)
+#dev.off()
 
@@
 GPP.bar.s
-tiff("GPPbar.tiff", units="in", width=10, height=6,  res=300)
-print(GPP.bar.s)
-dev.off()
+#tiff("GPPbar.tiff", units="in", width=10, height=6,  res=300)
+#print(GPP.bar.s)
+#dev.off()
 
@@
 ER.bar.s
-tiff("ERbar.tiff", units="in", width=10, height=6,  res=300)
-print(ER.bar.s)
-dev.off()
+#tiff("ERbar.tiff", units="in", width=10, height=6,  res=300)
+#print(ER.bar.s)
+#dev.off()
 

### 2022-10-24 scripts/paper1_v3.Rmd
update

---
title: "Paper1_V2"
author: "Marion Nyberg"
date: '2022-08-02'
output: html_document
theme: yeti 
---

```{r setup, include=FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(data.table)
library(janitor)
library(plotly)
library(plyr)
library(dplyr)
library(knitr)
library(tidyverse)
#library(devtools)
library(openair)
library(tidyr)
library(naniar)
library(forecast)
library(kableExtra)
library(htmltools)
library(ggpubr)
library(rstatix)
library(broom)
library(gtable)
library(gridExtra)
library(cowplot)
library(viridis)
library(zoo)
library(DT)
library(Hmisc)
library(MuMIn)
library(RColorBrewer)
#library(MASS)

rm(list = ls())
#wd <- ("R:/SET/PlantSci/Shared Work Spaces/Ecology/Flux/SP_data")
#setwd(wd)
#knitr::opts_knit$set(root.dir = wd)

#input <- fread("R:/SET/PlantSci/Shared Work Spaces/Ecology/Peoples files/Marion Nyberg/PhD/paperone.csv", drop = 1)

input <- fread("C:/Users/Marion/Documents/UTas/Papers/paperone_v2.csv", drop =1)
```

```{r functions and conversions, include=FALSE}
d.avg <- 1800 * 48 #60 secs * 60 mins * 24 hours (# of secs in day)
co2_conv <- 12.01/(10^6)

tidy.csv <- function(x){
  input <- x[-c(1,2),] %>%
    row_to_names(., 1)
}

gofC.f <- function(x){ # function to convert to mean 30 minute to g of C
  (x*d.avg)*co2_conv
}

gtomg.f <- function(x){ # function to convert from g to mg
  x*1000
}

quadratic_fun <- function(x){
  x^2
}
```

```{r weird stuff in data and corrections, include=FALSE}
input$SWC.corr <- ifelse(input$SWC >= 0.3, 0.6673*(input$SWC) + 0.2369, 
                         0.0944+2.511*(input$SWC)-4.8425*(input$SWC)^2)

input$SWin <- ifelse(input$SWin < 0, 0, input$SWin)
input$PAR <-ifelse(input$PAR <0, 0, input$PAR)

#input$PAR[which(is.na(input$PAR))] <- (-21.19 + 1.02*(input$SWin)) #not sure that this is right
correction.par<-input$PAR[which(is.na(input$PAR))]
input$PAR[correction.par] <-  replace_na(input$SWin[correction.par] * 4.5 * 0.5) # because NAs at same time can't fill using SWin?

plot(input$Timestamp, input$PAR)

```

```{r summarise data, include = FALSE}
# add variables to this daily df as needed
input.d <- input %>%
  drop_na(Timestamp) %>% # some NAs in the Timestamp for some reason. Need to look into
  ddply(c("Year", "jday", "month"), summarise,
        Precip = sum(Precip, na.rm = TRUE),
        SWin = sum(SWin),
        Ta.mean = mean(Ta, na.rm = TRUE),
        Ta.max = max(Ta, na.rm = TRUE),
        Ta.min = min(Ta, na.rm = TRUE),
        Ts.mean = mean(Ts, na.rm = TRUE),
        Ts.max = max(Ts, na.rm = TRUE),
        Ts.min = min(Ts, na.rm = TRUE),
        SWC = mean(SWC, na.rm = TRUE),
        SWC.corr = mean(SWC.corr, na.rm = TRUE),
        RH = mean(RH, na.rm = TRUE),
        VPD = mean(VPD, na.rm = TRUE),
        ET = sum(ET*60*30, na.rm = TRUE), # /second into daily total (60 sec/min * 30 mins for each timestamp)
        NEE_LT = mean(NEE_LT, na.rm = TRUE), #daily average umol m-2 s-1
        ER_LT = mean(ER_LT, na.rm = TRUE),
        ER_ngf = mean(ER_ngf, na.rm = TRUE),
        GPP_LT = mean(GPP_LT, na.rm = TRUE)) %>%
  mutate(NEE_LT.gC = gofC.f(NEE_LT),  #converts to daily total NEE in g C CO2
         ER_LT.gC = gofC.f(ER_LT),
         ER_ngf.gC = gofC.f(ER_ngf),
         GPP_LT.gC = gofC.f(GPP_LT))

input.d$month <- as.numeric(input.d$month) 
input.d$month.name <- month.abb[input.d$month]
input.d$date <- as.Date(with(input.d,paste(Year,month,jday,sep="-")),"%Y-%m-%j")
input.d$Year <- as.factor(input.d$Year)
```

```{r add days since June 1 variable, include = FALSE}
input.d$dayssinceJun1 <- ""

Grow19.20 <- input.d[1:164,]
Grow19.20$dayssinceJun1 <- 202:365
Grow19.20$GSYear <- "19/20"

Grow20.21 <- input.d[165:529,]
Grow20.21$dayssinceJun1 <- 1:365
Grow20.21$GSYear <- "20/21"

Grow21.22 <- input.d[530:894,]
Grow21.22$dayssinceJun1 <-1:365
Grow21.22$GSYear <- "21/22"

input.r <- rbind(Grow19.20,Grow20.21, Grow21.22)
input.r$monthyear <- as.yearmon(paste(input.r$month, input.r$Year), "%m %Y")

#start.time <- as.Date("2020-06-01", "%m-%d")
#end.time <- as.Date("2022-05-31", "%m-%d")
#start.end <- c(start.time, end.time)
```

```{r add seasons, include = FALSE}
input.r$season <- "" # add season variable

# define seasons (6)
earlywinter <- (input.r$month.name == "Jun" | input.r$month.name == "Jul")
latewinter <- (input.r$month.name == "Aug" | input.r$month.name == "Sep")
spring <- (input.r$month.name == "Oct" | input.r$month.name == "Nov")
earlysummer <- (input.r$month.name == "Dec" | input.r$month.name == "Jan")
latesummer <- (input.r$month.name == "Feb" | input.r$month.name == "Mar")
autumn <- (input.r$month.name == "Apr" |input.r$month.name == "May")

#input.r$season[earlywinter] <- "EarlyWinter"
#input.r$season[latewinter] <- "LateWinter"
#input.r$season[spring] <- "Spring"
#input.r$season[earlysummer] <- "EarlySummer"
#input.r$season[latesummer] <- "LateSummer"
#input.r$season[autumn] <- "Autumn"

#input.r$season <- factor(input.r$season , levels=c('EarlyWinter', 'LateWinter', 'Spring', 'EarlySummer', 'LateSummer', 'Autumn'))
#season.cols <- c('#91bfdb','#4575b4','#fee090', '#f46d43', '#d73027', '#8073ac')

# define seasons (4)
winter <- (input.r$month.name == "Jun" | input.r$month.name == "Jul" |input.r$month.name == "Aug")
spring <- (input.r$month.name == "Sep"| input.r$month.name == "Oct" | input.r$month.name == "Nov")
summer <- (input.r$month.name == "Dec" | input.r$month.name == "Jan" | input.r$month.name == "Feb")
autumn <- (input.r$month.name == "Mar" | input.r$month.name == "Apr" |input.r$month.name == "May")

input.r$season[winter] <- "Winter"
input.r$season[spring] <- "Spring"
input.r$season[summer] <- "Summer"
input.r$season[autumn] <- "Autumn"

input.r$season <- factor(input.r$season , levels=c('Winter', 'Spring', 'Summer', 'Autumn'))
season.cols <- c('#91bfdb','#fee090', '#f46d43', '#8073ac')
```

```{r add lagged variables anf offset variable, echo = FALSE}
input.r$GPP.monthLag <- Lag(input.r$GPP_LT.gC, shift = +30)
input.r$ER.monthLag <- Lag(input.r$ER_LT.gC, shift = +30)
input.r$GPP_offset <- input.r$GPP_LT.gC + 1.25
input.r$ER_ngf.gC <- ifelse(input.r$ER_ngf.gC <0, NA, input.r$ER_ngf.gC)

```

## Data {.tabset}

### Met/Env. variables {.tabset}

#### Air Temperature

```{r Temperature, echo = FALSE, fig.cap= "Mean daily air temperature at the Silver Plains EC tower. Dark line is mean, shading is mean max and min."}
(TA <- ggplot(input.d, aes(x = date, y = Ta.mean)) +
   geom_point(size = 0.001)+
   geom_line(size = 0.72)+
        geom_ribbon(aes(ymin=Ta.min, ymax=Ta.max), alpha=.3, linetype=0) +
    xlab("Date")+
    ylab("Air temperature (°C)")+
     scale_x_date(limit = c(as.Date("2019-06-01"), c(as.Date("2022-05-31"))), expand = c(0, 0))+
   #scale_x_date(limit=c(as.Date("2017-01-01"),as.Date("2017-02-11"))) 
  theme_classic()+
    theme(axis.title = element_text(size = 16),
          axis.text = element_text(size = 15),
          legend.text = element_text(size = 13),
          legend.title = element_text(size = 14)))
ggplotly(TA)

alltogher <- input.d %>% group_by(jday)  %>%
  summarise(mean(Ta.mean))

input.d %>% group_by(month, Year)  %>%
  summarise(mean(Ta.min))
```

```{r echo = FALSE, fig.cap= "Mean daily air temperature at the Silver Plains EC tower by growing season year"}
TA.GSYear <- ggplot(input.r, aes(x = dayssinceJun1, y = Ta.mean), group = GSYear) +
   #geom_point(aes(color = GSYear))+
   geom_line(aes(color = GSYear))+
        #geom_ribbon(aes(ymin=Ta.min, ymax=Ta.max), alpha=.3, linetype=0) +
    xlab("Days since June 1")+
    ylab("Air temperature (°C)")+
  theme_classic()+
    theme(axis.title = element_text(size = 14),
          axis.text = element_text(size = 13),
          legend.text = element_text(size = 13),
          legend.title = element_text(size = 14))

ggplotly(TA.GSYear)

```

#### Soil temperature

```{r soil temperature, echo = FALSE, fig.cap= "Mean daily soil temperature at 5cm at the Silver Plains EC tower. Dark line is mean, shading is mean max and min."}
(TS <- ggplot(input.d, aes(x = date, y = Ts.mean)) +
   geom_point(size = 0.001)+
   geom_line(size = 0.72)+
        geom_ribbon(aes(ymin=Ts.min, ymax=Ts.max), alpha=.3, linetype=0) +
        scale_x_date(limit = c(as.Date("2019-06-01"), c(as.Date("2022-05-31"))), expand = c(0, 0))+
    xlab("Date")+
    ylab("10-cm soil temperature (°C)")+
  theme_classic()+
    theme(axis.title = element_text(size = 16),
          axis.text = element_text(size = 15),
          legend.text = element_text(size = 13),
          legend.title = element_text(size = 14)))

input.d %>% group_by(month, Year) %>%
  summarise(mean(Ts.min))

alltogher <- input.d %>% group_by(jday)  %>%
  summarise(mean(Ts.mean))

```

```{r soil t, echo = FALSE}

(TS.GSYear <- ggplot(input.r, aes(x = dayssinceJun1, y = Ts.mean), group = GSYear) +
   #geom_point(aes(color = GSYear))+
   geom_line(aes(color = GSYear))+
        #geom_ribbon(aes(ymin=Ta.min, ymax=Ta.max), alpha=.3, linetype=0) +
    xlab("Days since June 1")+
    ylab("Air temperature (°C)")+
  theme_classic()+
    theme(axis.title = element_text(size = 14),
          axis.text = element_text(size = 13),
          legend.text = element_text(size = 13),
          legend.title = element_text(size = 14)))
```

#### Precipitation

```{r Precipitation, echo=FALSE, message = FALSE}
#below is precip data from liaweenee - it only goes up to Jan 2022 right now
rainfall_L <- read.csv("C:/Users/Marion/Documents/UTas/Papers/rainfall.csv")
#rainfall_L <- read.csv("G:/Other computers/My Laptop/Documents/UTas/Papers/rainfall.csv")
rainfall_L <- rainfall_L[-4]
colnames(rainfall_L)[4] <- "Precip"
rainfall_L$Year <- as.factor(rainfall_L$Year)
rainfall_L <- rainfall_L %>% filter(Year == 2019)
colnames(rainfall_L)[1] <- "jday"
colnames(rainfall_L)[3] <- "month"
rainfall_L$Site <- "L"
rainfall_L <- rainfall_L %>% filter(month >= 6)
rainfall_L$month <- as.numeric(rainfall_L$month) 
rainfall_L$month.name<- month.abb[rainfall_L$month]
rainfall_L$GSYear <- "19/20"

#earlywinter <- (rainfall_L$month.name == "Jun" | rainfall_L$month.name == "Jul")
#latewinter <- (rainfall_L$month.name == "Aug" | rainfall_L$month.name == "Sep")
#spring <- (rainfall_L$month.name == "Oct" | rainfall_L$month.name == "Nov")
#earlysummer <- (rainfall_L$month.name == "Dec" | rainfall_L$month.name == "Jan")
#latesummer <- (rainfall_L$month.name == "Feb" | rainfall_L$month.name == "Mar")
#autumn <- (rainfall_L$month.name == "Apr" |rainfall_L$month.name == "May")

#rainfall_L$season[earlywinter] <- "EarlyWinter"
#rainfall_L$season[latewinter] <- "LateWinter"
#rainfall_L$season[spring] <- "Spring"
#rainfall_L$season[earlysummer] <- "EarlySummer"
#rainfall_L$season[latesummer] <- "LateSummer"
#rainfall_L$season[autumn] <- "Autumn"

# define seasons (4)
winter <- (rainfall_L$month.name == "Jun" | rainfall_L$month.name == "Jul" |rainfall_L$month.name == "Aug")
spring <- (rainfall_L$month.name == "Sep"| rainfall_L$month.name == "Oct" | rainfall_L$month.name == "Nov")
summer <- (rainfall_L$month.name == "Dec" | rainfall_L$month.name == "Jan" | rainfall_L$month.name == "Feb")
autumn <- (rainfall_L$month.name == "Mar" | rainfall_L$month.name == "Apr" |rainfall_L$month.name == "May")

rainfall_L$season[winter] <- "Winter"
rainfall_L$season[spring] <- "Spring"
rainfall_L$season[summer] <- "Summer"
rainfall_L$season[autumn] <- "Autumn"

rainfall_L$season <- factor(rainfall_L$season , levels=c('Winter', 'Spring', 'Summer', 'Autumn'))
season.cols <- c('#91bfdb','#fee090', '#f46d43', '#8073ac')

rainfall.SP <- input.r %>% select(Precip, month, GSYear, season, Year, month.name)
rainfall <- rainfall_L %>% select(Precip, month, GSYear, season, Year, month.name) %>% rbind(., rainfall.SP)

#rainfall$season <- factor(rainfall$season , levels=c('EarlyWinter', 'LateWinter', 'Spring', 'EarlySummer', 'LateSummer', 'Autumn'))
rainfall$season <- factor(rainfall$season , levels=c('Winter', 'Spring', 'Summer', 'Autumn'))

rainfall$monthyear <- as.yearmon(paste(rainfall$month, rainfall$Year), "%m %Y")

(rainfall.p <-rainfall %>%  mutate(Precip = replace_na(Precip, 0)) %>%
  ddply(c("monthyear", "Year"), summarise,
  monthly.total = sum(Precip)) %>%
  ggplot(., aes(x = monthyear, y = monthly.total)) +
  geom_col(position = "dodge") +
  scale_x_yearmon(n = 7, expand = c(0,0))+
  ylab("Monthly rainfall (mm)")+
  xlab("Date")+
  theme_classic()+
    theme(axis.title = element_text(size = 16),
          axis.text = element_text(size = 15),
          legend.text = element_text(size = 13),
          legend.title = element_text(size = 14),
          #axis.text.x = element_text( vjust = 0.5)
        ))

alltogherrain <- rainfall%>% group_by(GSYear, month)  %>%
  summarise(sum(Precip, na.rm = TRUE))
```

```{r Precip, echo=FALSE, fig.align='left'}
(rainfall.season <- rainfall %>%  mutate(Precip = replace_na(Precip, 0)) %>%
  ddply(c("GSYear", "season"), summarise,
  seasonal.total = sum(Precip)) %>%
  ggplot(., aes(x = GSYear, y = seasonal.total, group = GSYear, fill = season)) +
       #scale_x_discrete(limits = month.abb) +
  geom_col(aes(fill = season)) +
        #scale_fill_manual(values = season.colors)+
  ylab("Seasonal rainfall (mm)")+
  xlab("Growing season year")+
  theme_classic()+
    theme(axis.title = element_text(size = 14),
          axis.text = element_text(size = 13),
          legend.text = element_text(size = 13),
          legend.title = element_text(size = 14)))

```

```{r, echo=FALSE}
rainfall %>%  mutate(Precip = replace_na(Precip, 0)) %>%
  ddply(c("GSYear", "season"), summarise,
  seasonal.total = sum(Precip)) %>%
  datatable(rownames = FALSE, colnames = c("Year", "Season", "Total Precipitation"), class = "hover")  %>%
    formatRound(columns=c('seasonal.total'), digits=3)
 # kbl(col.names = c("Year", "Season", "Total precipitation"), centering = F) %>%
#  kable_minimal( )
```

#### SWC

```{r SWC, echo=FALSE}
(SWC.20 <- input.r  %>% ggplot(., aes(dayssinceJun1, SWC.corr), group = GSYear) +
  geom_line(aes(color = GSYear))+
   scale_x_continuous(limits = c(1, 365))+
  xlab('Days since June 1st') +
        ylab(bquote('SWC ('~m^-3~'/'~m^-3~')'))+
    #scale_color_manual(values=group.colour)+
  theme_classic() + 
    theme(axis.title = element_text(size = 14),
          axis.text = element_text(size = 13)))

(SWC.time <- ggplot(input.d, aes(x = date, y = SWC.corr)) +
   geom_point(size = 0.001)+
   geom_line(size = 0.72)+
    xlab("Date")+
         scale_x_date(limit = c(as.Date("2019-06-01"), c(as.Date("2022-05-31"))), expand = c(0, 0))+
ylab(bquote('SWC ('~m^-3~'/'~m^-3~')'))+
  theme_classic()+
    theme(axis.title = element_text(size = 16),
          axis.text = element_text(size = 15),
          legend.text = element_text(size = 13),
          legend.title = element_text(size = 14)))

SWC <- input.r %>% group_by(GSYear, month)  %>%
  summarise(mean(SWC, na.rm = TRUE))
```

#### Incoming SW radiation

```{r SWin, echo=FALSE, fig.cap= "Total daily incoming SW radiation."}
(SWin <- input.d %>% filter(SWin > 0) %>% ggplot(., aes(x = date, y = SWin)) +
   geom_line()+
    xlab("Date")+
    ylab("Incoming SW radiation (W m-2)")+
  theme_classic()+
    theme(axis.title = element_text(size = 14),
          axis.text = element_text(size = 13),
          legend.text = element_text(size = 13),
          legend.title = element_text(size = 14)))

```

```{r SW, echo=FALSE, fig.cap= "Total daily incoming SW radiation by growing season year."}
SWin.GSYear <- input.r %>% filter(SWin >0 ) %>% ggplot(., aes(x = dayssinceJun1, y = SWin), group = GSYear) +
   #geom_point(aes(color = GSYear))+
   geom_line(aes(color = GSYear))+
        #geom_ribbon(aes(ymin=Ta.min, ymax=Ta.max), alpha=.3, linetype=0) +
    xlab("Days since June 1")+
    ylab("Incoming SW radiation (W m-2)")+
  theme_classic()+
    theme(axis.title = element_text(size = 14),
          axis.text = element_text(size = 13),
          legend.text = element_text(size = 13),
          legend.title = element_text(size = 14))

ggplotly(SWin.GSYear)
```

#### Evapotranspiration

```{r ET, echo=FALSE, , fig.cap= "Total daily evapotranspiration."}
input.r %>% select(ET ,dayssinceJun1, GSYear) %>% 
  group_by(GSYear) %>% 
   ddply(c("GSYear"), summarise,
  annual.total = sum(ET)) %>%
  datatable(colnames = c("Year", "Total ET"), class = "compact")%>%
    formatRound(columns=c('annual.total'), digits=3)

(ET <- input.d %>% ggplot(., aes(x = date, y = ET)) +
   geom_line()+
         scale_x_date(limit = c(as.Date("2019-06-01"), c(as.Date("2022-05-31"))), expand = c(0, 0))+
    xlab("Date")+
    ylab("Daily total ET (mm) ")+
  theme_classic()+
    theme(axis.title = element_text(size = 16),
          axis.text = element_text(size = 15),
          legend.text = element_text(size = 13),
          legend.title = element_text(size = 14)))

ET.GSYear <- input.r  %>% ggplot(., aes(dayssinceJun1, ET), group = GSYear) +
  geom_line(aes(color = GSYear))+
   scale_x_continuous(limits = c(1, 365))+
  xlab('Days since June 1st') +
        ylab("Daily total ET (mm)")+
    #scale_color_manual(values=group.colour)+
  theme_classic() + 
    theme(axis.title = element_text(size = 14),
          axis.text = element_text(size = 13),
          legend.position = "none")

ggplotly(ET.GSYear)

(ET.season <- input.r %>% 
  ddply(c("GSYear", "season"), summarise,
  seasonal.total = sum(ET)) %>%
  ggplot(., aes(x = GSYear, y = seasonal.total, group = GSYear, fill = season)) +
       #scale_x_discrete(limits = month.abb) +
  geom_col(aes(fill = season)) +
        #scale_fill_manual(values = season.colors)+
  ylab("Seasonal evapotranspiration")+
  xlab("Growing season year")+
  theme_classic()+
    theme(axis.title = element_text(size = 14),
          axis.text = element_text(size = 13),
          legend.text = element_text(size = 13),
          legend.title = element_text(size = 14)))

ET <- input.r %>% group_by(GSYear, month)  %>%
  summarise(sum(ET, na.rm = TRUE))
```

### CO2 fluxes {.tabset}

#### NEE {.tabset}

```{r timeseries fluxes, echo = FALSE}
(NEEtime.p <-input.r%>%
  ggplot(., aes(dayssinceJun1, NEE_LT.gC, color = GSYear)) +
  geom_line()+
        #scale_color_manual(values = group.colour)+
       scale_x_continuous(limits = c(1, 365))+

  ylab(bquote(' NEE (g C ' ~m^-2~')'))+
  xlab("Days since June 1st")+
  theme_classic()+ 
    theme(axis.title = element_text(size = 14),
          axis.text = element_text(size = 13)))
```

```{r cumulative fluxes, echo = FALSE, message=FALSE}
cum.co2fluxes <- input.r %>%
  select(NEE_LT.gC, GPP_LT.gC, ER_LT.gC, dayssinceJun1, GSYear, season) %>% 
  group_by(GSYear) %>% 
  mutate(NEEcum = cumsum(NEE_LT.gC),
         GPPcum = cumsum(GPP_LT.gC),
         ERcum = cumsum(ER_LT.gC))

cum.co2fluxes$season <- factor(cum.co2fluxes$season, levels=c("Winter", "Spring", "Summer", "Autumn"))

(NEEcum.p <-cum.co2fluxes %>% 
  ggplot(., aes(dayssinceJun1, NEEcum, group = GSYear, color = GSYear)) +
  geom_line(size = 1, aes(color = GSYear))+
   # scale_color_manual(values = group.colour)+
       scale_x_continuous(limits = c(1, 365))+
  ylab(bquote('Cumulative NEE (g C ' ~m^-2~')'))+
  xlab("Days since June 1st")+
  theme_classic()+ 
    theme(axis.title = element_text(size = 14),
          axis.text = element_text(size = 13)))

#CO2 <- cum.co2fluxes %>% group_by(GSYear)  %>% filter (season == "Spring" | season == "EarlySummer" | season == "LateSummer") %>%
 #   summarise(sum(NEE_LT.gC))

#CO2.winter <- cum.co2fluxes %>% group_by(GSYear)  %>% filter (season == "EarlyWinter" | season == "LateWinter" | season == "Autumn") %>%
  #  summarise(sum(NEE_LT.gC))
```
### check data

```{r check distribution}
library(MASS)
library(ggpubr)
#GPP
qqnorm(input.r$GPP_offset)
bc <- boxcox(input.r$GPP_offset ~ input.r$Ta.mean)
(lambda <- bc$x[which.max(bc$y)])

GPP.1 <- lm((GPP_offset^lambda-1)/lambda~Ta.mean, input.r)
GPP.1log <- lm(log(GPP_offset)~Ta.mean, input.r)

#hist((input.r$GPP_offset^lambda-1)) # Positive / right skewed
qqnorm(GPP.1$residuals)
qqline(GPP.1$residuals)

qqnorm(GPP.1log$residuals)
qqline(GPP.1log$residuals)
# For GPP could be log or lambda value

#ER
qqnorm(input.r$ER_ngf.gC)

bc <- boxcox(input.r$ER_ngf.gC ~ input.r$Ts.mean)
(lambda <- bc$x[which.max(bc$y)])

ER.1 <- lm((ER_ngf.gC^lambda-1)/lambda~Ts.mean, input.r)
ER.1log <- lm(log(ER_ngf.gC)~Ts.mean, input.r)

hist((input.r$ER_ngf.gC^lambda-1)/lambda) # Positive / right skewed
hist(log(input.r$ER_ngf.gC))
qqnorm(ER.1$residuals)
qqline(ER.1$residuals)

qqnorm(ER.1log$residuals)
qqline(ER.1log$residuals)
```

#### GPP

__Seasonal total GPP__

```{r GPP, echo = FALSE, message=FALSE}

GPP.summary<- cum.co2fluxes %>% select(GPP_LT.gC,dayssinceJun1, GSYear, season) %>% 
  group_by(GSYear, season) %>% 
   ddply(c("GSYear", "season"), summarise,
  seasonal.total = sum(GPP_LT.gC))

cum.co2fluxes$season <- factor(cum.co2fluxes$season, levels=c("Autumn", "Summer", "Spring", "Winter"))
#cum.co2fluxes$season <- factor(cum.co2fluxes$season , levels=c('Autumn', 'LateSummer', 'EarlySummer', 'Spring', 'LateWinter', 'EarlyWinter'))

(GPP.bar.s <- cum.co2fluxes  %>%
  ggplot(., aes(fill = season, x = GSYear, y = GPP_LT.gC)) +
  #geom_col(aes(fill = season)) + 
    geom_bar(position = "stack", stat = "identity") +
         #scale_x_discrete(limits = start.end)+
  xlab("Growing season year")+
         ylab(bquote('Total seasonal GPP (g C ' ~m^-2~')'))+
    #scale_fill_manual(values = season.colors)+
  theme_classic()) +
  theme(axis.title = element_text(size = 14),
          axis.text = element_text(size = 13),
          legend.text = element_text(size = 13),
          legend.title = element_text(size = 14))

GPP <- cum.co2fluxes %>% group_by(GSYear)  %>% filter (season == "Spring" | season == "EarlySummer" | season == "LateSummer") %>%
    summarise(sum(GPP_LT.gC))

GPP.winter <- cum.co2fluxes %>% group_by(GSYear)  %>% filter (season == "EarlyWinter" | season == "LateWinter" | season == "Autumn") %>%
    summarise(sum(GPP_LT.gC))

```

__Daily mean GPP and env. variables__

```{r daily GPP env, eval=FALSE, message=FALSE, include=FALSE}
ggplot(input.r, aes(SWC, GPP_LT.gC)) +
  geom_point(aes(color = season))+
  geom_smooth(method = lm, aes(color = season))+
 scale_x_continuous(breaks = c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9))+
  ylab("Daily mean GPP (g C m-2)")+
  xlab('Mean daily SWC')+
  theme_classic()

ggplot(input.r, aes(ET, GPP_LT.gC)) +
  geom_point(aes(color = season))+
  geom_smooth(method = lm, aes(color = season))+
  ylab("Daily mean GPP (g C m-2)")+
  xlab('Total daily ET')+
 #scale_x_continuous(breaks = c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9))+
  theme_classic()

```

__Monthly GPP__

```{r monthly GPP env, echo = FALSE, message = FALSE, fig.height=8, fig.width=7}
season.cols <- c('#4575b4', '#f46d43', '#d73027', '#8073ac')

summary.month<- input.r %>% dplyr::select(GPP_LT.gC, GPP_offset, ER_LT.gC, ER_ngf.gC, dayssinceJun1, GSYear, season, month, ET, SWC.corr, Precip, Ta.mean, Ts.mean, SWin) %>% 
  group_by(GSYear, month) %>% 
   ddply(c("GSYear", "season", "month"), summarise,
  GPP = sum(GPP_LT.gC),
  GPP_offset = sum(GPP_offset),
  ER = sum(ER_LT.gC),
  ET = sum(ET),
  SWC = mean(SWC.corr),
  Precip = sum(Precip),
  TA = mean(Ta.mean),
  TS = mean(Ts.mean), 
  SWin = mean(SWin))

#ggplot(GPP.summary.month, aes(ET.month, seasonal.total)) +
 # geom_point(aes(color = season))+
  ##geom_smooth(method = lm, aes(color = season))+
  #ylab("Daily mean GPP (g C m-2)")+
  #xlab('Total daily ET')+
 #scale_x_continuous(breaks = c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9))+
  #theme_classic()

(TA.GPP <- ggplot(summary.month, aes(TA, GPP)) +
  geom_point(aes(color = GSYear), size = 4) +
  geom_smooth(method = "lm", se = F, aes(color = GSYear)) +
  #geom_smooth(span = 1.5, color = "black", se = F) +
                 ylab(bquote('GPP  (g C ' ~m^-2~'' ~month^-1~')'))+
    xlab("Air temperature (°C)")+
    ggtitle("a") +
    scale_color_manual(values = season.cols) + 
  theme_classic() +
    theme(axis.text = element_text(size = 12),
         axis.title = element_text(size = 13)))

TS.GPP <- ggplot(summary.month, aes(TS, GPP)) +
  geom_point(aes(color = season)) +
  geom_smooth(method = "lm", se = F, aes(color = season)) +
    scale_color_manual(values = season.cols) + 
  theme_classic()+
   theme(axis.text = element_text(size = 12),
         axis.title = element_text(size = 13))

P.GPP <- ggplot(summary.month, aes(Precip, GPP)) +
  geom_point(aes(color = season)) +
    geom_smooth(method = "lm", se = F, aes(color = season)) +
    scale_color_manual(values = season.cols) + 
  theme_classic()

(ET.GPP <- ggplot(summary.month, aes(ET, GPP)) +
  geom_point(aes(color = GSYear), size = 4) +
    geom_smooth(method = "lm", se = F, aes(color = GSYear)) +
  #geom_smooth(span = 1.3, color = "black", se = F) +
    scale_color_manual(values = season.cols) + 
               ylab(bquote('GPP  (g C ' ~m^-2~'' ~month^-1~')'))+
        xlab("ET (mm)") +
    ggtitle("c") +
  theme_classic()+
   theme(axis.text = element_text(size = 12),
         axis.title = element_text(size = 13),
         legend.key.size = unit(1, 'cm'),
        legend.title = element_text(size = 13),
        legend.text = element_text(size = 13))+
    guides(color=guide_legend(title="Year")))

(SWC.GPP <- ggplot(summary.month, aes(SWC, GPP)) +
  geom_point(aes(color = GSYear), size = 4) +
   # geom_smooth(span = 1.3, se = F, aes(color = GSYear)) +
    stat_smooth(method = lm, formula = y ~ poly(x, 2, raw = TRUE), se = F, aes(color = GSYear)) +
  #geom_smooth(span = 1.3, color = "black", se = F) +
    scale_color_manual(values = season.cols) + 
               ylab(bquote('GPP  (g C ' ~m^-2~'' ~month^-1~')'))+
            xlab(bquote('SWC ('~m^-3~'/'~m^-3~')'))+
    ggtitle("b") +
  theme_classic()+
   theme(axis.text = element_text(size = 12),
         axis.title = element_text(size = 13)))

(SWin.GPP <- ggplot(summary.month, aes(SWin, GPP)) +
  geom_point(aes(color = GSYear), size = 4) +
  #geom_smooth(span = 1.3, color = "black", se = F) + 
    geom_smooth(method = "lm", se = F, aes(color = GSYear)) +
    scale_color_manual(values = season.cols) + 
                 ylab(bquote('GPP (g C ' ~m^-2~'' ~month^-1~')'))+
    xlab(bquote('Incoming SW radiation (W' ~m^-2~')')) + 
  theme_classic()+
   theme(axis.text = element_text(size = 12),
         axis.title = element_text(size = 13)))

GPP.leg.month <- get_legend(ET.GPP)

GPP.env.plots <- plot_grid(TS.GPP + theme(legend.position = 'none'), 
          ET.GPP+ theme(legend.position = 'none'), SWC.GPP+ theme(legend.position = 'none'), SWin.GPP+ theme(legend.position = 'none'), GPP.leg.month, ncol = 2)

```

__GPP lagged by 1 month__

```{r lag GPP, , echo = FALSE, message = FALSE, eval = FALSE, fig.height=8, fig.width=7} 
TA.GPPL <- ggplot(summary.month, aes(TA, GPPlag)) +
  geom_point(aes(color = season)) +
  geom_smooth(method = "lm", se = F, aes(color = season)) +
    scale_color_manual(values = season.cols) + 
  theme_classic()

TS.GPPL <- ggplot(summary.month, aes(TS, GPPlag)) +
  geom_point(aes(color = season)) +
  geom_smooth(method = "lm", se = F, aes(color = season)) +
    scale_color_manual(values = season.cols) + 
  theme_classic()

P.GPPL <- ggplot(summary.month, aes(Precip, GPPlag)) +
  geom_point(aes(color = season)) +
    geom_smooth(method = "lm", se = F, aes(color = season)) +
    scale_color_manual(values = season.cols) + 
  theme_classic()

ET.GPPL <- ggplot(summary.month, aes(ET, GPPlag)) +
  geom_point(aes(color = season)) +
    geom_smooth(method = "lm", se = F, aes(color = season)) +
    scale_color_manual(values = season.cols) + 
  theme_classic()

SWC.GPPL <- ggplot(summary.month, aes(SWC, GPPlag)) +
  geom_point(aes(color = season)) +
    geom_smooth(method = "lm", se = F, aes(color = season)) +
    scale_color_manual(values = season.cols) + 
  theme_classic()

SWin.GPPL <- ggplot(summary.month, aes(SWin, GPPlag)) +
  geom_point(aes(color = season)) +
    geom_smooth(method = "lm", se = F, aes(color = season)) +
    scale_color_manual(values = season.cols) + 
  theme_classic()

plot_grid(TA.GPPL + theme(legend.position = 'none'), TS.GPPL + theme(legend.position = 'none'), 
          P.GPPL + theme(legend.position = 'none'), 
          ET.GPPL+ theme(legend.position = 'none'), SWC.GPPL+ theme(legend.position = 'none'), SWin.GPPL+ theme(legend.position = 'none'), GPP.leg.month, ncol = 2)
```

#### ER

__Seasonal total ER__

```{r ER, echo = FALSE, message=FALSE}

ER.summary<- cum.co2fluxes %>% select(ER_LT.gC,dayssinceJun1, GSYear, season) %>% 
  group_by(GSYear, season) %>% 
   ddply(c("GSYear", "season"), summarise,
  seasonal.total = sum(ER_LT.gC))

cum.co2fluxes$season <- factor(cum.co2fluxes$season, levels=c("Autumn", "Summer", "Spring", "Winter"))
#cum.co2fluxes$season <- factor(cum.co2fluxes$season , levels=c('Autumn', 'LateSummer', 'EarlySummer', 'Spring', 'LateWinter', 'EarlyWinter'))

(ER.bar.s <- cum.co2fluxes  %>%
  ggplot(., aes(fill = season, x = GSYear, y = ER_LT.gC)) +
  #geom_col(aes(fill = season)) + 
    geom_bar(position = "stack", stat = "identity") +
         #scale_x_discrete(limits = start.end)+
  xlab("Growing season year")+
         ylab(bquote('Total seasonal  (g C ' ~m^-2~')'))+
    #scale_fill_manual(values = season.colors)+
  theme_classic()) +
  theme(axis.title = element_text(size = 14),
          axis.text = element_text(size = 13),
          legend.text = element_text(size = 13),
          legend.title = element_text(size = 14))

ER <- cum.co2fluxes %>% group_by(GSYear)  %>% filter (season == "Spring" | season == "EarlySummer" | season == "LateSummer") %>%
    summarise(sum(ER_LT.gC))

ER.winter <- cum.co2fluxes %>% group_by(GSYear)  %>% filter (season == "EarlyWinter" | season == "LateWinter" | season == "Autumn") %>%
    summarise(sum(ER_LT.gC))

```

__Daily mean ER and env. variables__

```{r daily ER env, echo=FALSE, message=FALSE}
ggplot(input.r, aes(SWC, ER_LT.gC)) +
  geom_point(aes(color = season))+
  geom_smooth(method = lm, aes(color = season))+
 scale_x_continuous(breaks = c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9))+
  ylab("Daily mean ER (g C m-2)")+
  xlab('Mean daily SWC')+
  theme_classic()

ggplot(input.r, aes(Ts.mean, ER_LT.gC)) +
  geom_point(aes(color = season))+
  #geom_smooth(method = lm, aes(color = season))+
 scale_x_continuous(breaks = c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9))+
  ylab("Daily mean ER (g C m-2)")+
  xlab('Mean daily SWC')+
  theme_classic()

ggplot(input.r, aes(ET, ER_LT.gC)) +
  geom_point(aes(color = season))+
  #geom_smooth(method = lm, aes(color = season))+
  ylab("Daily mean ER (g C m-2)")+
  xlab('Total daily ET')+
 #scale_x_continuous(breaks = c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9))+
  theme_classic()

```

__Monthly mean ER__

```{r monthly ER env, echo = FALSE, message = FALSE, fig.height=8, fig.width=7}
season.cols <- c('#4575b4', '#f46d43', '#d73027', '#8073ac')

#ggplot(ER.summary.month, aes(ET.month, seasonal.total)) +
 # geom_point(aes(color = season))+
  ##geom_smooth(method = lm, aes(color = season))+
  #ylab("Daily mean ER (g C m-2)")+
  #xlab('Total daily ET')+
 #scale_x_continuous(breaks = c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9))+
  #theme_classic()

(TA.ER <- ggplot(summary.month, aes(TA, ER)) +
  geom_point(aes(color = GSYear)) +
  geom_smooth(method = "lm", se = F, aes(color = GSYear)) +
  scale_color_manual(values = season.cols) + 
  theme_classic()+
   theme(axis.text = element_text(size = 12),
         axis.title = element_text(size = 13)))

(TS.ER <- ggplot(summary.month, aes(TS, ER)) +
  geom_point(aes(color = GSYear), size = 4) +
  geom_smooth(method = "lm", span = 1.3, se = F, aes(color = GSYear)) +
    #geom_smooth(span  = 1.3, se = F, color = "black") +
    scale_color_manual(values = season.cols) + 
             ylab(bquote('ER  (g C ' ~m^-2~'' ~month^-1~')'))+
    xlab("10-cm soil temperature (°C)")+
  theme_classic() +
   theme(axis.text = element_text(size = 12),
         axis.title = element_text(size = 13)))

P.ER <- ggplot(summary.month, aes(Precip, ER)) +
  geom_point(aes(color = season)) +
    geom_smooth(method = "lm", se = F, aes(color = season)) +
    scale_color_manual(values = season.cols) + 
  theme_classic()+
   theme(axis.text = element_text(size = 12),
         axis.title = element_text(size = 13))

(ET.ER <- ggplot(summary.month, aes(ET, ER)) +
  geom_point(aes(color = GSYear), size = 4) +
    geom_smooth(method = "lm", span = 1.3, se = F, aes(color = GSYear)) +
    #geom_smooth(span = 1.3, se = F, color = "black") +
    scale_color_manual(values = season.cols) + 
                 ylab(bquote('ER  (g C ' ~m^-2~'' ~month^-1~')'))+
    xlab("ET (mm)") +
  theme_classic()+
  theme(legend.key.size = unit(1, 'cm'),
        legend.title = element_text(size = 13),
        legend.text = element_text(size = 13))+
   theme(axis.text = element_text(size = 12),
         axis.title = element_text(size = 13))+
    guides(color=guide_legend(title="Season")))

SWCER.int <- -2.63 
SWCER.coeff1 <- 15.39 
SWCER.coeff2 <- -13.84

(SWC.ER <- ggplot(summary.month, aes(SWC, ER)) +
  geom_point(aes(color = GSYear), size = 4) +
    #geom_smooth(span = 1.5, se = F, aes(color = GSYear)) +
    #stat_function(fun=function(x) SWCER.int +(SWCER.coeff1*x) + x^2)+
   #geom_smooth(span = 1, se = F, color = "black")+
    stat_smooth(method = lm, formula = y ~  poly(x, 2, raw = TRUE), se = F, aes(color = GSYear)) + 
    scale_color_manual(values = season.cols) + 
                 ylab(bquote('ER  (g C ' ~m^-2~'' ~month^-1~')'))+
            xlab(bquote('SWC ('~m^-3~'/'~m^-3~')'))+
  theme_classic()+
   theme(axis.text = element_text(size = 12),
         axis.title = element_text(size = 13)))

ER.leg.month <- get_legend(ET.ER)

(ER.env.plots <- plot_grid(TS.ER + theme(legend.position = 'none'), 
          ET.ER+ theme(legend.position = 'none'),SWC.ER+ theme(legend.position = 'none'), ER.leg.month, ncol = 2))

```

### For publication

```{r for publication climatic, fig.height = 12, fig.width= 12}

#plot_grid(ER.TS5.P.d + theme(legend.position = 'none', axis.title.y = element_text(margin = margin(r = 0))), ER.WTH.P + #theme(legend.position = 'none'), p2a_legend,
 #                 Temp.logCH4D+ theme(legend.position = 'none', axis.title.y = element_text(margin = margin(r = 5))), WTH.logCH4D + #theme(legend.position = 'none', axis.title.y = element_text(margin = margin(r = 5))), NULL,
 #                
  #         hjust = -1,
   #        nrow = 2, ncol = 3, rel_widths = c(1,1, 0.3), rel_heights = c(1,1))

(climate.plots <- plot_grid(
  TA+ theme(axis.title.y = element_text(margin = margin(r = 18)), axis.title.x = element_blank(), axis.text.x = element_blank()), 
  TS + theme(axis.title.y = element_text(margin = margin(r = 22)), axis.text.x = element_blank(), axis.title.x = element_blank()), 
  rainfall.p + theme(axis.title.y = element_text(margin = margin(r = 13)), axis.text.x = element_blank(), axis.title.x = element_blank()),
  SWC.time + theme(axis.title.y = element_text(margin = margin(r = 8)), axis.title.x = element_blank(), axis.text.x = element_blank()),
  ET+ theme(axis.title.y = element_text(margin = margin(r = 29))),
   ncol = 1, rel_heights = c(0.2,.2, 0.2, 0.2, 0.25)))

tiff("climate.tiff", units="in", width=15, height=15,  res=300)
print(climate.plots)
dev.off()
```

```{r for publication cumulative and daily co2}
GSYear.cols <- c('#f46d43', '#4575b4', '#91bfdb')

(NEEcum.p <-cum.co2fluxes %>% 
  ggplot(., aes(dayssinceJun1, NEEcum, group = GSYear, color = GSYear)) +
  geom_line(size = 1, aes(color = GSYear))+
   # scale_color_manual(values = group.colour)+
       scale_x_continuous(limits = c(1, 365))+
    scale_color_manual(values = GSYear.cols)+
  ylab(bquote('Cumulative NEE (g C ' ~m^-2~')'))+
  xlab("Days since June 1st")+
  theme_classic()+ 
    theme(axis.title = element_text(size = 14),
          axis.text = element_text(size = 13)))

monthlycumsum <- input.r %>%
  select(NEE_LT.gC, GPP_LT.gC, ER_LT.gC, dayssinceJun1, GSYear, season, month) %>% 
  group_by(GSYear, month) %>% 
  ddply(c("month", "GSYear"), summarise,
        NEE = sum(NEE_LT.gC),
         GPP = sum(GPP_LT.gC),
         ER = sum(ER_LT.gC),
        GPPneg = -1*sum(GPP_LT.gC))

monthlycumsum$month <- as.factor(monthlycumsum$month)
monthlycumsum$month <- factor(monthlycumsum$month, levels=c('6', '7', '8', '9', '10', '11', '12', '1', '2', '3', '4','5'))

(NEE.month.p <- monthlycumsum %>%
  ggplot(., aes(x = month, y = NEE, group = GSYear, fill = GSYear)) +
  geom_col(position = position_dodge2(preserve = 'single')) +
  scale_fill_manual(values = GSYear.cols) + 
  scale_x_discrete(labels = c("June", "July", "August", "September", "October", "November", "December", "January", "Febuary", "March", "April", "May")) + 
  xlab("Month")+
      ylab(bquote(' NEE (g C ' ~m^-2~')'))+
    ggtitle("a") +
  theme_classic()+
  theme(axis.text.x = element_text(angle = 45, vjust = 0.7),
        legend.key.size = unit(0.5, 'cm'),
        legend.title = element_text(size = 13),
        legend.text = element_text(size = 13),
        axis.text = element_text(size = 12),
        axis.title = element_text(size = 13))+
    guides(fill=guide_legend(title="Growing season year")))

NEE.leg.month <- get_legend(NEE.month.p)

(GPP.month.p <- monthlycumsum %>%
  ggplot(., aes(x = month, y = GPPneg, group = GSYear, fill = GSYear)) +
  geom_col(position = position_dodge2(preserve = 'single')) +
  scale_fill_manual(values = GSYear.cols) + 
  scale_x_discrete(labels = c("June", "July", "August", "September", "October", "November", "December", "January", "Febuary", "March", "April", "May")) + 
  xlab("Month")+
    ylab("GPP")+
      ylab(bquote(' GPP (g C ' ~m^-2~')'))+
    ggtitle("b")+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 45, vjust = 0.7),
        axis.text = element_text(size = 12),
         axis.title = element_text(size = 13)))

tiff("GPPmonth.tiff", units="in", width=25, height=30,  res=300)
print(GPP.month.p)
dev.off()

(ER.month.p <- monthlycumsum %>%
  ggplot(., aes(x = month, y = ER, group = GSYear, fill = GSYear)) +
  geom_col(position = position_dodge2(preserve = 'single')) +
  scale_fill_manual(values = GSYear.cols) + 
  scale_x_discrete(labels = c("June", "July", "August", "September", "October", "November", "December", "January", "Febuary", "March", "April", "May")) +  
  xlab("Month")+
      ylab(bquote(' ER (g C ' ~m^-2~')'))+
    ggtitle("c") +
  theme_classic()+
  theme(axis.text.x = element_text(angle = 45, vjust = 0.7),
        axis.text = element_text(size = 12),
         axis.title = element_text(size = 13)))

(CO2fluxes <- plot_grid(NEE.month.p + theme(legend.position = 'none', axis.title.x = element_blank(), axis.text.x = element_blank(), axis.title.y = element_text(margin = margin(r = 9))), NULL,
          GPP.month.p + theme(legend.position = 'none', axis.title.x = element_blank(), axis.text.x = element_blank()), NEE.leg.month,
          ER.month.p + theme(legend.position = 'none', axis.title.y = element_text(margin = margin(r = 6))), NULL,
          ncol = 2, rel_heights = c(0.27, 0.27, 0.35), rel_widths = c(0.7, 0.3)))

tiff("CO2fluxesmonthly.tiff", units="in", width=10, height=10,  res=300)
print(CO2fluxes)
dev.off()
```

```{r for publication env co2, fig.height = 12, fig.width= 10}
#season.cols <- c('#91bfdb','#4575b4','#fee090', '#f46d43', '#d73027', '#8073ac')
season.cols <- c('#4575b4', '#f46d43', '#d73027', '#8073ac')

plot_grid(TS.GPP + theme(legend.position = 'none'), 
          P.GPP + theme(legend.position = 'none'), 
          ET.GPP+ theme(legend.position = 'none'), SWC.GPP+ theme(legend.position = 'none'), SWin.GPP+ theme(legend.position = 'none'), GPP.leg.month, ncol = 2)

tiff("ERenv.tiff", units="in", width=10, height=12,  res=300)
print(ER.env.plots)
dev.off()

tiff("GPPenv.tiff", units="in", width=10, height=12,  res=300)
print(GPP.env.plots)
dev.off()

GPPER.env.plots <- plot_grid(TA.GPP + theme(legend.position = 'none'), TS.ER + theme(legend.position = 'none'),
          SWC.GPP + theme(legend.position = 'none'), SWC.ER + theme(legend.position = 'none'),
          ET.GPP+ theme(legend.position = 'none'), ET.ER + theme(legend.position = 'none'),
          SWin.GPP+ theme(legend.position = 'none'), GPP.leg.month,
          ncol = 2)

tiff("GPPERenv.tiff", units="in", width=10, height=12,  res=300)
print(GPPER.env.plots)
dev.off()
```

```{r models with RECO}

#Annual average
#Q10.RECO<- lm(log(ER_LT.gC)~Ts.mean, data = input.r)
Q10.RECO<- lm(log(ER_ngf.gC)~Ts.mean, data = input.r)
summary(Q10.RECO)
lnQ10 <- exp(10*0.1)

#19/20
input.1920 <- input.r %>% filter(GSYear == "19/20")
monthly.1920 <- summary.month %>% filter(GSYear == "19/20")
Q10.RECO.1920<- lm(log(ER_ngf.gC)~Ts.mean, data = input.1920)
summary(Q10.RECO.1920)
lnQ10.1920 <- exp(10*0.05)

#20/21
input.2021 <- input.r %>% filter(GSYear == "20/21")
monthly.2021 <- summary.month %>% filter(GSYear == "20/21")
Q10.RECO.2021<- lm(log(ER_ngf.gC)~Ts.mean, data = input.2021)
summary(Q10.RECO.2021)
lnQ10.2021 <- exp(10*0.11)

#21/22
input.2122 <- input.r %>% filter(GSYear == "21/22")
monthly.2122 <- summary.month %>% filter(GSYear == "21/22")
Q10.RECO.2122<- lm(log(ER_ngf.gC)~Ts.mean, data = input.2122)
summary(Q10.RECO.2122)
lnQ10 <- exp(10*0.11)

ks.test(input.r$ER_LT.gC, "pnorm") # results suggest data does not come from a normal distribution
hist(log(input.r$ER_LT.gC))

model.1 <- lm(log(ER_ngf.gC)~Ts.mean+GSYear, data = input.r)
summary(model.1)
# log(ER) = 0.11 + 0.10 (Ts)

model.2 <- lm(log(ER_LT.gC)~SWC.corr, data = input.r)
summary(model.2)
# log(ER) = 2 - 1.24 * (SWC)

input.r$SWC2 <- input.r$SWC.corr^2
model.2.p <- lm(log(ER_LT.gC)~SWC.corr+SWC2, data = input.r)
summary(model.2.p)
# log(ER) = -2.63 + 15.39 (SWC)- 13.84 (SWC^2)

model.3 <- lm(log(ER_LT.gC)~ET, data = input.r)
summary(model.3) 
# log(ER) = 0.68 + 0.34 * (ET)

model.sel(model.1, model.2, model.3)

# 19/20 daily
SWC.ER1920 <- lm(log(ER_ngf.gC) ~  SWC.corr, data = input.1920)
SWC.ER1920.1 <- lm(log(ER_ngf.gC) ~  SWC.corr + I(SWC.corr^2), data = input.1920)
SWC.ER1920.2 <- lm(log(ER_ngf.gC) ~  SWC.corr * I(SWC.corr^2), data = input.1920)
summary(SWC.ER1920)
model.sel(SWC.ER1920, SWC.ER1920.1, SWC.ER1920.2)

plot(input.1920$SWC.corr, log(input.1920$ER_ngf.gC))

SWCTs.ER <- lm(log(ER_LT.gC) ~ SWC.corr + Ts.mean, data = input.1920)
SWCTs.ER.1 <- lm(log(ER_LT.gC) ~ SWC.corr * Ts.mean, data = input.1920)
SWCTs.ER.2 <- lm(log(ER_LT.gC) ~ SWC.corr * I(SWC^2) + Ts.mean, data = input.1920)
SWCTs.ER.3 <- lm(log(ER_LT.gC) ~ SWC.corr * I(SWC^2) * Ts.mean, data = input.1920)
summary(SWCTs.ER.2)
model.sel(SWCTs.ER,SWCTs.ER.1, SWCTs.ER.2, SWCTs.ER.3)

# 20/21
SWC.ER2021 <- lm(log(ER_ngf.gC) ~  SWC.corr, data = input.2021)
SWC.ER2021.1 <- lm(log(ER_ngf.gC) ~  SWC.corr + I(SWC.corr^2), data = input.2021)
SWC.ER2021.2 <- lm(log(ER_ngf.gC) ~  SWC.corr * I(SWC.corr^2), data = input.2021)
summary(SWC.ER2021.2)
model.sel(SWC.ER2021, SWC.ER2021.1, SWC.ER2021.2)

# 21/22
SWC.ER2122 <- lm(log(ER_ngf.gC) ~  SWC.corr, data = input.2122)
SWC.ER2122.1 <- lm(log(ER_ngf.gC) ~  SWC.corr + I(SWC.corr^2), data = input.2122)
SWC.ER2122.2 <- lm(log(ER_ngf.gC) ~  SWC.corr * I(SWC.corr^2), data = input.2122)
summary(SWC.ER2122.2)
model.sel(SWC.ER2122, SWC.ER2122.1, SWC.ER2122.2)
```

```{r models with GPP}
cor.test(input.r$Ta.mean, input.r$Ts.mean) #Air temp and soil temp are sig. correlated

ks.test(log(input.r$GPP_LT.gC), "pnorm")
hist(log(input.r$GPP_offset))
GPP.lm1 <- lm(log(GPP_offset) ~ Ta.mean, input.r)

GPP.model.all <- lm(GPP_LT.gC ~ SWC.corr * Ta.mean, input.r)
Anova(GPP.model.all)

options(na.action = "na.fail")
m1 <- dredge(GPP.model.all)
subset(m1, delta < 4)

#19/20
GPP.TA1920 <- lm(log(GPP_offset)~Ta.mean, input.1920)
summary(GPP.TA1920)

SWC.GPP1920 <- lm(log(GPP_offset) ~  SWC.corr, data = input.1920)
# lnGPP = 1.67 - 0.84(SWC)
SWC.GPP1920.1 <- lm(log(GPP_offset) ~  SWC.corr + I(SWC.corr^2), data = input.1920)
SWC.GPP1920.2 <- lm(log(GPP_offset) ~  SWC.corr * I(SWC.corr^2), data = input.1920)
summary(SWC.GPP1920)
model.sel(SWC.GPP1920, SWC.GPP1920.1, SWC.GPP1920.2)

GPP.ET1920 <- lm(log(GPP_offset)~ET, input.1920)
summary(GPP.ET1920)

#20/21
GPP.TA2021 <- lm(log(GPP_offset)~Ta.mean, input.2021)
summary(GPP.TA2021)

SWC.GPP2021 <- lm(log(GPP_offset) ~  SWC.corr, data = input.2021)
SWC.GPP2021.1 <- lm(log(GPP_offset) ~  SWC.corr + I(SWC.corr^2), data = input.2021)
SWC.GPP2021.2 <- lm(log(GPP_offset) ~  SWC.corr * I(SWC.corr^2), data = input.2021)
# lnGPP = 203.54 - 933.83(SWC) + 1431.47(SWC^2) - 726.19(SWC * SWC^2)
summary(SWC.GPP2021.2)
model.sel(SWC.GPP2021, SWC.GPP2021.1, SWC.GPP2021.2)

GPP.ET2021 <- lm(log(GPP_offset)~ET, input.2021)
summary(GPP.ET2021)

#21/22
GPP.TA2122 <- lm(log(GPP_offset)~Ta.mean, input.2122)
summary(GPP.TA2122)

SWC.GPP2122 <- lm(log(GPP_offset) ~  SWC.corr, data = input.2122)
SWC.GPP2122.1 <- lm(log(GPP_offset) ~  SWC.corr + I(SWC.corr^2), data = input.2122)
SWC.GPP2122.2 <- lm(log(GPP_offset) ~  SWC.corr * I(SWC.corr^2), data = input.2122)
# lnGPP = 15.82 - 78.15(SWC) + 141.88(SWC^2) - 83.61(SWC * SWC^2)
summary(SWC.GPP2122.2)
model.sel(SWC.GPP2122, SWC.GPP2122.1, SWC.GPP2122.2)

GPP.ET2122 <- lm(log(GPP_offset)~ET, input.2122)
summary(GPP.ET2122)

# all years together
SWC.GPP <- lm(log(GPP_offset) ~  SWC.corr + GSYear, data = input.r)
SWC.GPP.1 <- lm(log(GPP_offset) ~  SWC.corr + I(SWC.corr^2) + GSYear, data = input.r)
SWC.GPP.2 <- lm(log(GPP_offset) ~  SWC.corr * I(SWC.corr^2), data = input.r)
summary(SWC.GPP.1)
model.sel(SWC.GPP, SWC.GPP.1, SWC.GPP.2)

```

```{r more GPP plots, fig.width = 16, fig.height=6}
season.cols <- c('#4575b4', '#f46d43', '#d73027', '#8073ac')

(TA.GPP.1920 <- ggplot(input.1920, aes(Ta.mean, GPP_offset)) +
  geom_point(aes(color = season), size = 3) +
  geom_smooth(method = "lm", se = F, aes(color = season)) +
    ylim(0,15) + 
    scale_color_manual(values = c('#d73027', '#8073ac'))+
  #geom_smooth(span = 1.5, color = "black", se = F) +
                 ylab(bquote('GPP  (g C ' ~m^-2~'' ~month^-1~')'))+
    xlab("Air temperature (°C)")+
  theme_classic() +
    theme(axis.text = element_text(size = 12),
         axis.title = element_text(size = 13)))

(TA.GPP.2021 <- ggplot(input.2021, aes(Ta.mean, GPP_offset)) +
  geom_point(aes(color = season), size = 3) +
  geom_smooth(method = "lm", se = F, aes(color = season)) +
        ylim(0,15) + 
  #geom_smooth(span = 1.5, color = "black", se = F) +
                 ylab(bquote('GPP  (g C ' ~m^-2~'' ~month^-1~')'))+
    xlab("Air temperature (°C)")+
    scale_color_manual(values = season.cols) + 
  theme_classic() +
    theme(axis.text = element_text(size = 12),
         axis.title = element_text(size = 13)))

(TA.GPP.2122 <- ggplot(input.2122, aes(Ta.mean, GPP_offset)) +
  geom_point(aes(color = season), size = 3) +
  geom_smooth(method = "lm", se = F, aes(color = season)) +
        ylim(0,15) + 
  #geom_smooth(span = 1.5, color = "black", se = F) +
                 ylab(bquote('GPP  (g C ' ~m^-2~'' ~month^-1~')'))+
    xlab("Air temperature (°C)")+
    scale_color_manual(values = season.cols) + 
  theme_classic() +
    theme(axis.text = element_text(size = 12),
         axis.title = element_text(size = 13)))

(SWC.GPP <- ggplot(monthly.1920, aes(SWC, GPP)) +
  geom_point(aes(color = season), size = 3) +
   # geom_smooth(span = 1.3, se = F, aes(color = GSYear)) +
    stat_smooth(method = lm, formula = y ~ poly(x, 2, raw = TRUE), se = F, aes(color = season)) +
  #geom_smooth(span = 1.3, color = "black", se = F) +
    scale_color_manual(values = season.cols) + 
               ylab(bquote('GPP  (g C ' ~m^-2~'' ~month^-1~')'))+
            xlab(bquote('SWC ('~m^-3~'/'~m^-3~')'))+
  theme_classic()+
   theme(axis.text = element_text(size = 12),
         axis.title = element_text(size = 13)))

plot_grid(TA.GPP.1920, TA.GPP.2021, TA.GPP.2122, ncol = 3)

win.ER <- (input.r %>%filter(season =="Winter") %>% ggplot(., aes(Ta.mean, GPP_offset)) +
  geom_point(aes(color = GSYear), size = 3) +
  geom_smooth(method = "lm", span = 1.3, se = F, aes(color = GSYear)) +
    ylim(0,10)+
       xlim(0,10)+
    #geom_smooth(span  = 1.3, se = F, color = "black") +
    scale_color_manual(values = c('#f46d43','#d73027'))+
             ylab(bquote('ER  (g C ' ~m^-2~'' ~month^-1~')'))+
    xlab("10-cm soil temperature (°C)")+
    ggtitle("Winter") +
  theme_classic() +
   theme(axis.text = element_text(size = 12),
         axis.title = element_text(size = 13)))

spr.ER <- (input.r %>%filter(season =="Spring") %>% ggplot(., aes(Ta.mean, GPP_offset)) +
  geom_point(aes(color = GSYear), size = 3) +
  geom_smooth(method = "lm", span = 1.3, se = F, aes(color = GSYear)) +
    ylim(0,10)+
       xlim(0,15)+
    #geom_smooth(span  = 1.3, se = F, color = "black") +
    scale_color_manual(values = c('#f46d43','#d73027'))+
             ylab(bquote('ER  (g C ' ~m^-2~'' ~month^-1~')'))+
    xlab("10-cm soil temperature (°C)")+
    ggtitle("Spring") +
  theme_classic() +
   theme(axis.text = element_text(size = 12),
         axis.title = element_text(size = 13)))

sum.ER <- (input.r %>%filter(season =="Summer") %>% ggplot(., aes(Ta.mean, GPP_offset)) +
  geom_point(aes(color = GSYear), size = 3) +
  geom_smooth(method = "lm", span = 1.3, se = F, aes(color = GSYear)) +
    ylim(0,10)+
       xlim(10,15)+
    #geom_smooth(span  = 1.3, se = F, color = "black") +
    scale_color_manual(values = season.cols) + 
             ylab(bquote('ER  (g C ' ~m^-2~'' ~month^-1~')'))+
    xlab("10-cm soil temperature (°C)")+
    ggtitle("Summer") +
  theme_classic() +
   theme(axis.text = element_text(size = 12),
         axis.title = element_text(size = 13)))

aut.ER <- (input.r %>%filter(season =="Autumn") %>% ggplot(., aes(Ta.mean, GPP_offset)) +
  geom_point(aes(color = GSYear), size = 3) +
  geom_smooth(method = "lm", span = 1.3, se = F, aes(color = GSYear)) +
    ylim(0,15)+
       xlim(4,15)+
    #geom_smooth(span  = 1.3, se = F, color = "black") +
    scale_color_manual(values = season.cols) + 
             ylab(bquote('ER  (g C ' ~m^-2~'' ~month^-1~')'))+
    xlab("10-cm soil temperature (°C)")+
    ggtitle("Autumn") +
  theme_classic() +
   theme(axis.text = element_text(size = 12),
         axis.title = element_text(size = 13)))

(seasonal.plots <- plot_grid(win.ER, spr.ER, sum.ER, aut.ER, ncol = 2))

```

```{r more ER plots, fig.width=16, fig.height=6}
(TS.ER.1920 <- ggplot(input.1920, aes(Ts.mean, ER_LT.gC)) +
  geom_point(aes(color = season), size = 3) +
  geom_smooth(method = "lm", span = 1.3, se = F, aes(color = season)) +
       ylim(0,15)+
   xlim(0,20)+
    #geom_smooth(span  = 1.3, se = F, color = "black") +
    scale_color_manual(values = c('#d73027', '#8073ac'))+
             ylab(bquote('ER  (g C ' ~m^-2~'' ~month^-1~')'))+
    xlab("10-cm soil temperature (°C)")+
   ggtitle("19/20") + 
  theme_classic() +
   theme(axis.text = element_text(size = 12),
         axis.title = element_text(size = 13)))

(TS.ER.2021 <- ggplot(input.2021, aes(Ts.mean, ER_LT.gC)) +
  geom_point(aes(color = season), size =3) +
  geom_smooth(method = "lm", span = 1.3, se = F, aes(color = season)) +
        ylim(0,15)+
       xlim(0,20)+
    #geom_smooth(span  = 1.3, se = F, color = "black") +
    scale_color_manual(values = season.cols) + 
             ylab(bquote('ER  (g C ' ~m^-2~'' ~month^-1~')'))+
    xlab("10-cm soil temperature (°C)")+
    ggtitle("20/21") +
  theme_classic() +
   theme(axis.text = element_text(size = 12),
         axis.title = element_text(size = 13)))

(TS.ER.2122 <- ggplot(input.2122, aes(Ts.mean, ER_LT.gC)) +
  geom_point(aes(color = season), size = 3) +
  geom_smooth(method = "lm", span = 1.3, se = F, aes(color = season)) +
    ylim(0,15)+
       xlim(0,20)+
    #geom_smooth(span  = 1.3, se = F, color = "black") +
    scale_color_manual(values = season.cols) + 
             ylab(bquote('ER  (g C ' ~m^-2~'' ~month^-1~')'))+
    xlab("10-cm soil temperature (°C)")+
    ggtitle("21/22") +
  theme_classic() +
   theme(axis.text = element_text(size = 12),
         axis.title = element_text(size = 13)))

plot_grid(TS.ER.1920, TS.ER.2021, TS.ER.2122, ncol = 3)

win.ER <- (input.r %>%filter(season =="Winter") %>% ggplot(., aes(Ts.mean, ER_LT.gC)) +
  geom_point(aes(color = GSYear), size = 3) +
  geom_smooth(method = "lm", span = 1.3, se = F, aes(color = GSYear)) +
    ylim(0,10)+
       xlim(0,10)+
    #geom_smooth(span  = 1.3, se = F, color = "black") +
    scale_color_manual(values = c('#f46d43','#d73027'))+
             ylab(bquote('ER  (g C ' ~m^-2~'' ~day^-1~')'))+
    xlab("10-cm soil temperature (°C)")+
    ggtitle("Winter") +
  theme_classic() +
   theme(axis.text = element_text(size = 12),
         axis.title = element_text(size = 13)))

spr.ER <- (input.r %>%filter(season =="Spring") %>% ggplot(., aes(Ts.mean, ER_LT.gC)) +
  geom_point(aes(color = GSYear), size = 3) +
  geom_smooth(method = "lm", span = 1.3, se = F, aes(color = GSYear)) +
    ylim(0,10)+
       xlim(0,15)+
    #geom_smooth(span  = 1.3, se = F, color = "black") +
    scale_color_manual(values = c('#f46d43','#d73027'))+
             ylab(bquote('ER  (g C ' ~m^-2~'' ~day^-1~')'))+
    xlab("10-cm soil temperature (°C)")+
    ggtitle("Spring") +
  theme_classic() +
   theme(axis.text = element_text(size = 12),
         axis.title = element_text(size = 13)))

sum.ER <- (input.r %>%filter(season =="Summer") %>% ggplot(., aes(Ts.mean, ER_LT.gC)) +
  geom_point(aes(color = GSYear), size = 3) +
  geom_smooth(method = "lm", span = 1.3, se = F, aes(color = GSYear)) +
    ylim(0,10)+
       xlim(10,15)+
    #geom_smooth(span  = 1.3, se = F, color = "black") +
    scale_color_manual(values = season.cols) + 
             ylab(bquote('ER  (g C ' ~m^-2~'' ~day^-1~')'))+
    xlab("10-cm soil temperature (°C)")+
    ggtitle("Summer") +
  theme_classic() +
   theme(axis.text = element_text(size = 12),
         axis.title = element_text(size = 13)))

aut.ER <- (input.r %>%filter(season =="Autumn") %>% ggplot(., aes(Ts.mean, ER_LT.gC)) +
  geom_point(aes(color = GSYear), size = 3) +
  geom_smooth(method = "lm", span = 1.3, se = F, aes(color = GSYear)) +
    ylim(0,15)+
       xlim(4,15)+
    #geom_smooth(span  = 1.3, se = F, color = "black") +
    scale_color_manual(values = season.cols) + 
             ylab(bquote('ER  (g C ' ~m^-2~'' ~day^-1~')'))+
    xlab("10-cm soil temperature (°C)")+
    ggtitle("Autumn") +
  theme_classic() +
   theme(axis.text = element_text(size = 12),

              axis.title = element_text(size = 13)))
```

```{r fig.width 12, fig.height = 12}
seasonal.plots <- plot_grid(win.ER, spr.ER, sum.ER, aut.ER, ncol = 2)

tiff("seasonaler.tiff", units="in", width=12, height=10,  res=300)
print(seasonal.plots)
dev.off()
```

```{r calculating flux footprint, include = FALSE}
# using the online tool: https://footprint.kljun.net/

# first need to organise data in format suitable for uploading

# variables needed: 
# yyyy = Year
# mm = Month [1‐12]
# day = Day of month [1‐31]
# HH = Hour [0‐23] or [1‐24] – has to be in UTC, NOT local time
# MM = Minutes, for example [0 30]
# zm = Measurement height above ground [m]
# d = Displacement height [m]
# z0 = Roughness length [m] ‐ enter [‐999] if not known
# u_mean = Mean wind speed at zm [ms‐1] ‐ enter [‐999] if not known
# L = Obukhov length [m]
# sigma_v = Standard deviation of lateral velocity fluctuations after rotation [ms‐1]
# u_star = Friction velocity [ms‐1]  
# wind_dir = Wind direction in degrees (of 360) for rotation of the footprint

FFP <- input %>% select(Timestamp, Year, month,L,WS, sigma_v,  WD, ustar, L)
#FFP[2:13] <- as.data.frame(sapply(FFP[2:13], as.numeric)) # convert data frame from character to numeric

FFP$HH_UTC <- format(as.POSIXct(FFP$Timestamp), format = "%H")
FFP$MM <- format(as.POSIXct(FFP$Timestamp), format = "%M")
FFP$day <- format(as.POSIXct(FFP$Timestamp), format = "%d")

FFP$zm <- "2.5"
names(FFP)[3] <- "mm"
names(FFP)[2] <- "yyyy"
names(FFP)[5] <- "u_mean"
names(FFP)[6] <- "sigma_v"
names(FFP)[7] <- "wind_dir"
names(FFP)[8] <- "u_star"
FFP$d <- "0.07362071"
FFP$z0 <- "-999"
FFP <- FFP[, -1]
FFP[is.na(FFP)] <- "-999" # change NA to -999 to comply with data format
FFP <- as.data.frame(sapply(FFP, as.numeric)) # convert data frame from character to numeric

FFP <- FFP[, c(1, 2, 3, 9,10,  11, 12, 13, 4, 8, 5,7, 6)] # change variable order to comply with data format

meanmm  <- FFP %>% select(zm, d, L, z0, u_mean, sigma_v, wind_dir, u_star, mm, day, HH_UTC, MM) %>% ddply(c("mm","day", "HH_UTC", "MM"), summarise,
                                                                                                 zm = mean(zm), 
                                                                                                 d = mean(d),
                                                                                                 z0 = mean(z0),
                                                                                                 u_mean = mean(u_mean),
                                                                                                 L = mean(L),
                                                                                                 sigma_v = mean(sigma_v),
                                                                                                 u_star = mean(u_star),
                                                                                                 wind_dir = mean(wind_dir)
                                                                                                 )

meanmm$yyyy <- "2022"
meanmm <- meanmm[, c(13, 1, 2, 3,4, 5, 6, 7, 8, 9, 10, 11, 12)] # change variable order to comply with data format

meanmm$zmL <-  meanmm$zm/meanmm$L

FFP.GS <- meanmm %>% filter(mm ==  "12")
FFP.NGS <- meanmm %>% filter(mm == "4" |mm ==  "5" |mm ==  "6" |mm ==  "7" |mm ==  "8" |mm ==  "9")

#write.csv(FFP.GS, 'G:/Other computers/My Laptop/Documents/UTas/FluxProcessing_SP/Data/GS.csv', row.names = FALSE)
#write.csv(FFP.NGS, 'G:/Other computers/My Laptop/Documents/UTas/FluxProcessing_SP/Data/NGS.csv', row.names = FALSE)

#write.csv(FFP.2021.GS, 'G:/Other computers/My Laptop/Documents/UTas/FluxProcessing_SP/Data/FFP2021GS.csv', row.names = FALSE)

#the full output file isn't working with the website. When I subset to ~2 months where there are no -999 values except in z0, the online modelling tool works. 
```

```{r missing data}
input.met <- input[,c(2:17)]
summary(input.met)
(sum(is.na(input.met)))/42866 # 9% of met data missing over 2.5 years

(sum(is.na(input$ER_ngf)))/42866
```

### 2022-10-25 scripts/getL6data.R
add FFP variables

@@ -1,0 +1,64 @@
+
+library(data.table)
+library(janitor)
+library(plotly)
+library(plyr)
+library(dplyr)
+library(knitr)
+library(tidyverse)
+#library(devtools)
+library(openair)
+library(tidyr)
+library(naniar)
+library(forecast)
+library(kableExtra)
+library(htmltools)
+library(ggpubr)
+library(rstatix)
+library(broom)
+library(gtable)
+library(gridExtra)
+library(cowplot)
+library(viridis)
+library(zoo)
+
+rm(list = ls())
+
+
+#Below are conversion factors and functions used in the markdown file:
+d.avg <- 1800 * 48 #60 secs * 60 mins * 24 hours (# of secs in day)
+co2_conv <- 12.01/(10^6) 
+
+tidy.csv <- function(x){
+  input <- x[-c(1,2),] %>%
+    row_to_names(., 1)
+}  
+
+gofC.f <- function(x){ # function to convert to mean 30 minute to g of C
+  (x*d.avg)*co2_conv
+}
+
+gtomg.f <- function(x){ # function to convert from g to mg
+  x*1000
+}
+
+
+input <- fread("R:/SET/PlantSci/Shared Work Spaces/Ecology/Flux/SP_data/PFP/L6/SilverPlains_L6.csv", header = FALSE, na.strings = "-9999") 
+input <- tidy.csv(input)
+
+input <- input %>% dplyr::select(xlDateTime, Fe, Fg_Av, Fh, Fld, Flu, Fn, Fsu, Fsd, Precip, RH, Sws, Ta, Ts, VPD, Wd_SONIC_Av, Ws_SONIC_Av,ER_LT_all, GPP_LT,GPP_SOLO, NEE_LT, ET, ER, PAR, ustar, L, Uy_SONIC_Sd) # select variables (add more as needed)
+colnames(input) <- c('Timestamp', 'LE', 'G', 'H', 'LWin', 'LWout', 'NETRAD', 'SWout', 'SWin', 'Precip', 'RH', 'SWC', 'Ta', 'Ts', 'VPD', 'WD', 'WS', 'ER_LT', 'GPP_LT', 'GPP_SOLO', 'NEE_LT', 'ET', 'ER_ngf', 'PAR', 'u_star', 'L', 'sigma_v')
+
+input$Timestamp <- as.POSIXct(input$Timestamp, format= "%d/%m/%Y %H:%M") # change from character to POSIXct
[…]

### 2022-10-27 scripts/paper1_v3.Rmd
CUP

@@
 #input$PAR[which(is.na(input$PAR))] <- (-21.19 + 1.02*(input$SWin)) #not sure that this is right
-correction.par<-input$PAR[which(is.na(input$PAR))]
-input$PAR[correction.par] <-  replace_na(input$SWin[correction.par] * 4.5 * 0.5) # because NAs at same time can't fill using SWin?
-
-plot(input$Timestamp, input$PAR)
+#correction.par<-input$PAR[which(is.na(input$PAR))]
+#input$PAR[correction.par] <-  replace_na(input$SWin[correction.par] * 4.5 * 0.5) # because NAs at same time can't fill using SWin?
+
+#plot(input$Timestamp, input$PAR)
 
@@
 spring <- (input.r$month.name == "Sep"| input.r$month.name == "Oct" | input.r$month.name == "Nov")
-summer <- (input.r$month.name == "Dec" | input.r$month.name == "Jan" | input.r$month.name == "Feb")
-autumn <- (input.r$month.name == "Mar" | input.r$month.name == "Apr" |input.r$month.name == "May")
+summer <- (input.r$month.name == "Dec" | input.r$month.name == "Jan" | input.r$month.name == "Feb" | input.r$month.name =="Mar")
+autumn <- (input.r$month.name == "Apr" |input.r$month.name == "May")
 
@@
 ```{r add lagged variables anf offset variable, echo = FALSE}
-input.r$GPP.monthLag <- Lag(input.r$GPP_LT.gC, shift = +30)
-input.r$ER.monthLag <- Lag(input.r$ER_LT.gC, shift = +30)
+#input.r$GPP.monthLag <- Lag(input.r$GPP_LT.gC, shift = +30)
+#input.r$ER.monthLag <- Lag(input.r$ER_LT.gC, shift = +30)
 input.r$GPP_offset <- input.r$GPP_LT.gC + 1.25
@@
 
-GPP.summary<- cum.co2fluxes %>% select(GPP_LT.gC,dayssinceJun1, GSYear, season) %>% 
+GPP.summary<- cum.co2fluxes %>% dplyr::select(GPP_LT.gC,dayssinceJun1, GSYear, season) %>% 
   group_by(GSYear, season) %>% 
@@
 
-plot_grid(TA.GPPL + theme(legend.position = 'none'), TS.GPPL + theme(legend.position = 'none'), 
-          P.GPPL + theme(legend.position = 'none'), 
-          ET.GPPL+ theme(legend.position = 'none'), SWC.GPPL+ theme(legend.position = 'none'), SWin.GPPL+ theme(legend.position = 'none'), GPP.leg.month, ncol = 2)
+#plot_grid(TA.GPPL + theme(legend.position = 'none'), TS.GPPL + theme(legend.position = 'none'), 
+ #         P.GPPL + theme(legend.position = 'none'), 
+  #        ET.GPPL+ theme(legend.position = 'none'), SWC.GPPL+ theme(legend.position = 'none'), SWin.GPPL+ theme(legend.position = 'none'), GPP.leg.month, ncol = 2)
 ```
@@
 
-ER.summary<- cum.co2fluxes %>% select(ER_LT.gC,dayssinceJun1, GSYear, season) %>% 
+ER.summary<- cum.co2fluxes %>% dplyr::select(ER_LT.gC,dayssinceJun1, GSYear, season) %>% 
   group_by(GSYear, season) %>% 
@@
 monthlycumsum <- input.r %>%
-  select(NEE_LT.gC, GPP_LT.gC, ER_LT.gC, dayssinceJun1, GSYear, season, month) %>% 
+  dplyr:: select(NEE_LT.gC, GPP_LT.gC, ER_LT.gC, dayssinceJun1, GSYear, season, month) %>% 
   group_by(GSYear, month) %>% 
@@
 
-FFP <- input %>% select(Timestamp, Year, month,L,WS, sigma_v,  WD, ustar, L)
+FFP <- input %>% dplyr::select(Timestamp, Year, month,L,WS, sigma_v,  WD, u_star)
 #FFP[2:13] <- as.data.frame(sapply(FFP[2:13], as.numeric)) # convert data frame from character to numeric
@@
 
-FFP <- FFP[, c(1, 2, 3, 9,10,  11, 12, 13, 4, 8, 5,7, 6)] # change variable order to comply with data format
-
-meanmm  <- FFP %>% select(zm, d, L, z0, u_mean, sigma_v, wind_dir, u_star, mm, day, HH_UTC, MM) %>% ddply(c("mm","day", "HH_UTC", "MM"), summarise,
+FFP <- FFP[, c(1, 2, 3, 9,10, 6, 11, 12, 13, 4, 8, 5,7)] # change variable order to comply with data format
+
+write.csv(FFP, "C:/Users/Marion/Documents/UTas/FluxProcessing_SilverPlains/FFP.csv")
+
+meanmm  <- FFP %>% dplyr::select(zm, d, L, z0, u_mean, sigma_v, wind_dir, u_star, mm, day, HH_UTC, MM) %>% ddply(c("mm","day", "HH_UTC", "MM"), summarise,
                                                                                                  zm = mean(zm), 
@@
 ```
+
+```{r Carbon uptake period}
+summer.input <- input.r %>% filter (season == "Summer" | season =="Autumn")
+
+cum.co2fluxes.sum <- summer.input%>%
+  dplyr::select(NEE_LT.gC, GPP_LT.gC, ER_LT.gC, dayssinceJun1, GSYear, season) %>% 
+  group_by(GSYear) %>% 
+  mutate(NEEcum = cumsum(NEE_LT.gC),
+         GPPcum = cumsum(GPP_LT.gC),
+         ERcum = cumsum(ER_LT.gC))
+
+(NEEcum.p <-cum.co2fluxes.sum %>% 
+  ggplot(., aes(dayssinceJun1, NEEcum, group = GSYear, color = GSYear)) +
+  geom_line(size = 1, aes(color = GSYear))+
+   # scale_color_manual(values = group.colour)+
+       scale_x_continuous(limits = c(184, 365))+
+  ylab(bquote('Cumulative NEE (g C ' ~m^-2~')'))+
+  xlab("Days since June 1st")+
+  theme_classic()+ 
+    theme(axis.title = element_text(size = 14),
+          axis.text = element_text(size = 13)))
+
+(NEEtime.p <-summer.input%>%
+  ggplot(., aes(dayssinceJun1, NEE_LT.gC, color = GSYear)) +
+  geom_line()+
+        #scale_color_manual(values = group.colour)+
+       scale_x_continuous(limits = c(184, 365))+
+
+  ylab(bquote(' NEE (g C ' ~m^-2~')'))+
+  xlab("Days since June 1st")+
+  theme_classic()+ 
+    theme(axis.title = element_text(size = 14),
+          axis.text = element_text(size = 13)))
+
+CO2uptakesum <- summer.input %>% filter(NEE_LT.gC<0)
+CO2uptakesum.1920 <- CO2uptakesum %>% filter(GSYear == '19/20') #49
+CO2uptakesum.2021 <- CO2uptakesum %>% filter(GSYear == '20/21') #101
+CO2uptakesum.2122 <- CO2uptakesum %>% filter(GSYear == '21/22') #107
+
+```
